---
title: <center style="font-size:30px;font-style:normal;color:black;">Hierarchical Mapping: Additional Figures and Tables :</center>
subtitle: <center style="font-size:30px;font-style:normal;color:#0E0E7D;"></center>
 &nbsp;
author: |
  <center style="font-style:normal;">
  <a style="font-size:22px;color:#337ab7;text-decoration: underline;"href="http://smith-vidaurre.com/">G. Smith-Vidaurre</a><sup><span style="font-size:12px;color:black;text-decoration:none!important;">1*</span></sup>, 
  <a style="font-size:22px;color:#337ab7;text-decoration: underline;"href="http://wrightbehaviorlab.org">V. Perez</a><sup><span style="font-size:12px;color:black;text-decoration:none!important;">1</span></sup>,
  <a style="font-size:22px;color:#337ab7;text-decoration: underline;"href="http://wrightbehaviorlab.org">T.F. Wright</a><sup><span style="font-size:12px;color:black;text-decoration:none!important;">1</span></sup></center>
  &nbsp;
  <center style="font-size:18px;font-style:normal;color:black;"><sup><span style="font-size:12px;color:black;">1</span></sup>Department of Biology, New Mexico State University</center>
  <center style="font-size:18px;font-style:normal;color:black;"><sup><span style="font-size:12px;color:black;">2</span></sup>Department of Biological Sciences, University of Cincinnati</center>
  <center style="font-size:18px;font-style:normal;color:black;"><sup><span style="font-size:12px;color:black;">3</span></sup>Facultad de Biologia, Universidad Michoacana de San Nicolas de Hidalgo</center>
  <br />
  <center style="font-size:18px;"><sup style="font-size:12px;">*</sup>gsvidaurre@gmail.com</center>
  &nbsp;
date: <center style="font-size:22px;font-style:normal;>`r format(Sys.time(), '%d %B, %Y')`</center>
  <br />
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---

<style type="text/css">

a:hover {
  color: #23527c !important;
}

h1.title {
  font-size: 32px;
  color: black;
  font-weight: normal;
}

h1 {
   color: black;
   font-size: 26px;
   font-weight: normal;
}

h2 {
   color: black;
   font-size: 24px;
   font-weight: bold;
}

h3 {
   color: black;
   font-size: 20px;
   font-weight: normal;
}

h4 {
   color: black;
   font-size: 20px;
   font-weight: normal;
}

body{ /* Normal */
      font-size: 18px;
  }
code.r{ /* Code block */
    font-size: 18px;
}
</style>

```{r setup, eval = TRUE, echo = FALSE}

knitr::opts_knit$set(root.dir = "/home/owner/Desktop/GitHub_repos/vocal-learning-invasion")

```

```{r echo = TRUE, eval = TRUE, message = FALSE}

rm(list = ls())

X <- c("tidyverse", "pbapply", "dplyr", "data.table", "parallel", "scales", "knitr", "warbleR", "magick", "grid", "gridExtra", "ggplot2", "ggsn", "maptools", "png", "pracma", "dynaSpec", "viridis")

invisible(lapply(X, library, character.only = TRUE))

path <- "/media/gsvidaurre/MYIOPSITTA/R/VocalLearning_PostInvasion/Data"
gpath <- "/media/gsvidaurre/MYIOPSITTA/R/VocalLearning_PostInvasion/Graphics"
twt_path <- "/home/gsvidaurre/Desktop/Professional_Development/ABSTwitterTakeover"
seed <- 401
cores <- parallel::detectCores() - 2

```

Read in the full extended selection table for both ranges, and the selection table of the site-scale calls that went through visual inspection, to choose among calls less likely to be potential repeated individuals for an example lexicon in the main manuscript. 
```{r echo = TRUE, eval = TRUE}

nat_inv_est <- readRDS(file.path(path, "nat_inv_indiv_site_EST.RDS"))
glimpse(nat_inv_est)

site_scale_vf <- readRDS(file.path(path, "site_scale_vf.RDS"))
glimpse(site_scale_vf)

```

Make spectrograms for the example lexicons at each social scale that are main figures.

First, individual scale calls. 
```{echo = TRUE, eval = FALSE}

# Select 3 individuals per range that are used in the acoustic space panel
# indivs <- c("NAT-AAT", "NAT-UM2", "NAT-UM4", "INV-UM7", "INV-UM9", "INV-UM16")

# indivs <- c("NAT-AAT", "INV-UM7")
# Select 1 individual per range

indivs <- c("NAT-UM5", "INV-UM16")
calls <- c(
  "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_1.WAV",
  "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_5.WAV",
  "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_6.WAV",
  "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_7.WAV",
  "2019_08_09_FIEL_GSV1088_8.WAV",
  "2019_08_09_FIEL_GSV1088_9.WAV",
  "2019_08_09_FIEL_GSV1088_10.WAV",
  "2019_08_09_FIEL_GSV1088_11.WAV" 
)

indiv_calls <- nat_inv_est %>%
  as_tibble() %>%
  dplyr::filter(social_scale == "Individual") %>%
  dplyr::filter(Bird_ID %in% indivs) %>%
  dplyr::filter(sound.files %in% calls) %>%
  pull(sound.files)

head(indiv_calls)

# Filter the full EST by these calls
tmp_est <- nat_inv_est[grep(paste(paste("^", indiv_calls, "$", sep = ""), collapse = "|"), nat_inv_est$sound.files), ]
nrow(tmp_est)
class(tmp_est)

# Make spectrograms with axis labels, inner.mar helps cut out the axis titles
# spectrograms(tmp_est, wl = 378, flim = c(1, 8), ovlp = 90, mar = 0.01, res = 300, path = gpath, osci = FALSE, parallel = cores, line = FALSE, title.labels = NULL, axisX = TRUE, axisY = TRUE, inner.mar =  c(2, 3, 0.5, 0), propwidth = FALSE)

# Make spectrograms with no axes
# specreator(tmp_est, flim = c(1, 8), ovlp = 90, mar = 0.01, res = 300, path = gpath, osci = FALSE, parallel = cores, line = FALSE, title.labels = NULL, axisX = FALSE, axisY = FALSE, inner.mar = c(0, 0, 0, 0), wl = 378)

# Make spectrograms with ggspectro to have more control over axis text, need to loop over .wav files in the EST
# https://rug.mnhn.fr/seewave/spec.html

# x label formatter
s_formatter <- function(x){
  # lab <- paste0(x, " s")
  lab <- sprintf("%0.2f", x)
}

# y label formatter
khz_formatter <- function(y){
  lab <- paste0(y)
  # lab <- paste0(y, " kHz")
}

oscillo_theme_dark <- theme(
  panel.grid.major.y = element_blank(),
  panel.grid.major.x = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill = "transparent"),
  panel.border = element_rect(linetype = "solid", fill = NA, color = "grey"),
  axis.line = element_line(size = 0.15),
  legend.position = "none",
  plot.background = element_rect(fill = "white"),
  plot.margin = unit(c(0, 0, 0.1, 0.1), "lines"), # top, right, bottom, left
  axis.title = element_blank(),
  axis.text = element_text(size = 6.5, color = "black", vjust = 0),
  axis.ticks = element_line(color = "black", size = 0.15)
)

gray_colors <- reverse.gray.colors.2(12)

x11()

# attributes(tmp_est)

tmp_est_nat <- tmp_est[grep("Native", tmp_est$range), ]
glimpse(tmp_est_nat)

# The native range calls, x-axis limits up to 0.24 s
invisible(pblapply(1:nrow(tmp_est_nat), function(w){
  
  gg <- ggspectro(wave = attr(tmp_est_nat, "wave.objects")[[w]], f = attr(tmp_est_nat, "wave.objects")[[w]]@samp.rate, ovlp = 90)+ 
    scale_x_continuous(limits = c(0.04, 0.26), breaks = seq(from = 0.04, to = 0.24, by = 0.04), labels = s_formatter, expand = c(0, 0))+
    scale_y_continuous(limits = c(0.5, 6.75), breaks = seq(from = 1, to = 6, by = 1), expand = c(0, 0), labels = khz_formatter, position = "left")+
    geom_raster(aes(fill = amplitude), hjust = 0, vjust = 0, interpolate = TRUE) +
    scale_fill_gradientn(colours = gray_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-30, 0)) +
    oscillo_theme_dark
  
  print(gg)
  
  ggsave(file.path(gpath, paste(tmp_est_nat$sound.files[w], "-1.jpeg", sep = "")), dpi = 300, units = "px", width = 425, height = 300)
  
}))

# Invasive range calls, which are slightly shorter
tmp_est_inv <- tmp_est[grep("Invasive", tmp_est$range), ]
glimpse(tmp_est_inv)

# The invasive range calls, x-axis limits up to 0.2 s
invisible(pblapply(1:nrow(tmp_est_inv), function(w){
  
  gg <- ggspectro(wave = attr(tmp_est_inv, "wave.objects")[[w]], f = attr(tmp_est_inv, "wave.objects")[[w]]@samp.rate, ovlp = 90)+ 
    scale_x_continuous(limits = c(0.04, 0.22), breaks = seq(from = 0.04, to = 0.20, by = 0.04), labels = s_formatter, expand = c(0, 0))+
    scale_y_continuous(limits = c(0.5, 6.75), breaks = seq(from = 1, to = 6, by = 1), expand = c(0, 0), labels = khz_formatter, position = "left")+
    geom_raster(aes(fill = amplitude), hjust = 0, vjust = 0, interpolate = TRUE) +
    scale_fill_gradientn(colours = gray_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-30, 0)) +
    oscillo_theme_dark
  
  print(gg)
  
  ggsave(file.path(gpath, paste(tmp_est_inv$sound.files[w], "-1.jpeg", sep = "")), dpi = 300, units = "px", width = 425, height = 300)
  
}))

```

I selected 4 of the highest quality calls from each individual. This is the list of spectrograms I used, in order per individual by top to bottom:

NAT-UM5:

2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_1.WAV
2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_5.WAV
2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_6.WAV
2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_7.WAV


INV-UM16:

2019_08_09_FIEL_GSV1088_8.WAV
2019_08_09_FIEL_GSV1088_9.WAV
2019_08_09_FIEL_GSV1088_10.WAV
2019_08_09_FIEL_GSV1088_11.WAV (used as guide image, made smaller to have axes fit)



Other individuals if need these later:

NAT-UM2:

2017_07_24_1145-01_INDIV-UNMARKED-BIRD2_MZ000284_20.WAV
2017_07_24_1145-01_INDIV-UNMARKED-BIRD2_MZ000284_17.WAV
2017_07_24_1145-01_INDIV-UNMARKED-BIRD2_MZ000284_7.WAV


NAT-UM4:

2017_07_26_1145-02_INDIV-UNMARKED-BIRD4_MZ000321_10.WAV
2017_07_26_1145-02_INDIV-UNMARKED-BIRD4_MZ000321_6.WAV
2017_07_26_1145-02_INDIV-UNMARKED-BIRD4_MZ000321_7.WAV

INV-UM9:

2019_08_06_ELEM_GSV1033_8.WAV
2019_08_06_ELEM_GSV1033_9.WAV
2019_08_06_ELEM_GSV1033_10.WAV

INV-UM16:

2019_08_09_FIEL_GSV1088_9.WAV
2019_08_09_FIEL_GSV1088_10.WAV
2019_08_09_FIEL_GSV1088_11.WAV

```{r echo = TRUE, eval = FALSE}

# Add colored borders by individual.
cols <- scales::alpha(c("navy", "gold2", 0.45))
indivs <- c("NAT-UM5", "INV-UM16")

img_list <- list(
  c(
    "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_1.WAV",
    "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_5.WAV",
    "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_6.WAV",
    "2017_08_21_CHAC_INDIV-UNMARKED-BIRD5_1242_7.WAV"
    ),
  c(
    "2019_08_09_FIEL_GSV1088_8.WAV",
    "2019_08_09_FIEL_GSV1088_9.WAV",
    "2019_08_09_FIEL_GSV1088_10.WAV",
    "2019_08_09_FIEL_GSV1088_11.WAV"
  )
)


# i <- 1
# z <- 1
invisible(pblapply(1:length(img_list), function(i){
  
  lapply(1:length(img_list[[i]]), function(z){
    
    img <- image_read(file.path(gpath, paste(img_list[[i]][z], "-1.jpeg", sep = "")))
  
    image_write(image_border(img, cols[i], "10x10"), path = file.path(gpath, paste(img_list[[i]][z], "_border.jpeg", sep = "")), format = "jpeg")
    
  })
  
}))

```

Second, site scale calls. 
```{echo = TRUE, eval = FALSE}

# Select 1 site per range
sites <- c("LENA_2017", "INTR_2019")

# Filter the full EST by these sites and randomly select 10 calls per site to select 4 among these for the main figure
# set.seed(seed)
# site_calls <- site_scale_vf %>%
#   filter(social_scale == "Site") %>%
#   filter(site_year %in% sites) %>%
#   droplevels() %>%
#   group_by(site_year) %>%
#   nest() %>%
#   ungroup() %>%
#   inner_join(
#     site_scale_vf %>%
#       filter(social_scale == "Site") %>%
#       filter(site_year %in% sites) %>%
#       droplevels() %>%
#       group_by(site_year) %>%
#       dplyr::summarise(
#         n_calls = length(sound.files)
#       ) %>%
#       dplyr::mutate(
#         n_samp = ifelse(n_calls > 12, 12, n_calls)
#       ) %>%
#       dplyr::select(c(-n_calls)),
#     by = "site_year"
#   ) %>%
#   dplyr::mutate(
#     rsamp_call = purrr::map2(data, n_samp, sample_n, replace = FALSE)
#   ) %>%
#   dplyr::select(-data) %>%
#   unnest(rsamp_call) %>%
#   pull(sound.files)
# 
# head(site_calls)

site_calls <- c(
  "2017_10_23_LENA_1550_1.WAV",
  "2017_10_23_LENA_1553_2.WAV",
  "2017_10_23_LENA_1554_5.WAV",
  "2017_10_23_LENA_1554_6.WAV",
  "2019_08_08_INTR_1094_8.WAV",
  "2019_08_08_INTR_GSV1056_5.WAV",
  "2019_08_08_INTR_1088_2.WAV",
  "2019_08_08_INTR_1094_31.WAV"
)


# Filter the full EST by these calls
tmp_est <- nat_inv_est[grep(paste(paste("^", site_calls, "$", sep = ""), collapse = "|"), nat_inv_est$sound.files), ]
nrow(tmp_est)
class(tmp_est)

# Make spectrograms with ggspectro to have more control over axis text, need to loop over .wav files in the EST
# https://rug.mnhn.fr/seewave/spec.html

# x label formatter
s_formatter <- function(x){
  # lab <- paste0(x, " s")
  lab <- sprintf("%0.2f", x)
}

# y label formatter
khz_formatter <- function(y){
  lab <- paste0(y)
  # lab <- paste0(y, " kHz")
}

oscillo_theme_dark <- theme(
  panel.grid.major.y = element_blank(),
  panel.grid.major.x = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill = "transparent"),
  panel.border = element_rect(linetype = "solid", fill = NA, color = "grey"),
  axis.line = element_line(size = 0.15),
  legend.position = "none",
  plot.background = element_rect(fill = "white"),
  plot.margin = unit(c(0, 0, 0.1, 0.1), "lines"), # top, right, bottom, left
  axis.title = element_blank(),
  axis.text = element_text(size = 6.5, color = "black", vjust = 0),
  axis.ticks = element_line(color = "black", size = 0.15)
)

gray_colors <- reverse.gray.colors.2(12)

x11()

# attributes(tmp_est)

tmp_est_nat <- tmp_est[grep("Native", tmp_est$range), ]
glimpse(tmp_est_nat)

# The native range calls, x-axis limits up to 0.24 s
invisible(pblapply(1:nrow(tmp_est_nat), function(w){
  
  gg <- ggspectro(wave = attr(tmp_est_nat, "wave.objects")[[w]], f = attr(tmp_est_nat, "wave.objects")[[w]]@samp.rate, ovlp = 90)+ 
    scale_x_continuous(limits = c(0.04, 0.24), breaks = seq(from = 0.04, to = 0.22, by = 0.04), labels = s_formatter, expand = c(0, 0))+
    scale_y_continuous(limits = c(0.5, 6.75), breaks = seq(from = 1, to = 6, by = 1), expand = c(0, 0), labels = khz_formatter, position = "left")+
    geom_raster(aes(fill = amplitude), hjust = 0, vjust = 0, interpolate = TRUE) +
    scale_fill_gradientn(colours = gray_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-30, 0)) +
    oscillo_theme_dark
  
  print(gg)
  
  ggsave(file.path(gpath, paste(tmp_est_nat$sound.files[w], "-1.jpeg", sep = "")), dpi = 300, units = "px", width = 425, height = 300)
  
}))

# Invasive range calls, which are slightly shorter
tmp_est_inv <- tmp_est[grep("Invasive", tmp_est$range), ]
glimpse(tmp_est_inv)

# The invasive range calls, x-axis limits up to 0.2 s
invisible(pblapply(1:nrow(tmp_est_inv), function(w){
  
  gg <- ggspectro(wave = attr(tmp_est_inv, "wave.objects")[[w]], f = attr(tmp_est_inv, "wave.objects")[[w]]@samp.rate, ovlp = 90)+ 
    scale_x_continuous(limits = c(0.04, 0.24), breaks = seq(from = 0.04, to = 0.22, by = 0.04), labels = s_formatter, expand = c(0, 0))+
    scale_y_continuous(limits = c(0.5, 6.75), breaks = seq(from = 1, to = 6, by = 1), expand = c(0, 0), labels = khz_formatter, position = "left")+
    geom_raster(aes(fill = amplitude), hjust = 0, vjust = 0, interpolate = TRUE) +
    scale_fill_gradientn(colours = gray_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-30, 0)) +
    oscillo_theme_dark
  
  print(gg)
  
  ggsave(file.path(gpath, paste(tmp_est_inv$sound.files[w], "-1.jpeg", sep = "")), dpi = 300, units = "px", width = 425, height = 300)
  
}))

```

I selected 4 of the highest quality calls from each site. This is the list of spectrograms I used, in order per site by top to bottom:

LENA:

2017_10_23_LENA_1550_1.WAV
2017_10_23_LENA_1553_2.WAV
2017_10_23_LENA_1554_5.WAV
2017_10_23_LENA_1554_6.WAV

INTR:

2019_08_08_INTR_1094_8.WAV
2019_08_08_INTR_GSV1056_5.WAV
2019_08_08_INTR_1088_2.WAV
2019_08_08_INTR_1094_31.WAV


```{r echo = TRUE, eval = FALSE}

# Also add colored borders by individual...wavs <- ccs_est_predict %>%
cols <- scales::alpha(c("navy", "gold2", 0.45))
sites <- c("LENA_2017", "INTR_2019")

img_list <- list(
  c(
    "2017_10_23_LENA_1550_1.WAV",
    "2017_10_23_LENA_1553_2.WAV",
    "2017_10_23_LENA_1554_5.WAV",
    "2017_10_23_LENA_1554_6.WAV"
  ),
  c(
    "2019_08_08_INTR_1094_8.WAV",
    "2019_08_08_INTR_GSV1056_5.WAV",
    "2019_08_08_INTR_1094_31.WAV",
    "2019_08_08_INTR_1088_2.WAV"
  )
)

# i <- 1
# z <- 1
invisible(pblapply(1:length(img_list), function(i){
  
  lapply(1:length(img_list[[i]]), function(z){
    
    img <- image_read(file.path(gpath, paste(img_list[[i]][z], "-1.jpeg", sep = "")))
  
    image_write(image_border(img, cols[i], "10x10"), path = file.path(gpath, paste(img_list[[i]][z], "_border.jpeg", sep = "")), format = "jpeg")
    
  })
  
}))


```

### Audio files

Chose one call from spectrograms above, and wrote out .wav files in real and 1/4 time to be used for talks. 
```{r echo = TRUE, eval = FALSE}

wav_nm <- "2017_10_23_LENA_1553_2.WAV"

# Wrote out the .wav file
nat_inv_est

wav <- attr(nat_inv_est, "wave.objects")[grep(wav_nm, names(attr(nat_inv_est, "wave.objects")))]
wav[[1]]

writeWave(wav[[1]], filename = file.path(gpath, "2017_10_23_LENA_1553_2.WAV"))

# Then used sox to created a slowed version 
# sox /media/owner/MYIOPSITTA/R/VocalLearning_PostInvasion/Graphics/2017_10_23_LENA_1553_2.WAV /media/owner/MYIOPSITTA/R/VocalLearning_PostInvasion/Graphics/2017_10_23_LENA_1553_2_quarterTime.WAV speed 0.25

# Made spectrograms (had to use more than one .wav file or else the EST isn't recognized)
# Filter the full EST by these calls
tmp_est <- nat_inv_est[grep("LENA", nat_inv_est$site), ]
nrow(tmp_est)
class(tmp_est)

# Make spectrograms with axis labels, inner.mar helps cut out the axis titles
specreator(tmp_est, flim = c(0, 10), ovlp = 90, mar = 0.01, res = 300, path = path, osci = FALSE, parallel = cores, line = FALSE, title.labels = NULL, wl = 378)

```


# Spectrograms for defense talk lexicon, native range only

Individual scale calls for the 5 individuals at site 1145, and calls for sites INES-08, LENA, RIAC, SEMI.  
```{echo = TRUE, eval = FALSE}

indiv_calls <- nat_inv_est %>%
  as_tibble() %>%
  filter(social_scale == "Individual") %>%
  filter(site == "1145") %>%
  droplevels() %>%
  pull(sound.files)

head(indiv_calls)

# Filter the full EST by these calls
tmp_est <- nat_inv_est[grep(paste(paste("^", indiv_calls, "$", sep = ""), collapse = "|"), nat_inv_est$sound.files), ]
nrow(tmp_est)
class(tmp_est)

# Make spectrograms with axis labels, inner.mar helps cut out the axis titles
specreator(tmp_est, flim = c(1, 8), ovlp = 90, mar = 0.01, res = 300, path = gpath, osci = FALSE, parallel = cores, line = FALSE, title.labels = NULL, axisX = FALSE, axisY = FALSE, wl = 378, inner.mar = c(0, 0, 0, 0))
# inner.mar = c(2, 2, 0.5, 0) # if axis text not desired, note that the font size scales very poorly

# Resize the image files to be used for the lexicon
imgs <- c(
  "2017_07_29_1145-02_INDIV-AAT_1224_1.WAV",
  "2017_07_29_1145-02_INDIV-AAT_1224_2.WAV",
  "2017_07_29_1145-02_INDIV-AAT_1224_3.WAV",
  "2017_07_29_1145-02_INDIV-AAT_1224_4.WAV",
  "2017_07_28_1145-01_INDIV-UNMARKED-BIRD1_1193_8.WAV",
  "2017_07_28_1145-01_INDIV-UNMARKED-BIRD1_1193_9.WAV",
  "2017_07_28_1145-01_INDIV-UNMARKED-BIRD1_1193_10.WAV",
  "2017_07_28_1145-01_INDIV-UNMARKED-BIRD1_1193_16.WAV",
  "2017_07_24_1145-01_INDIV-UNMARKED-BIRD2_MZ000284_4.WAV",
  "2017_07_24_1145-01_INDIV-UNMARKED-BIRD2_MZ000284_5.WAV",
  "2017_07_24_1145-01_INDIV-UNMARKED-BIRD2_MZ000284_6.WAV",
  "2017_07_24_1145-01_INDIV-UNMARKED-BIRD2_MZ000284_10.WAV"
  
  )

# Resize images to 430 pixels wide by 285 pixels high, ignore aspect ratio
# Leaves enough space for adding a colored border around each image file
invisible(pblapply(1:length(imgs), function(i){
  
  img <- image_read(file.path(gpath, paste(imgs[i], "-1.jpeg", sep = "")))
  image_write(image_scale(img, geometry = "435x300!"), path = file.path(gpath, paste(imgs[i], "sm.jpeg", sep = "_")))
  
}))

# Site scale calls
site_calls <- nat_inv_est %>%
  as_tibble() %>%
  filter(social_scale == "Site") %>%
  filter(site %in% c("INES-08", "LENA", "RIAC")) %>%
  droplevels() %>%
  pull(sound.files)

head(site_calls)

# Filter the full EST by these calls
tmp_est <- nat_inv_est[grep(paste(paste("^", site_calls, "$", sep = ""), collapse = "|"), nat_inv_est$sound.files), ]
nrow(tmp_est)
class(tmp_est)

# Make spectrograms with axis labels, inner.mar helps cut out the axis titles
specreator(tmp_est, flim = c(1, 8), ovlp = 90, mar = 0.01, res = 300, path = gpath, osci = FALSE, parallel = cores, line = FALSE, title.labels = NULL, axisX = FALSE, axisY = FALSE, inner.mar = c(0, 0, 0, 0), wl = 378)

imgs <- c(
  "2017_07_13_INES-08_1103_5.WAV",
  "2017_07_13_INES-08_1094_3.WAV",
  "2017_07_13_INES-08_1094_4.WAV",
  "2017_07_13_INES-08_1098_2.WAV",
  "2017_10_23_LENA_1550_1.WAV",
  "2017_10_23_LENA_1553_2.WAV",
  "2017_10_23_LENA_1554_5.WAV",
  "2017_10_23_LENA_1554_6.WAV",
  "2017_06_28_RIAC-01_1045_1.WAV",
  "2017_06_28_RIAC-01_1048_3.WAV",
  "2017_06_28_RIAC-01_1049_7.WAV",
  "2017_06_28_RIAC-01_1050_3.WAV"
  )


# Resize images to 430 pixels wide by 285 pixels high, ignore aspect ratio
# Leaves enough space for adding a colored border around each image file
invisible(pblapply(1:length(imgs), function(i){
  
  img <- image_read(file.path(gpath, paste(imgs[i], "-1.jpeg", sep = "")))
  image_write(image_scale(img, geometry = "435x300!"), path = file.path(gpath, paste(imgs[i], "sm.jpeg", sep = "_")))
  
}))

```


# Acoustic space figures for talks (monk parakeet, yellow-naped amazon)

Read in the full dataset used for comparison between ranges.
```{r echo = TRUE, eval = TRUE}

site_scale_nf <- readRDS(file.path(path, "site_scale_nf.RDS"))

# Full site scale dataset
# 1191 calls
site_scale_nf %>%
  nrow()

```

## Acoustic space for species comparison

SPCC acoustic space for monk parakeets (both ranges), and yellow-naped amazons. Used as a visual for talks. 

# Individual scale for both species

Here, performed t-SNE for the YNA similarity matrix. MDS did not pull apart sites as well as I hoped.
```{r echo = TRUE, eval = FALSE}

yna_est <- readRDS(file.path(path, "YNA_extended_selection_table.RDS"))
glimpse(yna_est)

```

```{r echo = TRUE, eval = FALSE}

xc_mat_yna <- readRDS(file.path(path, "xc_mat_yna.RDS"))

# Change dimension names
dimnames(xc_mat_yna) <- list(yna_est$sound.files, yna_est$sound.files)
str(xc_mat_yna)

########## MDS #################

# Convert to a distance matrix and dist object for isoMDS
# dist_mat <- stats::as.dist(1 - xc_mat_yna, diag = TRUE, upper = TRUE)
# str(dist_mat)

# Reduce dimensionality of the SPCC matrix to visualize calls in 2D acoustic space
# iso <- invisible(MASS::isoMDS(dist_mat, k = 2, maxit = 1000, trace = FALSE))
# str(iso)

########## t-SNE #################

X <- stats::as.dist(1 - xc_mat_yna, diag = TRUE, upper = TRUE)
  
tmp <- list()
  
# Embed in 2 dimensions for visualization with intermediate perplexity
tmp <- lapply(1:10, function(n){
  Rtsne::Rtsne(X, dims = 2, pca = FALSE, max_iter = 5000, perplexity = round((dim(xc_mat_yna)[1] - 1)/4), is_distance = TRUE, theta = 0.0)
})
# str(tmp)

KL <- sapply(1:length(tmp), function(i){
  tmp[[i]]$itercosts[100]
}, simplify = TRUE)
  
# Overwrite tmp with the solution that minimized KL
tsne_yna <- tmp[[which(KL == min(KL))]]

saveRDS(tsne_yna, file.path(path, "tsne_spcc_yna.RDS"))

```

Get individuals from a single Northern dialect site.
```{r echo = TRUE, eval = TRUE}

tsne_yna <- readRDS(file.path(path, "tsne_spcc_yna.RDS"))

yna_spcc_tsne_df <- data.frame(X = tsne_yna$Y[, 1]) %>%
  dplyr::mutate(
    Y = tsne_yna$Y[, 2], 
    spp = "Yellow-naped amazon",
    dialect = yna_est$regional_dialect,
    site = yna_est$site,
    indiv = yna_est$bird_ID, 
    sound.files = yna_est$sound.files
  )
glimpse(yna_spcc_tsne_df)

# Filter by Northern dialect calls
yna_nor <- yna_spcc_tsne_df %>%
  as_tibble() %>%
  filter(dialect == "Nor") %>%
  droplevels()

# How many individuals per site?
yna_nor %>%
  group_by(site) %>%
  dplyr::summarise(
    n_indivs = n_distinct(indiv)
  )

# Get 4 individuals from one site
# set.seed(seed)
indivs <- yna_nor %>%
  filter(site == "horiz") %>%
  pull(indiv) %>%
  unique() %>%
  as.character()

indivs

yna_indivs_df <- yna_spcc_tsne_df %>%
  filter(indiv %in% indivs) %>%
  dplyr::mutate(
    indiv = toupper(indiv)
  ) %>%
  droplevels()

glimpse(yna_indivs_df)

```

Make the acoustic space plot.
```{r echo = TRUE, eval = TRUE}

### Yellow-naped amazon, individual scale

# Colors by range, hues by individual or site
cols <- scales::alpha(c("maroon", "firebrick", "red", "orangered"), 0.65)

# Shapes by individual
shps <- c(21, 23, 24, 25)

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(yna_indivs_df, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

glimpse(yna_indivs_df)

gg <- yna_indivs_df %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("firebrick", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_SPCC_tSNE_YNA_IndivScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()

```

## Monk parakeets

Performed t-SNE for the monk parakeet similarity matrix, individual scale calls.
```{r echo = TRUE, echo = TRUE}

xc_mat_spec <- readRDS(file.path(path, "xc_mat_NAT_INV.RDS"))
# dim(xc_mat_spec) == nrow(nat_inv_est)

# Rename dimension names of matrix
wavs <- dimnames(xc_mat_spec)[[1]]
wavs <- gsub(".WAV-1", ".WAV", wavs)
# head(wavs)

dimnames(xc_mat_spec) <- list(wavs, wavs)

nat_indivs <- c("NAT-AAT", "NAT-UM1", "NAT-UM2", "NAT-UM4")
inv_indivs <- c("INV-UM7", "INV-UM9", "INV-UM16", "INV-UM17")

# Subset the ESTby these individuals
mnk_indiv_df <- nat_inv_est %>%
  as_tibble() %>%
  filter(social_scale == "Individual") %>%
  filter(Bird_ID %in% c(nat_indivs, inv_indivs)) %>%
  droplevels()
glimpse(mnk_indiv_df)

```

```{r echo = TRUE, echo = TRUE}

# Get calls for these birds
calls_tmp <- mnk_indiv_df %>%
  pull(sound.files) %>%
  as.character()

# Subset matrices by these calls
inds <- grep(paste(paste("^", calls_tmp, "$", sep = ""), collapse = "|"), dimnames(xc_mat_spec)[[1]])
# length(inds) == length(calls_tmp)

xc_mat_tmp <- xc_mat_spec[inds, inds]
# Calls in the filtered are in the same order as in calls_tmp
# all(dimnames(xc_mat_tmp)[[1]] == calls_tmp)

# Convert to a distance matrix and dist object for isoMDS
# dist_mat <- stats::as.dist(1 - xc_mat_tmp, diag = TRUE, upper = TRUE)
# str(dist_mat)

# Reduce dimensionality of the SPCC matrix to visualize calls in 2D acoustic space
# iso <- invisible(MASS::isoMDS(dist_mat, k = 2, maxit = 1000, trace = FALSE))
# str(iso)

X <- stats::as.dist(1 - xc_mat_tmp, diag = TRUE, upper = TRUE)
  
tmp <- list()
  
# Embed in 2 dimensions for visualization with intermediate perplexity
tmp <- lapply(1:10, function(n){
  Rtsne::Rtsne(X, dims = 2, pca = FALSE, max_iter = 5000, perplexity = round((dim(xc_mat_tmp)[1] - 1)/4), is_distance = TRUE, theta = 0.0)
})
# str(tmp)

KL <- sapply(1:length(tmp), function(i){
  tmp[[i]]$itercosts[100]
}, simplify = TRUE)
  
# Overwrite tmp with the solution that minimized KL
tsne_mnk <- tmp[[which(KL == min(KL))]]

saveRDS(tsne_mnk, file.path(path, "tsne_spcc_indiv_mnk.RDS"))

```

```{r echo = TRUE, eval = TRUE}

tsne_mnk <- readRDS(file.path(path, "tsne_spcc_indiv_mnk.RDS"))

mnk_spcc_indiv_tsne_df <- data.frame(spp = "Monk parakeet", X = tsne_mnk$Y[, 1], Y = tsne_mnk$Y[, 2]) %>%
  dplyr::mutate(
    indiv = mnk_indiv_df$Bird_ID,
    range = mnk_indiv_df$range,
    indiv = gsub("NAT-|INV-", "", indiv)
  )
glimpse(mnk_spcc_indiv_tsne_df)

```

Native range individuals.
```{r echo = TRUE, echo = TRUE}

# Colors by range, hues by individual or site
cols <- scales::alpha(c("navy", "royalblue2", "turquoise", "dodgerblue", "deepskyblue4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24, 25, 6)

mnk_nat_indiv <- mnk_spcc_indiv_tsne_df %>%
  filter(range == "Native") %>%
  dplyr::mutate(
    spp = paste(spp, "Native", sep = " - ")
  ) %>%
  droplevels()

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(mnk_nat_indiv, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

gg <- mnk_nat_indiv %>%
  droplevels() %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_SPCC_tSNE_MNKNative_IndivScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()

```

Monks, invasive range individuals.
```{r echo = TRUE, echo = TRUE}

# Colors by range, hues by individual or site
cols <- scales::alpha(c("gold2", "goldenrod2", "darkorange3", "gold4", "darkorange4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24, 25, 6)

mnk_inv_indiv <- mnk_spcc_indiv_tsne_df %>%
  filter(range == "Invasive") %>%
  dplyr::mutate(
    spp = paste(spp, "Invasive", sep = " - ")
  ) %>%
  droplevels()

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(mnk_inv_indiv, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

gg <- mnk_inv_indiv %>%
  droplevels() %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_SPCC_tSNE_MNKInvasive_IndivScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()

```


# Site scale for both species

```{r echo = TRUE, eval = TRUE}

tsne_yna <- readRDS(file.path(path, "tsne_spcc_yna.RDS"))

yna_spcc_tsne_df <- data.frame(X = tsne_yna$Y[, 1]) %>%
  dplyr::mutate(
    Y = tsne_yna$Y[, 2], 
    spp = "Yellow-naped amazon",
    ids = yna_est$site, 
    sound.files = yna_est$sound.files
  )
glimpse(yna_spcc_tsne_df)

# Filter by Northern dialect calls
yna_nor <- yna_est %>%
  as_tibble() %>%
  filter(regional_dialect == "Nor") %>%
  droplevels()

# Get 4 sites for YNA Northern dialect (all sites were recorded in the same year)
set.seed(seed)
sites <- yna_nor %>%
  pull(site) %>%
  unique() %>%
  as.character() %>%
  sample(4, replace = FALSE)

sites

yna_spcc_tsne_df <- yna_spcc_tsne_df %>%
  filter(ids %in% sites) %>%
  droplevels()

glimpse(yna_spcc_tsne_df)

```

Yellow-naped amazon sites.
```{r echo = TRUE, eval = FALSE}

### Yellow-naped amazons

yna_spcc_tsne_df <- yna_spcc_tsne_df %>%
  dplyr::mutate(
    ids = toupper(ids)
  )

# Colors by range, hues by individual or site
cols <- scales::alpha(c("brown", "maroon", "firebrick", "red", "orangered"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24, 25, 6)

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(yna_spcc_tsne_df, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

gg <- yna_spcc_tsne_df %>%
  ggplot(aes(x = X, y = Y, shape = ids)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("firebrick", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_SPCC_tSNE_YNA_SiteScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()

```

# Monks, site scale, SPCC

Performed t-SNE for the monk parakeet SPCC similarity matrix.
```{r echo = TRUE, echo = TRUE}

############### Site scale calls, full dataset #############

# Native range: Randomly sample 4 sites from the Colonia department
# Invasive range: 4 sites from Austin 2019

# set.seed(seed)
# nat_sites <- nat_inv_est %>%
#   filter(range == "Native" & dept_state == "Colonia" & social_scale == "Site") %>%
#   pull(site_year) %>%
#   unique() %>%
#   sample(5, replace = FALSE)

nat_sites <- c("INES-08_2017", "LENA_2017", "RIAC_2017", "SEMI_2017")

# set.seed(seed)
# inv_sites <- nat_inv_est %>%
#   filter(range == "Invasive" & year == "2019" & social_scale == "Site" & invasive_city == "Austin") %>%
#   pull(site_year) %>%
#   unique() %>%
#   sample(5, replace = FALSE)

inv_sites <- c("INTR_2019", "ELEM_2019", "SOCC_2019", "MART_2019")

nat_sites
inv_sites

# Subset the site scale calls by these site-years
sites_df <- site_scale_nf %>%
  filter(social_scale == "Site") %>%
  filter(site_year %in% c(nat_sites, inv_sites)) %>%
  droplevels()
glimpse(sites_df)

# Get calls from the full dataset (no filtering) for these sites
calls_tmp <- sites_df %>%
  pull(sound.files) %>%
  as.character()

```

```{r echo = TRUE, echo = TRUE}

# Subset matrices by these calls
inds <- grep(paste(paste("^", calls_tmp, "$", sep = ""), collapse = "|"), dimnames(xc_mat_spec)[[1]])
# length(inds) == length(calls_tmp)

xc_mat_tmp <- xc_mat_spec[inds, inds]
# Calls in the filtered are in the same order as in calls_tmp
# all(dimnames(xc_mat_tmp)[[1]] == calls_tmp)

# Convert to a distance matrix and dist object for isoMDS
# dist_mat <- stats::as.dist(1 - xc_mat_tmp, diag = TRUE, upper = TRUE)
# str(dist_mat)

# Reduce dimensionality of the SPCC matrix to visualize calls in 2D acoustic space
# iso <- invisible(MASS::isoMDS(dist_mat, k = 2, maxit = 1000, trace = FALSE))
# str(iso)

X <- stats::as.dist(1 - xc_mat_tmp, diag = TRUE, upper = TRUE)
  
tmp <- list()
  
# Embed in 2 dimensions for visualization with intermediate perplexity
# Did not use perplexity = round((dim(xc_mat_tmp)[1] - 1)/4), too high 
tmp <- lapply(1:10, function(n){
  Rtsne::Rtsne(X, dims = 2, pca = FALSE, max_iter = 5000, perplexity = 35, is_distance = TRUE, theta = 0.0)
})
# str(tmp)

KL <- sapply(1:length(tmp), function(i){
  tmp[[i]]$itercosts[100]
}, simplify = TRUE)
  
# Overwrite tmp with the solution that minimized KL
tsne_mnk <- tmp[[which(KL == min(KL))]]

saveRDS(tsne_mnk, file.path(path, "tsne_spcc_sites_mnk.RDS"))

```

```{r echo = TRUE, eval = TRUE}

tsne_mnk <- readRDS(file.path(path, "tsne_spcc_sites_mnk.RDS"))

mnk_spcc_tsne_df <- data.frame(spp = "Monk parakeet", X = tsne_mnk$Y[, 1], Y = tsne_mnk$Y[, 2], ids = sites_df %>%
  pull(site_year) %>%
  as.character(), sound.files = calls_tmp, range = sites_df %>%
  pull(range) %>%
  as.character())
glimpse(mnk_spcc_tsne_df)

```

Monk parakeets, both ranges.
```{r echo = TRUE, echo = TRUE}

mnk_spcc_tsne_df <- mnk_spcc_tsne_df %>%
  dplyr::mutate(
    spp_range = paste(spp, range, sep = " - "),
    spp_range = factor(spp_range, levels = c("Monk parakeet - Native", "Monk parakeet - Invasive")),
    # Remove year labels in IDs
    ids = gsub("_2017|_2019", "", ids)
  )

glimpse(mnk_spcc_tsne_df)


# Monk parakeets, native
mnk_nat <- mnk_spcc_tsne_df %>%
  filter(spp_range == "Monk parakeet - Native") %>%
  droplevels()
glimpse(mnk_nat)

# Colors by range, hues by individual or site
cols <- scales::alpha(c("navy", "royalblue2", "turquoise", "dodgerblue", "deepskyblue4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24, 25, 6)

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(mnk_nat, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

gg1 <- mnk_nat %>%
  ggplot(aes(x = X, y = Y, shape = ids)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg1

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg1))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_SPCC_tSNE_MNKNative_SiteScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()


# Monk parakeets, invasive
mnk_inv <- mnk_spcc_tsne_df %>%
  filter(spp_range == "Monk parakeet - Invasive") %>%
  droplevels()
glimpse(mnk_inv)

# Colors by range, hues by individual or site
cols <- scales::alpha(c("gold2", "goldenrod2", "darkorange3", "gold4", "darkorange4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24, 25, 6)

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(mnk_inv, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

gg2 <- mnk_inv %>%
  ggplot(aes(x = X, y = Y, shape = ids)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg2

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg2))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_SPCC_tSNE_MNKInvasive_SiteScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()

```

# Monks, site scale, random forests

Performed t-SNE for the monk parakeet random forests similarity matrix.
```{r echo = TRUE, echo = TRUE}

# Read RF similarity
predictn_prox_mat <- readRDS(file.path(path, "prediction_prox_mat.RDS"))

# Random forests datasets (training, validation, prediction)
sup_rf_df <- read.csv(file.path(path, "supervised_RF_datasets_acousticSimilarity.csv")) %>%
 dplyr::mutate(
    year = as.character(year)
  )

predictn_df <- sup_rf_df %>%
  filter(rf_set == "prediction") %>%
  droplevels()

# Add dimension names to the RF similarity matrix
dimnames(predictn_prox_mat) <- list(predictn_df$sound.files, predictn_df$sound.files)

############### Site scale calls, full dataset #############

nat_sites <- c("INES-08_2017", "LENA_2017", "RIAC_2017", "SEMI_2017")

inv_sites <- c("INTR_2019", "ELEM_2019", "SOCC_2019", "MART_2019")

nat_sites
inv_sites

# Subset the site scale calls by these site-years
sites_df <- site_scale_nf %>%
  filter(social_scale == "Site") %>%
  filter(site_year %in% c(nat_sites, inv_sites)) %>%
  droplevels()
glimpse(sites_df)

# Get calls from the full dataset (no filtering) for these sites
calls_tmp <- sites_df %>%
  pull(sound.files) %>%
  as.character()

# Subset matrices by these calls
inds <- grep(paste(paste("^", calls_tmp, "$", sep = ""), collapse = "|"), dimnames(predictn_prox_mat)[[1]])
# length(inds) == length(calls_tmp)

prox_mat_tmp <- predictn_prox_mat[inds, inds]
# Calls in the filtered are in the same order as in calls_tmp
# all(dimnames(prox_mat_tmp)[[1]] == calls_tmp)

X <- stats::as.dist(1 - prox_mat_tmp, diag = TRUE, upper = TRUE)
  
tmp <- list()
  
# Embed in 2 dimensions for visualization with intermediate perplexity
# Did not use perplexity = round((dim(xc_mat_tmp)[1] - 1)/4), too high 
tmp <- lapply(1:10, function(n){
  Rtsne::Rtsne(X, dims = 2, pca = FALSE, max_iter = 5000, perplexity = 35, is_distance = TRUE, theta = 0.0)
})
# str(tmp)

KL <- sapply(1:length(tmp), function(i){
  tmp[[i]]$itercosts[100]
}, simplify = TRUE)
  
# Overwrite tmp with the solution that minimized KL
tsne_mnk <- tmp[[which(KL == min(KL))]]

saveRDS(tsne_mnk, file.path(path, "tsne_rf_sites_mnk.RDS"))

```

```{r echo = TRUE, eval = TRUE}

tsne_mnk <- readRDS(file.path(path, "tsne_rf_sites_mnk.RDS"))

mnk_rf_tsne_df <- data.frame(spp = "Monk parakeet", X = tsne_mnk$Y[, 1], Y = tsne_mnk$Y[, 2], ids = sites_df %>%
  pull(site_year) %>%
  as.character(), sound.files = calls_tmp, range = sites_df %>%
  pull(range) %>%
  as.character())
glimpse(mnk_rf_tsne_df)

```

Monk parakeets, both ranges.
```{r echo = TRUE, echo = TRUE}

mnk_rf_tsne_df <- mnk_rf_tsne_df %>%
  dplyr::mutate(
    spp_range = paste(spp, range, sep = " - "),
    spp_range = factor(spp_range, levels = c("Monk parakeet - Native", "Monk parakeet - Invasive")),
    # Remove year labels in IDs
    ids = gsub("_2017|_2019", "", ids)
  )

glimpse(mnk_rf_tsne_df)


# Monk parakeets, native
mnk_nat <- mnk_rf_tsne_df %>%
  filter(spp_range == "Monk parakeet - Native") %>%
  droplevels()
glimpse(mnk_nat)

# Colors by range, hues by individual or site
cols <- scales::alpha(c("navy", "royalblue2", "turquoise", "dodgerblue", "deepskyblue4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24, 25, 6)

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(mnk_nat, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

gg1 <- mnk_nat %>%
  ggplot(aes(x = X, y = Y, shape = ids)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg1

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg1))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_RF_tSNE_MNKNative_SiteScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()


# Monk parakeets, invasive
mnk_inv <- mnk_rf_tsne_df %>%
  filter(spp_range == "Monk parakeet - Invasive") %>%
  droplevels()
glimpse(mnk_inv)

# Colors by range, hues by individual or site
cols <- scales::alpha(c("gold2", "goldenrod2", "darkorange3", "gold4", "darkorange4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24, 25, 6)

# Convex hull polygons by species, range, site
hulls <- plyr::ddply(mnk_inv, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

gg2 <- mnk_inv %>%
  ggplot(aes(x = X, y = Y, shape = ids)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids), size = 1.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y", scales = "free") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )

gg2

# Color strip labels by range
g <- ggplot_gtable(ggplot_build(gg2))
stripr <- which(grepl('strip-t', g$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

grid.draw(g)

dev.off()

# Change resolution later as needed
tiff(file.path(gpath, "HierarchicalMapping_TalkFigure_RF_tSNE_MNKInvasive_SiteScale.tiff"), units = "in", width = 3.6, height = 2.25, res = 300) 
grid.draw(g)
dev.off()

```


#######################################

# Acoustic space plots for Twitter Takeover GIFs

Will use the same native and invasive range spectrograms used to generate slides for the defense, and I want spectrograms per individual to pop up with their convex hull polygons in acoustic space per still in the GIF. Per range and social scale: 4 GIFS total, and 12 stills total of acoustic space (3 individuals and sites per range).

```{r echo = TRUE, eval = TRUE}

nat_indivs <- c("NAT-AAT", "NAT-UM1", "NAT-UM2", "NAT-UM4")
inv_indivs <- c("INV-UM7", "INV-UM9", "INV-UM16", "INV-UM17", "INV-UM10") # Austin 2019 birds

# Subset the EST by these individuals
mnk_indiv_df <- nat_inv_est %>%
  as_tibble() %>%
  filter(social_scale == "Individual") %>%
  filter(Bird_ID %in% c(nat_indivs, inv_indivs)) %>%
  droplevels()
glimpse(mnk_indiv_df)

# Reran t-SNE to include the 5th Austin 2019 bird, which is not included in the RDS object saved above for SPCC t-SNE
# Get calls for these birds
calls_tmp <- mnk_indiv_df %>%
  pull(sound.files) %>%
  as.character()

xc_mat_spec <- readRDS(file.path(path, "xc_mat_NAT_INV.RDS"))
# dim(xc_mat_spec) == nrow(nat_inv_est)

# Rename dimension names of matrix
wavs <- dimnames(xc_mat_spec)[[1]]
wavs <- gsub(".WAV-1", ".WAV", wavs)
# head(wavs)

dimnames(xc_mat_spec) <- list(wavs, wavs)

# Subset matrices by these calls
inds <- grep(paste(paste("^", calls_tmp, "$", sep = ""), collapse = "|"), dimnames(xc_mat_spec)[[1]])
# length(inds) == length(calls_tmp)

xc_mat_tmp <- xc_mat_spec[inds, inds]
# Calls in the filtered are in the same order as in calls_tmp
# all(dimnames(xc_mat_tmp)[[1]] == calls_tmp)

# Convert to a distance matrix and dist object for isoMDS
# dist_mat <- stats::as.dist(1 - xc_mat_tmp, diag = TRUE, upper = TRUE)
# str(dist_mat)

# Reduce dimensionality of the SPCC matrix to visualize calls in 2D acoustic space
# iso <- invisible(MASS::isoMDS(dist_mat, k = 2, maxit = 1000, trace = FALSE))
# str(iso)

X <- stats::as.dist(1 - xc_mat_tmp, diag = TRUE, upper = TRUE)
  
tmp <- list()
  
# Embed in 2 dimensions for visualization with intermediate perplexity
tmp <- lapply(1:10, function(n){
  Rtsne::Rtsne(X, dims = 2, pca = FALSE, max_iter = 5000, perplexity = round((dim(xc_mat_tmp)[1] - 1)/4), is_distance = TRUE, theta = 0.0)
})
# str(tmp)

KL <- sapply(1:length(tmp), function(i){
  tmp[[i]]$itercosts[100]
}, simplify = TRUE)
  
# Overwrite tmp with the solution that minimized KL
tsne_mnk <- tmp[[which(KL == min(KL))]]

# tsne_mnk <- readRDS(file.path(path, "tsne_spcc_indiv_mnk.RDS"))

mnk_spcc_indiv_tsne_df <- data.frame(spp = "Monk parakeet", X = tsne_mnk$Y[, 1], Y = tsne_mnk$Y[, 2]) %>%
  dplyr::mutate(
    indiv = mnk_indiv_df$Bird_ID,
    range = mnk_indiv_df$range,
    indiv = gsub("NAT-|INV-", "", indiv)
  )
glimpse(mnk_spcc_indiv_tsne_df)

```

Native range individuals. Make 3 images that will be placed into LibreOffice draw and concatenated into GIFS with command line tools. Using just AAT, UM1, UM2, as these were in the lexicon for my defense slides.
```{r echo = TRUE, echo = TRUE}

# Make a Twitter TO theme to avoid using this code over and over
theme_AcousticSpace <- function(){ 
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    strip.text = element_text(size = 13),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 14),
    legend.justification = "center",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.margin = ggplot2::margin(0, 0, 0, 0),
    legend.box.margin = ggplot2::margin(-2, -5, -11, -5),
    legend.key.width = unit(0.5, "lines"),
    plot.margin = ggplot2::margin(0, 3, -3, -3)
  )
}

# Colors by range, hues by individual or site
cols <- scales::alpha(c("navy", "royalblue2", "turquoise"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24)

mnk_nat_indiv <- mnk_spcc_indiv_tsne_df %>%
  filter(range == "Native") %>%
  filter(indiv %in% c("AAT", "UM1", "UM2")) %>%
  dplyr::mutate(
    spp = paste(spp, "Native", sep = " - ")
  ) %>%
  droplevels()

# One individual added at a time
tmp_df1 <- mnk_nat_indiv %>%
  filter(indiv %in% c("AAT")) %>%
  droplevels() 

tmp_df2 <- mnk_nat_indiv %>%
  filter(indiv %in% c("AAT", "UM1")) %>%
  droplevels() 

# Convex hull polygons by species, range, site
hulls1 <- plyr::ddply(tmp_df1, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

hulls2 <- plyr::ddply(tmp_df2, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

hulls3 <- plyr::ddply(mnk_nat_indiv, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

# One individual added at a time
gg1 <- tmp_df1 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls1, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y", scales = "fixed") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-6, 8)) +
  scale_y_continuous(limits = c(-4, 12)) +
  theme_bw() +
  theme_AcousticSpace()

gg1

gg2 <- tmp_df2 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls2, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-6, 8)) +
  scale_y_continuous(limits = c(-4, 12)) +
  theme_bw() +
  theme_AcousticSpace()

gg2


gg3 <- mnk_nat_indiv %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls3, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-6, 8)) +
  scale_y_continuous(limits = c(-4, 12)) +
  theme_bw() +
  theme_AcousticSpace()

gg3

# Color strip labels by range per visual
g1 <- ggplot_gtable(ggplot_build(gg1))
stripr <- which(grepl('strip-t', g1$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g1$grobs[[i]]$grobs[[1]]$childrenOrder))
  g1$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g2 <- ggplot_gtable(ggplot_build(gg2))
stripr <- which(grepl('strip-t', g2$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g2$grobs[[i]]$grobs[[1]]$childrenOrder))
  g2$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g3 <- ggplot_gtable(ggplot_build(gg3))
stripr <- which(grepl('strip-t', g3$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g3$grobs[[i]]$grobs[[1]]$childrenOrder))
  g3$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()


tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Native_IndivScale_01.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g1)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Native_IndivScale_02.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g2)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Native_IndivScale_03.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g3)
dev.off()

```

Monks, invasive range individuals. Spectrograms for lexicons made below. UM7, UM16, UM10
```{r echo = TRUE, echo = TRUE}

# Colors by range, hues by individual or site
cols <- scales::alpha(c("goldenrod2", "darkorange3", "gold4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24)

mnk_inv_indiv <- mnk_spcc_indiv_tsne_df %>%
  filter(range == "Invasive") %>%
  filter(indiv %in% c("UM7", "UM16", "UM10")) %>%
  dplyr::mutate(
    spp = paste(spp, "Invasive", sep = " - "),
    indiv = factor(indiv, levels = c("UM7", "UM16", "UM10"))
  ) %>%
  droplevels()

# One individual added at a time
tmp_df1 <- mnk_inv_indiv %>%
  filter(indiv %in% c("UM7")) %>%
  droplevels() 

tmp_df2 <- mnk_inv_indiv %>%
  filter(indiv %in% c("UM7", "UM16")) %>%
  dplyr::mutate(
    indiv = factor(indiv, levels = c("UM7", "UM16"))
  ) %>%
  droplevels() 

# Convex hull polygons by species, range, site
hulls1 <- plyr::ddply(tmp_df1, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

hulls2 <- plyr::ddply(tmp_df2, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

hulls3 <- plyr::ddply(mnk_inv_indiv, "indiv", function(x){
  x[chull(x$X, x$Y), ]
})

# One individual added at a time
gg1 <- tmp_df1 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls1, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y", scales = "fixed") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-9, 5)) +
  scale_y_continuous(limits = c(0, 11)) +
  theme_bw() +
  theme_AcousticSpace()

gg1

gg2 <- tmp_df2 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls2, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-9, 5)) +
  scale_y_continuous(limits = c(0, 11)) +
  theme_bw() +
  theme_AcousticSpace()

gg2


gg3 <- mnk_inv_indiv %>%
  droplevels() %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls3, aes(x = X, y = Y, fill = indiv, color = indiv), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = indiv, color = indiv, shape = indiv), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-9, 5)) +
  scale_y_continuous(limits = c(0, 11)) +
  theme_bw() +
  theme_AcousticSpace()

gg3

# Color strip labels by range per visual
g1 <- ggplot_gtable(ggplot_build(gg1))
stripr <- which(grepl('strip-t', g1$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g1$grobs[[i]]$grobs[[1]]$childrenOrder))
  g1$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g2 <- ggplot_gtable(ggplot_build(gg2))
stripr <- which(grepl('strip-t', g2$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g2$grobs[[i]]$grobs[[1]]$childrenOrder))
  g2$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g3 <- ggplot_gtable(ggplot_build(gg3))
stripr <- which(grepl('strip-t', g3$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g3$grobs[[i]]$grobs[[1]]$childrenOrder))
  g3$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()


tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Invasive_IndivScale_01.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g1)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Invasive_IndivScale_02.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g2)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Invasive_IndivScale_03.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g3)
dev.off()

```


Site scale, SPCC, 3 sites each per range. Will also need spectros for invasive range. 

```{r echo = TRUE, eval = TRUE}

tsne_mnk <- readRDS(file.path(path, "tsne_spcc_sites_mnk.RDS"))

nat_sites <- c("INES-08_2017", "LENA_2017", "RIAC_2017", "SEMI_2017")

inv_sites <- c("INTR_2019", "ELEM_2019", "SOCC_2019", "MART_2019")

nat_sites
inv_sites

# Subset the site scale calls by these site-years
sites_df <- site_scale_nf %>%
  filter(social_scale == "Site") %>%
  filter(site_year %in% c(nat_sites, inv_sites)) %>%
  droplevels()
glimpse(sites_df)

# Get calls from the full dataset (no filtering) for these sites
calls_tmp <- sites_df %>%
  pull(sound.files) %>%
  as.character()

mnk_spcc_tsne_df <- data.frame(
  spp = "Monk parakeet", X = tsne_mnk$Y[, 1], Y = tsne_mnk$Y[, 2], ids = sites_df %>%
    pull(site_year) %>%
    as.character(), 
  sound.files = calls_tmp, range = sites_df %>%
  pull(range) %>%
    as.character()
  ) %>%
  dplyr::mutate(
    spp_range = paste(spp, range, sep = " - "),
    spp_range = factor(spp_range, levels = c("Monk parakeet - Native", "Monk parakeet - Invasive")),
    # Remove year labels in IDs
    ids = gsub("_2017|_2019", "", ids)
  )

glimpse(mnk_spcc_tsne_df)

```

Monk parakeets, native range. INES-08, LENA, RIAC
```{r echo = TRUE, echo = TRUE}

# Monk parakeets, native
mnk_nat <- mnk_spcc_tsne_df %>%
  filter(spp_range == "Monk parakeet - Native") %>%
  filter(ids %in% c("INES-08", "LENA", "RIAC")) %>%
  droplevels()
glimpse(mnk_nat)

# Colors by range, hues by individual or site
cols <- scales::alpha(c("navy", "royalblue2", "turquoise"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24)

# One individual added at a time
tmp_df1 <- mnk_nat %>%
  filter(ids %in% c("INES-08")) %>%
  droplevels() 

tmp_df2 <- mnk_nat %>%
  filter(ids %in% c("INES-08", "LENA")) %>%
  droplevels() 

# Convex hull polygons by species, range, site
hulls1 <- plyr::ddply(tmp_df1, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

hulls2 <- plyr::ddply(tmp_df2, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

hulls3 <- plyr::ddply(mnk_nat, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

# One individual added at a time
gg1 <- tmp_df1 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls1, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids, shape = ids), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y", scales = "fixed") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(5, 27)) +
  scale_y_continuous(limits = c(-15, 4)) +
  theme_bw() +
  theme_AcousticSpace()

gg1

gg2 <- tmp_df2 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls2, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids, shape = ids), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(5, 27)) +
  scale_y_continuous(limits = c(-15, 4)) +
  theme_bw() +
  theme_AcousticSpace()

gg2


gg3 <- mnk_nat %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls3, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids, shape = ids), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(5, 27)) +
  scale_y_continuous(limits = c(-15, 4)) +
  theme_bw() +
  theme_AcousticSpace()

gg3

# Color strip labels by range per visual
g1 <- ggplot_gtable(ggplot_build(gg1))
stripr <- which(grepl('strip-t', g1$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g1$grobs[[i]]$grobs[[1]]$childrenOrder))
  g1$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g2 <- ggplot_gtable(ggplot_build(gg2))
stripr <- which(grepl('strip-t', g2$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g2$grobs[[i]]$grobs[[1]]$childrenOrder))
  g2$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g3 <- ggplot_gtable(ggplot_build(gg3))
stripr <- which(grepl('strip-t', g3$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("navy", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g3$grobs[[i]]$grobs[[1]]$childrenOrder))
  g3$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()


tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Native_SiteScale_01.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g1)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Native_SiteScale_02.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g2)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Native_SiteScale_03.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g3)
dev.off()

```

Monk parakeets, site scale, invasive range....need spectros.
```{r echo = TRUE, echo = TRUE}

mnk_inv <- mnk_spcc_tsne_df %>%
  filter(spp_range == "Monk parakeet - Invasive") %>%
   filter(ids %in% c("ELEM", "INTR", "MART")) %>%
  dplyr::mutate(
    ids = factor(ids, levels = c("ELEM", "INTR", "MART"))
  ) %>%
  droplevels()
glimpse(mnk_inv)

unique(mnk_inv$ids)
levels(mnk_inv$ids)

# Colors by range, hues by individual or site
cols <- scales::alpha(c("goldenrod2", "darkorange3", "gold4"), 0.65)

# Shapes by individual or site
shps <- c(21, 23, 24)

# One individual added at a time
tmp_df1 <- mnk_inv %>%
  filter(ids %in% c("ELEM")) %>%
  droplevels() 

tmp_df2 <- mnk_inv %>%
  filter(ids %in% c("ELEM", "INTR")) %>%
  droplevels() 

# Convex hull polygons by species, range, site
hulls1 <- plyr::ddply(tmp_df1, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

hulls2 <- plyr::ddply(tmp_df2, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

hulls3 <- plyr::ddply(mnk_inv, "ids", function(x){
  x[chull(x$X, x$Y), ]
})

# One individual added at a time
gg1 <- tmp_df1 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls1, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids, shape = ids), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y", scales = "fixed") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-25, 24)) +
  scale_y_continuous(limits = c(-20, 25)) +
  theme_bw() +
  theme_AcousticSpace()

gg1

gg2 <- tmp_df2 %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls2, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids, shape = ids), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-25, 24)) +
  scale_y_continuous(limits = c(-20, 25)) +
  theme_bw() +
  theme_AcousticSpace()

gg2


gg3 <- mnk_inv %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls3, aes(x = X, y = Y, fill = ids, color = ids), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = ids, color = ids, shape = ids), size = 2.5, stroke = 0.5) +
  facet_grid(cols = vars(spp_range), switch = "y") +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "", nrow = 1, byrow = TRUE), shape = guide_legend(title = "", nrow = 1, byrow = TRUE), fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
  scale_x_continuous(limits = c(-25, 24)) +
  scale_y_continuous(limits = c(-20, 25)) +
  theme_bw() +
  theme_AcousticSpace()

gg3

# Color strip labels by range per visual
g1 <- ggplot_gtable(ggplot_build(gg1))
stripr <- which(grepl('strip-t', g1$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g1$grobs[[i]]$grobs[[1]]$childrenOrder))
  g1$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g2 <- ggplot_gtable(ggplot_build(gg2))
stripr <- which(grepl('strip-t', g2$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g2$grobs[[i]]$grobs[[1]]$childrenOrder))
  g2$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()

g3 <- ggplot_gtable(ggplot_build(gg3))
stripr <- which(grepl('strip-t', g3$layout$name)) # strip-l for left strips, strip-t for upper
fills <- alpha("orange", 0.45)
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g3$grobs[[i]]$grobs[[1]]$childrenOrder))
  g3$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
dev.off()


tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Invasive_SiteScale_01.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g1)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Invasive_SiteScale_02.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g2)
dev.off()

tiff(file.path(twt_path, "TwitterTO_SPCC_tSNE_Invasive_SiteScale_03.tiff"), units = "in", width = 5.10, height = 4.5, res = 300) 
grid.draw(g3)
dev.off()

```


# Spectrograms for Twitter TO lexicons, invasive range only

I used the defense talk lexicons for native range social scales for Twitter Takeover visuals. here made spectrograms for invasive range individual and site scale. Individual scale calls for the 3 individuals from Austin 2019: UM7, UM16, UM9, and calls for sites ELEM, INTR, MART.  

As for the lexicon I made for the defense, I added colored borders in LibreOffice after resizing spectrograms.
```{echo = TRUE, eval = FALSE}

nat_inv_est %>%
  as_tibble() %>%
  filter(social_scale == "Individual") %>%
  filter(range == "Invasive" & invasive_city == "Austin") %>%
  distinct(site, year, Bird_ID)

indiv_calls <- nat_inv_est %>%
  as_tibble() %>%
  filter(social_scale == "Individual") %>%
  filter(Bird_ID %in% c("INV-UM7", "INV-UM16", "INV-UM10")) %>%
  droplevels() %>%
  dplyr::select(sound.files, Bird_ID)

head(indiv_calls)

# Sound files by individual
indiv_calls %>%
  View()

# Filter the full EST by these calls
tmp_est <- nat_inv_est[grep(paste(paste("^", indiv_calls$sound.files, "$", sep = ""), collapse = "|"), nat_inv_est$sound.files), ]
nrow(tmp_est)
class(tmp_est)

# Make spectrograms with axis labels, inner.mar helps cut out the axis titles
specreator(tmp_est, flim = c(1, 8), ovlp = 90, mar = 0.01, res = 300, path = gpath, osci = FALSE, parallel = cores, line = FALSE, title.labels = NULL, axisX = FALSE, axisY = FALSE, wl = 378, inner.mar = c(0, 0, 0, 0))
# inner.mar = c(2, 2, 0.5, 0) # if axis text not desired, note that the font size scales very poorly

# Resize the image files to be used for the lexicon
# In order per individual from top to bottom
imgs <- c(
  # UM7
  "2019_08_06_ELEM_GSV1030_10.WAV",
  "2019_08_06_ELEM_GSV1030_15.WAV",
  "2019_08_06_ELEM_GSV1030_16.WAV",
  "2019_08_06_ELEM_GSV1030_26.WAV",
  # UM16
  "2019_08_09_FIEL_GSV1088_8.WAV",
  "2019_08_09_FIEL_GSV1088_9.WAV",
  "2019_08_09_FIEL_GSV1088_10.WAV",
  "2019_08_09_FIEL_GSV1088_11.WAV",
  # UM10
  "2019_08_08_INTR_1091_6.WAV",
  "2019_08_08_INTR_1091_7.WAV",
  "2019_08_08_INTR_1091_8.WAV",
  "2019_08_08_INTR_1090_6.WAV"v
  )

# Resize images to 430 pixels wide by 285 pixels high, ignore aspect ratio
# Leaves enough space for adding a colored border around each image file
invisible(pblapply(1:length(imgs), function(i){
  
  img <- image_read(file.path(gpath, paste(imgs[i], "-1.jpeg", sep = "")))
  image_write(image_scale(img, geometry = "435x300!"), path = file.path(gpath, paste(imgs[i], "sm.jpeg", sep = "_")))
  
}))

# Site scale calls
site_calls <- nat_inv_est %>%
  as_tibble() %>%
  filter(social_scale == "Site") %>%
  filter(site_year %in% c("ELEM_2019", "INTR_2019", "MART_2019")) %>%
  # Filter by highest quality
  filter(Visual_quality_score == "H") %>%
  droplevels() %>%
  pull(sound.files)
  
head(site_calls)

# Filter the full EST by these calls
tmp_est <- nat_inv_est[grep(paste(paste("^", site_calls, "$", sep = ""), collapse = "|"), nat_inv_est$sound.files), ]
nrow(tmp_est)
class(tmp_est)

# Make spectrograms with axis labels, inner.mar helps cut out the axis titles
specreator(tmp_est, flim = c(1, 8), ovlp = 90, mar = 0.01, res = 300, path = gpath, osci = FALSE, parallel = cores, line = FALSE, title.labels = NULL, axisX = FALSE, axisY = FALSE, inner.mar = c(0, 0, 0, 0), wl = 378)

imgs <- c(
  "2019_08_06_ELEM_GSV1033_7.WAV",
  "2019_08_06_ELEM_GSV1024_8.WAV",
  "2019_08_06_ELEM_GSV1024_11.WAV",
  "2019_08_06_ELEM_GSV1029_3.WAV",
  "2019_08_08_INTR_1080_5.WAV",
  "2019_08_08_INTR_1088_2.WAV",
  "2019_08_08_INTR_1094_21.WAV",
  "2019_08_08_INTR_1094_33.WAV",
  "2019_08_10_MART_1142_1.WAV",
  "2019_08_10_MART_1147_2.WAV",
  "2019_08_10_MART_1161_6.WAV",
  "2019_08_10_MART_1163_1.WAV"
 )

# Resize images to 430 pixels wide by 285 pixels high, ignore aspect ratio
# Leaves enough space for adding a colored border around each image file
invisible(pblapply(1:length(imgs), function(i){
  
  img <- image_read(file.path(gpath, paste(imgs[i], "-1.jpeg", sep = "")))
  image_write(image_scale(img, geometry = "435x300!"), path = file.path(gpath, paste(imgs[i], "sm.jpeg", sep = "_")))
  
}))

```

Used the magick package to make a GIF after adding these acoustic space plots to lexicons
```{r echo = TRUE, echo = TRUE}

#################################
# Native range, individual scale

# List file names and read in
imgs <- list.files(twt_path, pattern = "TwitterTO_Native_IndivScale_LexiconTraitSpace", full.names = TRUE)
img_list <- lapply(imgs, image_read)

# Join images and add the last image twice so that it stays on longer
img_joined <- image_join(img_list, img_list[[length(img_list)]])

# Animate at 1 frames per second
img_animated <- image_animate(img_joined, fps = 1)

# View animated image
# img_animated

# Save to disk
image_write(image = img_animated,
            path = file.path(twt_path, "NativeRange_IndivScale.gif"))


#################################
# Native range, site scale

# List file names and read in
imgs <- list.files(twt_path, pattern = "TwitterTO_Native_SiteScale_LexiconTraitSpace", full.names = TRUE)
img_list <- lapply(imgs, image_read)

# Join images and add the last image twice so that it stays on longer
img_joined <- image_join(img_list, img_list[[length(img_list)]])

# Animate at 1 frames per second
img_animated <- image_animate(img_joined, fps = 1)

# View animated image
# img_animated

# Save to disk
image_write(image = img_animated,
            path = file.path(twt_path, "NativeRange_SiteScale.gif"))

#################################
# Invasive range, individual scale

# List file names and read in
imgs <- list.files(twt_path, pattern = "TwitterTO_Invasive_IndivScale_LexiconTraitSpace", full.names = TRUE)
img_list <- lapply(imgs, image_read)

# Join images and add the last image twice so that it stays on longer
img_joined <- image_join(img_list, img_list[[length(img_list)]])

# Animate at 1 frames per second
img_animated <- image_animate(img_joined, fps = 1)

# View animated image
# img_animated

# Save to disk
image_write(image = img_animated,
            path = file.path(twt_path, "InvasiveRange_IndivScale.gif"))


#################################
# Invasive range, site scale

# List file names and read in
imgs <- list.files(twt_path, pattern = "TwitterTO_Invasive_SiteScale_LexiconTraitSpace", full.names = TRUE)
img_list <- lapply(imgs, image_read)

# Join images and add the last image twice so that it stays on longer
img_joined <- image_join(img_list, img_list[[length(img_list)]])

# Animate at 1 frames per second
img_animated <- image_animate(img_joined, fps = 1)

# View animated image
# img_animated

# Save to disk
image_write(image = img_animated,
            path = file.path(twt_path, "InvasiveRange_SiteScale.gif"))


#################################
# Conceptual visual, FM

# List file names and read in
imgs <- list.files(twt_path, pattern = "ConceptualVisual_FM", full.names = TRUE)
imgs

img_list <- lapply(imgs, image_read)

# Join images and add the last image twice so that it stays on longer
img_joined <- image_join(img_list, img_list[[length(img_list)]])

# Animate at 1 frames per second
img_animated <- image_animate(img_joined, fps = 1)

# View animated image
# img_animated

# Save to disk
image_write(image = img_animated,
            path = file.path(twt_path, "ConceptualVisual_FM.gif"))


#################################
# RF acoustic space and FM visual

# List file names and read in
imgs <- list.files(twt_path, pattern = "RFKernelDensity_FreqMod", full.names = TRUE)
imgs

img_list <- lapply(imgs, image_read)

# Join images and add the last image twice so that it stays on longer
img_joined <- image_join(img_list, img_list[[length(img_list)]])

# Animate at 1 frames per second
img_animated <- image_animate(img_joined, fps = 1)

# View animated image
# img_animated

# Save to disk
image_write(image = img_animated,
            path = file.path(twt_path, "RFKernelDensity_FreqMod.gif"))

```

Dynamic spectrograms, Marcelo's new package dynaSpec.
```{r echo = TRUE, eval = TRUE}

?scrolling_spectro

wav_nm <- "/media/owner/MYIOPSITTA/R/Uruguay2017_MonkParakeet_CallAnalysis/Data/Site_Recordings/2017_07_28_ECIL-02_1181.WAV"

wav <- readWave(wav_nm, from = 2.8, to = 4.5, units = "seconds")
wav

scrolling_spectro(wav, file.name = file.path(twt_path, "2017_07_28_ECIL-02_1181_scrollSpectro.mp4"), flim = c(1, 6), collevels = seq(-40, 0, 5), ovlp = 90, colbg = "black", pal = magma, lower.spectro = FALSE, grid = FALSE, axis.type = "none", loop = 1, buffer = 0)

wav <- readWave(wav_nm, from = 2.8, to = 4.5, units = "seconds")
wav

scrolling_spectro(wav, file.name = file.path(twt_path, "2017_07_28_ECIL-02_1181_scrollSpectro_quarterSpeed.mp4"), flim = c(1, 6), collevels = seq(-40, 0, 5), ovlp = 90, colbg = "black", pal = magma, lower.spectro = FALSE, grid = FALSE, axis.type = "none", loop = 1, speed = 0.25, buffer = 0)

```


######################################

Sampling maps for defense and other talks.

Native and invasive range sampling. This code needs to be updated (see scalebar code below)
```{r echo = TRUE, eval = FALSE}

# Make western hemisphere vocal sampling map with state/country polygons filled in,

n <- 12
states <- map_data("state") %>%
  filter(region %in% c("texas", "louisiana", "florida", "connecticut"))
str(states)

ury <- map_data("world") %>%
  filter(region %in% c("Uruguay"))
str(ury)

world <- map_data("world")

gg_wrld <- ggplot() +
  geom_polygon(data = world, aes(x = long, y = lat, group = group), fill = "gray65") +
  geom_polygon(data = states, aes(x = long, y = lat, group = group), fill = heat.colors(n)[5]) +
  geom_polygon(data = ury, aes(x = long, y = lat, group = group), fill = topo.colors(n)[2]) +
  xlab("Longitude (Decimal Degrees)") + ylab("Latitude (Decimal Degrees)") +
  theme_classic() +
  theme(axis.title = element_text(size = 18), axis.text = element_text(size = 14)) +
  coord_cartesian(xlim = c(-170, -30))

gg_wrld <- gg_wrld +
  scalebar(x.min = -150, x.max = -100, y.min = -50, y.max = -20, dist = 1500, dd2km = TRUE, model = "WGS84", height = 0.15, st.size = 2.5, st.dist = 0.15)

# gg_wrld

buf <- 0.1
symbol <- 1
symbol <- sprintf("%02.f", symbol)
symbol <- readPNG(paste0(system.file("symbols", package = "ggsn"), 
                         "/", symbol, ".png"))
symbol <- rasterGrob(symbol, interpolate = TRUE)
gg_wrld <- gg_wrld + annotation_custom(grob = symbol, xmin = -114, xmax = -124, 
                                       ymin = -30, ymax = -10)

gg_wrld

ggsave(file.path(gpath, "CulturalEvo_Map.jpeg"), units = "cm", width = 10, height = 14, dpi = 200) 


```

Native range sampling only.
```{r echo = TRUE, eval = FALSE}

n <- 12

ury <- map_data("world") %>%
  filter(region %in% c("Uruguay"))
str(ury)

world <- map_data("world")

gg_wrld <- ggplot() +
  geom_polygon(data = world, aes(x = long, y = lat, group = group), fill = "gray65") +
  geom_polygon(data = ury, aes(x = long, y = lat, group = group), fill = "navy") +
  xlab("Longitude (Decimal Degrees)") + ylab("Latitude (Decimal Degrees)") +
  coord_cartesian(xlim = c(-90, -35), ylim = c(-50, 20)) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14), 
    axis.text = element_text(size = 12),
    panel.border = element_rect(size = 0.75),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) 

# gg_wrld

gg_wrld <- gg_wrld +
  scalebar(x.min = -60, x.max = -40, y.min = -45, y.max = -20, dist = 500, model = "WGS84", height = 0.05, st.size = 2.5, st.dist = 0.05, transform = TRUE, dist_unit = "km", border.size = 0.15)

gg_wrld

buf <- 0.1
symbol <- 1
symbol <- sprintf("%02.f", symbol)
symbol <- readPNG(paste0(system.file("symbols", package = "ggsn"), 
                         "/", symbol, ".png"))
symbol <- rasterGrob(symbol, interpolate = TRUE)
gg_wrld <- gg_wrld + annotation_custom(grob = symbol, xmin = -50, xmax = -40, 
                                       ymin = -40, ymax = -35)

gg_wrld

ggsave(file.path(gpath, "NativeRangeVocal_SamplingMap.jpeg"), units = "in", width = 3.5, height = 5, dpi = 200) 


```

