---
title: "Spectrogram figures"
output: html_document
date: "2025-02-14"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{r}

# install.packages("magick")
# install.packages("seewave")
# install.packages("tuneR")

library(tidyverse)
library(seewave)
library(tuneR)
library(magick)

```

Step 0: Check out the spectrograms generated using the warbleR package for all synthetic calls for paRsynth, and choose the audio file names that way. Drag the audio files to a new folder, and these files should be the only ones used for pub quality spectrograms.

Step 1: Figure out for which audio files we want to make spectrograms.

```{r}

# 4 example audio files saved in a folder called "tmp" on the Desktop
audio_path <- "/Users/gsvidaurre/Desktop/tmp"

wavs <- list.files(path = audio_path, pattern = ".wav$")

# Check out wavs, looks good
glimpse(wavs)

wavs

# Individual 10 in group 5: two calls
# [1] "IndividualIdentity_Group5_Indiv10_Call4.wav"
# [2] "IndividualIdentity_Group5_Indiv10_Call5.wav"

# Individual 9 in group 5: two calls
# [3] "IndividualIdentity_Group5_Indiv9_Call4.wav" 
# [4] "IndividualIdentity_Group5_Indiv9_Call5.wav" 

```

Step 2: Generate spectrograms for these audio files using ggplot (the function ggspectro()).
```{r}

# ?ggspectro

# Iterate over audio files (vocalizations) to generate 1 spectrogram and image file per vocalization
?lapply

# X is a vector of numbers that controls how many times the loop will iterate. In each iteration, the iterating variable will take on 1 value from X
# 1:length(wavs)

# FUN is a function that will be applied to each element of X
# FUN can be set to an existing function in R, like is.numeric()
# But you can also write your own function for the FUN argument, and the code for a custom function needs to sit inside the curly brackets
# To troubleshoot a function inside of a loop, or to understand it, you should freeze the loop in time by setting the iterating variable to a single iteration. For instance, if I set w to 1, then I can run the code inside of the curly brackets and see the behavior of the function in the first iteration
w <- 1 # freeze the loop in the first iteration

# Set the color palette
gray_colors <- reverse.gray.colors.2(12)

lapply(X = 1:length(wavs), FUN = function(w){
  
  # Read in the audio file, returns a Wave object
  tmp_wav <- tuneR::readWave(file.path(audio_path, wavs[w]))
  # str(tmp_wav)
  
  # Use ggspectro to generate a spectrogram
  # These spectrograms look funny
  gg <- ggspectro(wave = tmp_wav, f = tmp_wav@samp.rate, ovlp = 90) +
    
    # Plot amplitude values or cells in the spectrogram
    geom_raster(aes(fill = amplitude, hjust = 0, vjust = 0, interpolate = TRUE)) +
    
    # Control the x-axis aesthetics
    scale_x_continuous(limits = c(0.1, 0.8), breaks = seq(0.1, 0.8, 0.2), labels = seq(0.1, 0.8, 0.2)) +
    
    # Control the y-axis aesthetics
    scale_y_continuous(limits = c(0, 16), breaks = seq(0, 16, 2), labels = seq(0, 16, 2)) +
    
    # We want spectrograms to be in grayscale
    # Change the values of limits to change how colors are assigned across amplitude bins
    scale_fill_gradientn(colours = gray_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-30, 0))
  
})

```


Step 3: Add colored borders around the spectrogram image files.