---
title: "ConceptualFigure_FrequencyAnchors"
author: Grace Smith-Vidaurre, Brittany Coppinger
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Purpose: This script uses the synthetic call metadata to create a conceptual graphic of frequency anchors for the paRsynth pipeline. This figure is used for talks and potentially for the manuscript.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, messsage = FALSE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "tidyverse", "data.table", "gganimate")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

```

```{r load packages, eval = FALSE}

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE, verbose = FALSE))

```

```{r load packages in background, include = FALSE}

# The only solution right now to avoid having a whole bunch of verbose output printed from the chunk above
# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE, verbose = FALSE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "C:/Users/britt/Desktop" # Britt's path
path <- "/Users/summe/OneDrive/Desktop" #Summer's path

# Initialize a path for the local GitHub repo for this manuscript, for saving final figures here
# git_path <- "C:/Users/britt/Documents/GitHub" # Britt's path
# git_path <- "/Users/gracesmith-vidaurre/Desktop/GitHub_repos"
git_path <- "/Users/summe/OneDrive/Desktop/github_repo" #Summer's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

```

Read in the synthetic call metadata.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))
glimpse(synthetic_call_metadata)

```

Choose a single call for talk slides: get the character string and also the vector of frequency anchors.
```{r}

# Choose the first call in this dataset (Group 1, Individual 1, Call 1)
filt_data <- synthetic_call_metadata %>% 
  slice(1)

glimpse(filt_data)

# Call string
filt_data$Call

# [1] "CABCAABACCBCCBAA"

# Frequency anchors are in columns, pull these out as a vector
freq_cols <- filt_data %>%
  # Select only the columns that start with the pattern "Frequency"
  select(names(.)[grep("^Frequency", names(.))])

glimpse(freq_cols)

# We need to transpose this data frame so that all of the frequency values are in rows not columns, and then we need to convert the resulting matrix to a vector
frequency_anchors <- as.vector(t(freq_cols))

# Looks good
frequency_anchors
length(frequency_anchors)

```

Make a conceptual graphic showing how the frequency values produced from the paRsynth pipeline pipeline serve as frequency modulation "anchors" for soundgen to generate synthetic audio files. This be a line graph of the frequency anchors above.
```{r}

# Create a data frame of the frequency anchors plus timestamps
freq_anchors <- data.frame(
  freq_anchors = frequency_anchors,
  # The timestamps should be evenly spaced across the duration of the call, which is the soundgen default
  # We generated calls in the first script that had 200 ms duration
  time = round(seq(0, 0.2, 0.2/(length(frequency_anchors) - 1)), 3)
)

# X-axis is time, y-axis is frequency
glimpse(freq_anchors)

# Make a graphic of the frequency anchors plus a line through them
Freq_anch_plot <-  ggplot(freq_anchors, aes(x = time, y = freq_anchors/1000)) +
  # geom_line(color = scales::alpha("#A8CDECFF"), linetype = "dotted", linewidth = 2) +
  geom_line(color = "grey24", linetype = "dotted", linewidth = 2) +
  # Turn on the line below for the animation of the graph, turn off for the static version
  # geom_point(aes(group = seq_along(time)), shape = 21, size = 8, color = scales::alpha("#F6955EFF")) +
  # Turn on the line below for the static graph image, turn off for animated version
  # geom_point(size = 5, color = scales::alpha("#F6955EFF")) +
  geom_point(size = 2.5, shape = 21, color = "black", fill = "white") +
  xlab("Time (s)") +
  ylab("Frequency (kHz)") +
  scale_y_continuous(limits = c(0, 7)) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    # axis.title = element_text(size = 16),
    axis.text = element_text(size = 16),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  ) # +
  # The line below animates the plot, turn off for static image (make sure to remove the + from the line above too!)
  # gganimate::transition_reveal(time)

# We will use this image file and it may need to be resized
# use the ggsave line to save the static plot, as the anim_save line to save the animated plot
# this sizing is for use in a powerpoint presentation
# ggsave(file.path(figure_path, "Concept_FreqAnch.tiff"), units = "in", width = 5, height = 4.6, dpi = 600)
# This sizing is being used by Summer for creation of manuscript figure
ggsave(file.path(figure_path, "Concept_FreqAnch.tiff"), units = "in", width = 6, height = 5, dpi = 600)
# gganimate::animate(Freq_anch_plot, units = "in", height = 4.6, width = 4.6, res = 150)
# gganimate::anim_save(file.path(figure_path, "Concept_FreqAnch_GIF.gif"))


# resizing for thumbnail
Freq_anch_plot <-  ggplot(freq_anchors, aes(x = time, y = freq_anchors/1000)) +
  geom_line(color = scales::alpha("#A8CDECFF"), linetype = "dotted", linewidth = .8) +
  # Turn on the line below for the animation of the graph, turn off for the static version
  # geom_point(aes(group = seq_along(time)), size = 1.25, color = scales::alpha("#F6955EFF")) +
  # Turn on the line below for the static graph image, turn off for animated version
  geom_point(size = 5, color = scales::alpha("#F6955EFF")) +
  xlab("Time (s)") +
  ylab("Frequency (kHz)") +
  scale_y_continuous(limits = c(0, 7)) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    # axis.title = element_text(size = 16),
    axis.text = element_text(size = 8),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  ) # +
  # The line below animates the plot, turn off for static image (make sure to remove the + from the line above too!)
  # gganimate::transition_reveal(time)

# resizing for small thumbnail
# gganimate::animate(Freq_anch_plot, units = "in", height = 2, width = 2.1, res = 300)
# gganimate::anim_save(file.path(figure_path, "Concept_FreqAnch_GIF_thumbnail.gif"))

```