---
title: "Information Encoding Experiments"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "2024-07-08"
---

Purpose: The following code was designed to test the behavior of functions written to generate synthetic vocalizations that emphasize either individual identity or group membership information. These functions written by Ari generate individually distinctive or group-specific character strings that are converted to Parson's code and then audio files of frequency-modulated vocalizations using the `soundgen` package. The loops below iterate over varying ratios of how much of the initial character string is allocated to shared group membership versus unique individual identity. The output of each loop is the normalized mutual information (NMI) calculated between the original classes at both the individual and group levels compared to cluster labels obtained from k-means clustering on multidimensional scaling variables generated from a spectrographic cross-correlation (SPCC) matrix. 

The NMI calculations will allow us to address how much information about group membership versus individual identity is contained in patterns of acoustic variation across call datasets generated to emphasize either individual identity or group membership. For instance, when creating datasets of vocalizations that are more individually distinctive and less group-specific, the NMI for the individual-level should be high but low for the group-level, because patterns of acoustic variation should contain a lot of information about individual identity but less about individuals' group membership. Given that all calls contain individual identity and group membership information, we should also see some interesting patterns at intermediate ratios of the string allocated to individual identity versus group membership.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "aricode", "Rmisc", "warbleR")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# TKTK we will not use the package installation for now, instead directly source the paRsynth functions from the GitHub repo
# TKTK once we start using the package again in package format, we need to add paRsynth:: before eeach function
# Install the paRsynth package from GitHub if you haven't installed it already
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### MANULLY UPDATE EVERY TIME ##################################

# Initialize a base path (we may need a separate base path per user)
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "" # Brittany's path

###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_synthetic_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){ 
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){ 
  dir.create(figure_path)
}

```

Source the paRsynth functions directly from the GitHub repository. 
```{r}

# Brittany's path should include "GitHub/paRsynth"
repo_path <- "~/Desktop/R_packages/paRsynth/R" # Grace's path
# repo_path <- "~/Desktop/GitHub_repos/paRsynth/R"

# Get all of the R files for each function in this directory
function_files <- list.files(repo_path, pattern = ".R$", full.names = TRUE)
function_files

# Iterate over these files to load each function, and silence the output
invisible(sapply(X = function_files, FUN = source))

```

Check out documentation for the paRsynth functions. These functions are written below in the order in which they should be used. TKTK this will only work when paRsynth is installed as a package 
```{r eval = FALSE}

# ?paRsynth::generate_strings
# ?paRsynth::parsons_code
# ?paRsynth::frequency_anchors
# ?paRsynth::write_audio

```

In the code below, I handled negative SPCC values by setting these to the minimum observed non-zero SPCC value in the whole matrix. I handled values of 1 off of the diagonal by setting these to the maximum observed value less than 1 in the full matrix.

TKTK need to add an edit distance analysis!! To the NMI, for "true" information recovery at the string step compared to the bioacoustics signal step


TKTK also add your own function to calculate NMI following Kershenbaum et al. 2013 in PLOS One.

```{r}

X <- data.frame(classes = rep(seq(1, 5, 1), each = 2), clusters = rep(seq(1, 5, 1), each = 2))
X

class_col_nm <- "classes"
cluster_col_nm <- "clusters"

i <- 1
j <- 3

nmi <- function(X, class_col_nm, cluster_col_nm){
  
  classes <- unique(X[[class_col_nm]])
  clusters <- unique(X[[cluster_col_nm]])
  
  # n_i is the number of vocalizations from class (individual or group) i
  # n_j is the number of vocalizations in cluster j
  # n_ji is the number of vocalizations from individual i in cluster j
  # N is the number of total vocalizations
  
  # sum over j and i [ n_ji * log( (N * n_ji) / (n_j * n_i) ) ] / sqrt( sum over j [ n_j * log( n_j / N )] * sum over i [ n_i * log( n_i / N ) ] )
  
  # Get the total number of vocalizations
  N <- nrow(X)
  
  numerator <- sum(unlist(lapply(1:length(classes), function(i){
    
    lapply(1:length(clusters), function(j){
      
      # Get the number of vocalizations from class i
      n_i <- X %>% 
        dplyr::filter(!!sym(class_col_nm) == classes[i]) %>%
        nrow(.)
      
      # Get the number of vocalizations from cluster j
      n_j <- X %>% 
        dplyr::filter(!!sym(cluster_col_nm) == clusters[j]) %>% 
        nrow(.)
      
      # Get the number of vocalizations from class i that are in cluster j
      n_ji <- X %>% 
        dplyr::filter(!!sym(class_col_nm) == classes[i]) %>% 
        dplyr::filter(!!sym(cluster_col_nm) == clusters[j]) %>% 
        nrow(.)
      
      numerators <- n_ji * log( (N * n_ji) / (n_j * n_i) )
      
      # Set the calculation to 0 if the calculation above leads to an NaN value, which happens when n_ji is 0
      if(is.na(numerators)) numerators <- 0
      
      return(numerators)
      
    })
    
  })))
  
  
  # Calculate information in clusters and classes separately (each half of the denominator that goes into the square root expression)
  sum_clusters <- sum(unlist(lapply(1:length(clusters), function(j){
    
    # Get the number of vocalizations from cluster j
    n_j <- X %>% 
      dplyr::filter(!!sym(cluster_col_nm) == clusters[j]) %>% 
      nrow(.)
    
    return( n_j * log( n_j / N ) )
    
  })))
  
  sum_classes <- sum(unlist(lapply(1:length(classes), function(i){
    
    # Get the number of vocalizations from class i
    n_i <- X %>% 
      dplyr::filter(!!sym(class_col_nm) == classes[i]) %>% 
      nrow(.)
    
    return( n_i * log( n_i / N ) )
    
  })))
  
  denominator <- sqrt( sum_clusters * sum_classes )
  
  return( numerator / denominator )  
  
}

# TKTK I'm getting a value of 2 but I should be getting 1

```



# Synthetic experiments over varying social environment characteristics and information encoding rules

How well can we recover the information that was originally encoded over two social levels? Here we generate synthetic vocal identity signals over varying social environment characteristics and information encoding rules. Then we use traditional bioacoustics tools and Normalized Mutual Information to decode information encoded at the group and individual levels.

Iterate over each treatment a number of times so that we can calculate a 95% confidence interval around each NMI calculation. Update the loop so that a selection table is made and SPCC is performed each time a new call dataset is generated. Then save the selection table and SPCC matrix but remove audio files before initiating the subsequent iteration. The duration of the audio files impacts the computational time (files over 400 ms take a long time to generate). The number of calls that will be compared in SPCC also increases computational time, as well as the number of treatments and the number of iterations per treatment.
```{r}

#################### Social environment treatments #################### 

# Initialize varying values of the number of groups and individuals. Here, each group size and number of individuals will travel together per treatment to create 3 social environment treatments (few individuals, dozens of individuals, many individuals)
social_envts <- c("Sparse", "Intermediate", "Dense")
n_groups <- c(2, 8, 16)
n_individuals <- c(2, 8, 16)

# Keep the number of calls per individual constant across iterations
n_calls <- 2

# Check the total number of call comparisons in the largest social environment treatment, which will need to run 5 times (one per information encoding treatment)
# Here the total number of calls is 512
(max(n_groups) * max(n_individuals) ) * n_calls


#################### Information encoding treatments #################### 

# Ratios of group : individual information in a string
# Here these ratios are written as proportions from 0 to 1, such that 0 indicates 0:1 (no group membership and all individual information), and 1 indicates 1:0 (all group membership information)
# ratios <- c(0, 0.2, 0.4, 0.8, 1)
ratios <- c(0.2, 0.4, 0.8) # fewer social conditions for preliminary results

# The total length of the individual and group information together should be constant across strings
encoding_length <- 30

# Check the string lengths that will be assigned to group and individual information across the ratios above
information <- data.table::rbindlist(lapply(1:length(ratios), function(i){
  
  if(ratios[i] < 1){
    
    group_information <- ratios[i] * encoding_length
    
  } else {
    
    group_information <- encoding_length / ratios[i]
    
  }
  
  individual_information <- encoding_length - group_information
  
  return(
    data.frame(
      group_information = group_information,
      individual_information = individual_information
    )
  )
  
}))

information

# The length of the global header and tail should be the same across strings
globals <- 12 # 6 characters for the global head, 6 for the global tail

# Create variation within individuals, and this will be the same across strings
random_variation <- 6

# Initialize the total string length
string_length <- (globals + encoding_length + random_variation)
string_length # 46

# Initialize the number of iterations for each combination of information encoding and social environment treatments (15 total treatments)
# iteratns <- 5
iteratns <- 1 # fewer iterations for preliminary results

# Testing one iteration of each loop
# z <- 3 # social environments
# i <- 1 # information encoding treatments
# n <- 1 # replicates or iterations

# Iterate over the social environment and information encoding treatments to assess how well the original information encoded about group and individual identity can be recovered across these treatments.

system.time(
  
  # Iterate over social environment treatments
  invisible(pblapply(1:length(social_envts), function(z){
    
    # Iterate over information encoding treatments
    lapply(1:length(ratios), function(i){
      
      cat(paste("social condition =", social_envts[z], "\n", sep = " "))
      cat(paste("ratio = ", ratios[i], "\n", sep = ""))
      
      # Iterating over the number of replicates per treatment combination
      nmi_res_tmp <- data.table::rbindlist(lapply(1:iteratns, function(n){
        
        ### Step 1: Generate the string for each call
        calls <- suppressMessages(
          generate_strings(
            n_groups = n_groups[z], 
            n_individuals = n_individuals[z], 
            n_calls = n_calls, 
            string_length = string_length, 
            group_information = information[["group_information"]][i], 
            individual_information = information[["individual_information"]][i],
            random_variation = random_variation
          )
        )
        
        # glimpse(calls)
        
        ### Step 2: Convert the strings to Parsons code
        calls_parsons <- parsons_code(
          df = calls, 
          string_col = "Call",
          global_head_col = "Global_head",
          group_head_col = "Group_head", 
          individual_middle_col = "Individual_middle", 
          group_tail_col = "Group_tail", 
          global_tail_col = "Global_tail",
          random_variation_col = "Random_variation",
          mapping = list(A = "up", B = "down", C = "constant")
        )
        
        # glimpse(calls_parsons)
        
        ### Step 3: Convert the Parsons code to frequency values
        calls_parsons_frequencies <- frequency_anchors(
          df = calls_parsons, 
          parsons_col = "Call_Parsons_Code", 
          group_id_col = "Group", 
          individual_id_col = "Individual", 
          call_id_col = "Call_ID", 
          call_string_col = "Call",
          starting_frequency = 4000, 
          frequency_shift = 1000, 
          section_transition = "continuous_trajectory"
        )
        
        # glimpse(calls_parsons_frequencies)
        
        # ### Step 4: Select a single call per individual to reduce computational time
        # calls_parsons_frequencies_filt <- calls_parsons_frequencies %>% 
        #   group_by(Group, Individual) %>% 
        #   dplyr::slice_sample(n = 1) %>% 
        #   ungroup()
        
        # glimpse(calls_parsons_frequencies_filt)
        
        ### Step 4: For each call or string, use these frequency vectors to generate synthetic audio files with paRsynth and the soundgen package
        
        synthetic_call_metadata <- write_audio(
          df = calls_parsons_frequencies, 
          save_path = data_path, 
          sampling_rate = 44100,
          sylLen = 400,
          temperature = 0,
          prefix = paste(social_envts[z], paste("Ratio", ratios[i], sep = "-"), sep = "_"),
          invalidArgAction = "ignore" # This argument fixes the variable sampling rates that soundgen assigns in the background
        )
        
        # glimpse(synthetic_call_metadata)
        
        wavs <- list.files(
          path = data_path, 
          pattern = paste(paste(social_envts[z], paste("Ratio", ratios[i], sep = "-"), sep = "_"), "_", sep = "")
        )
        
        cat(paste("Number of audio files = ", length(wavs), "\n"))
        
        # Information recovery pipeline with traditional bioacoustics tools
        
        ### Step 5: Generate a selection table for the warbleR package
        # w <- 1 # testing
        
        sel_tbl <- data.table::rbindlist(lapply(1:length(wavs), function(w){
          
          # Read in the given audio file
          tmp <- tuneR::readWave(file.path(data_path, wavs[w]))
          
          # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
          metadats_tmp <- synthetic_call_metadata %>%
            dplyr::filter(grepl(wavs[w], audio_file_name))
          
          # glimpse(metadats_tmp)
          
          # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
          if(nrow(metadats_tmp) > 0){
            
            # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
            # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
            res <- data.frame(
              sound.files = wavs[w], 
              selec = 1,
              start = 0.1, 
              end = seewave::duration(tmp) - 0.1,
              duration = seewave::duration(tmp),
              group_ID = metadats_tmp[["Group"]],
              individual_ID = metadats_tmp[["Individual"]],
              call_ID = metadats_tmp[["Call_ID"]],
              sampling_rate = tmp@samp.rate,
              group_information = information[["group_information"]][i], 
              individual_information = information[["individual_information"]][i],
              social_envt = social_envts[z],
              information_encoding_ratio = ratios[i]
            )
            
          } else {
            
            res <- data.frame(
              sound.files = wavs[w], 
              selec = 1, 
              start = 0.1, 
              end = seewave::duration(tmp) - 0.1,
              duration = seewave::duration(tmp),
              group_ID = NA,
              individual_ID = NA,
              call_ID = NA,
              sampling_rate = tmp@samp.rate,
              group_information = NA, 
              individual_information = NA,
              social_envt = NA,
              information_encoding_ratio = NA
            )
            
          }
          
          return(res)
          
        }))
        
        # See the selection table in warbleR format with all useful metadata for the synthetic experiment
        # glimpse(sel_tbl)
        
        # And there is now a single sampling rate, as expected
        # unique(sel_tbl$sampling_rate)
        
        # All files should have the same sampling rate, otherwise the analyses below will fail
        if(length(unique(sel_tbl$sampling_rate)) > 1){
          stop("Variable sampling rates detected across synthetic audio files, and downstream analyses will fail")
        }
        
        ### Step 6: Perform SPCC using a default window length and a general bandpass filter
        xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 10), wn = "hanning", cor.method = "pearson", parallel = cores, na.rm = FALSE, type = "spectrogram", path = data_path)
        # str(xc_mat)
        
        # Get the percentage of values that are negative
        neg_values <- ((length(xc_mat[xc_mat < 0])/length(xc_mat))) * 100
        
        # # With the current settings, there are very few call comparisons that have this issue
        # # Which call comparisons lead to the negative values?
        # unlist(lapply(1:nrow(xc_mat), function(i){
        #   lapply(1:ncol(xc_mat), function(j){
        #     
        #     if(xc_mat[i, j] < 0){
        #       return(paste(dimnames(xc_mat)[[1]][i], dimnames(xc_mat)[[2]][j], sep = " - "))
        #     }
        #     
        #   })
        # }))
        
        # These two particular call structures are very different from one another, but the durations are not very different. So I think what's happening is a structural issue, and we could set the negative values to a very low non-negative number, or even change the sign of the negative values if they are very low. If we do this, we should track how many values we changed in each iteration 
        # "Dense_Ratio-0.8_Group16_Indiv8_Call2.wav-1 - Dense_Ratio-0.8_Group12_Indiv5_Call2.wav-1" 
        # xc_mat[xc_mat < 0]
        
        # Set all negative values to the minimum positive value in the SPCC matrix to represent the fact that these calls are very structurally different from one another
        if(neg_values > 0){
          
          # Initialize a record of what was changed to save to the final results
          neg_notes <- paste(round(neg_values, 8), "% of all SPCC cells or", length(xc_mat[xc_mat < 0])/2,"unique comparisons were negative and were changed to the minimum positive SPCC value of", round(min(xc_mat[xc_mat > 0]), 8), sep = " ")
          
          xc_mat[xc_mat < 0] <- round(min(xc_mat[xc_mat > 0]), 8)
          
        } else {
          
          neg_notes <- ""
          
        }
        
        # Continue with downstream analyses only if there are no 1's off of the diagonal, otherwise MDS will fail. Record NA values if there are 1's off of the diagonal (e.g. two calls of the same structure will present values of 1 as if the same call were compared to itself)
        
        # Make sure to calculate the true number of values in the symmetric matrix (multipy the number of unique values that are 1 by 2)
        ones <- ((length(which(xc_mat[lower.tri(xc_mat)] == 1))*2)/length(xc_mat)) * 100
        
        # With the current settings, there are very few call comparisons that have this issue
        # Which call comparisons lead to the values of 1 off of the diagonal?
        # Here a value of 1 pops up for 2 calls of the very same individual, which makes sense
        # [1] "Dense_Ratio-0.2_Group14_Indiv14_Call1.wav-1 - Dense_Ratio-0.2_Group14_Indiv14_Call2.wav-1"
        # [2] "Dense_Ratio-0.2_Group14_Indiv14_Call2.wav-1 - Dense_Ratio-0.2_Group14_Indiv14_Call1.wav-1"
        # unlist(lapply(1:nrow(xc_mat), function(i){
        #   lapply(1:ncol(xc_mat), function(j){
        #     
        #     if(xc_mat[i, j] == 1 & (dimnames(xc_mat)[[1]][i] != dimnames(xc_mat)[[2]][j])){
        #       return(paste(dimnames(xc_mat)[[1]][i], dimnames(xc_mat)[[2]][j], sep = " - "))
        #     }
        #     
        #   })
        # }))
        # 
        
        if(ones > 0){
          
          # Get the maximum similarity value after 1 in the matrix
          sec_max_val <- max(xc_mat[lower.tri(xc_mat)][xc_mat[lower.tri(xc_mat)] != 1])
          
          # Initialize a record of what was changed to save to the final results
          one_notes <- paste(round(ones, 8), "% of all SPCC cells or", length(which(xc_mat[lower.tri(xc_mat)] == 1)), "unique comparisons were negative and were changed to the next maximum SPCC value of", round(sec_max_val, 8), sep = " ")
          
          # Then set the values of 1 off of the diagonal to the next highest similarity value in this matrix
          xc_mat[lower.tri(xc_mat)][xc_mat[lower.tri(xc_mat)] == 1] <- round(sec_max_val, 8)
          
        } else {
          
          one_notes <- ""
          
        }
        
        # Update the dimension names of the matrix
        dimnames(xc_mat) <- list(wavs, wavs)
        
        cat(paste("Dimensions of SPCC matrix = ", dim(xc_mat)[1], dim(xc_mat)[2], "\n"))
        
        cat(paste("NA's in SPCC matrix?", any(is.na(xc_mat)), "\n"))
        
        ### Step 7: Perform MDS
        
        # Convert the SPCC similarity matrix to a distance matrix and dist object for isoMDS
        dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
        
        # str(1 - xc_mat)
        # str(dist_mat)
        
        # Reduce dimensionality of the SPCC matrix using multidimensional scaling (MDS). Use the a different number dimensions in the SPCC matrix per treatment combination in order to reduce the stress of the final solution
        if(social_envts[z] == "Sparse"){
          k <- 4
        } else {
          k <- 20
        }
        
        iso_res <- invisible(MASS::isoMDS(dist_mat, k = k, maxit = 1000, trace = FALSE))
        
        # str(iso_res)
        
        # Make a data frame of the first two MDS dimensions and call metadata
        mds_df <- data.frame(sound.files = dimnames(iso_res$points)[[1]]) %>%
          dplyr::mutate(
            X = iso_res$points[, 1],
            Y = iso_res$points[, 2]
          ) %>%
          inner_join(
            sel_tbl %>%
              dplyr::select(sound.files, group_ID, individual_ID, call_ID),
            by = c("sound.files")
          )
        
        # glimpse(mds_df)
        
        # cat(paste("Dimensions of MDS results = ", dim(mds_df)[1], dim(mds_df)[2], "\n"))
        
        # cat(paste("NA's in MDS X dimension?", any(is.na(mds_df$X)), "\n"))
        
        # cat(paste("NA's in MDS Y dimension?", any(is.na(mds_df$Y)), "\n"))
        
        ### Step 8: Remove .wav files to free up storage space
        rem_files <- file.path(data_path, wavs)
        invisible(file.remove(rem_files))
        
        ### Step 9: Perform clustering and Normalized Mutual Information (NMI) calculation
        # In order to compute NMI at two social levels (individual and group), we need to run clustering at these two levels
        
        ### Group-level clustering and NMI calculation
        
        # Set the number of clusters to the number of unique groups
        num_clusters <- length(unique(mds_df$group_ID))
        
        # Perform k-means clustering with this number of clusters
        # Ensure that the kmeans algorithm uses only the MDS variables, so that it uses information from the patterns of acoustic variation only in order to detect clusters
        kmeans_grp <- kmeans(mds_df[, grep("X|Y", names(mds_df))], centers = num_clusters)
        
        # str(kmeans_grp)
        
        # cat(paste("NA's in group clustering?", any(is.na(kmeans_grp$cluster)), "\n"))
        
        # Compute NMI at the group-level
        orig_classes <- mds_df$group_ID
        nmi_grp <- NMI(orig_classes, kmeans_grp$cluster)
        
        # NMI should be 1 when comparing the same vector to itself, looks good
        # NMI(orig_classes, orig_classes)
        
        NMI(orig_classes, orig_classes[sample(1:length(orig_classes), length(orig_classes), replace = FALSE)]) # group-level random chance is around 0.1
        
        # There two levels of specificity at the individual level. One is individuals is all unique individuals across groups (fine-grained), and the other is all individuals within a group, which will require nested NMI calculations within groups (coarse-grained)
        
        ### Fine-grained individual-level clustering and NMI calculation
        
        # Set the number of clusters to the number of unique individuals across all groups
        num_clusters <- mds_df %>% 
          distinct(paste(group_ID, individual_ID)) %>% 
          nrow()
        
        # num_clusters
        
        # Perform k-means clustering with this number of clusters
        # Ensure that the kmeans algorithm uses only the MDS variables, so that it uses information from the patterns of acoustic variation only in order to detect clusters
        kmeans_ind_fg <- kmeans(mds_df[, grep("X|Y", names(mds_df))], centers = num_clusters)
        
        # cat(paste("NA's in individual clustering?", any(is.na(kmeans_ind_fg$cluster)), "\n"))
        
        # Compute NMI at the individual-level, which means that the original classes are the group plus individual identity
        orig_classes <- as.integer(factor(paste(mds_df$group_ID, mds_df$individual_ID, sep = "-")))
        # head(orig_classes)
        # length(unique(orig_classes)) == num_clusters # looks good
        
        nmi_ind_fg <- NMI(orig_classes, kmeans_ind_fg$cluster)
        # nmi_ind_fg
        
        # TKTK what is the random chance level for NMI? Below it seems that when sorting the orig_classes vector randomly, I get NMI values vvery similar to the values I'm getting above for classifying back to unique individuals in a fine-grained way
        # Add this information to the results somehow? Fine-grined individual-level random chance is around 0.875
        NMI(orig_classes, orig_classes)
        NMI(orig_classes, orig_classes[sample(1:length(orig_classes), length(orig_classes), replace = FALSE)])
        
        
        ### Coarse-grained individual-level clustering and NMI calculation
        
        # Set the number of clusters to the number of unique individuals within each group
        num_clusters <- mds_df %>% 
          distinct(individual_ID) %>% 
          nrow()
        
        # Perform k-means clustering with this number of clusters within each group, so iterate over groups for the NMI calculation
        # n <- 2 # testing
        kmeans_ind_cg <- unlist(lapply(1:n_groups[z], function(n){
          
          tmp <- mds_df[mds_df$group_ID == n, ]
          
          # Checking, looks good
          unique(tmp$group_ID)
          all(tmp$group_ID == n)
          
          # Perform clustering using the MDS coordinates as input
          res <- kmeans(tmp[, grep("X|Y", names(tmp))], centers = num_clusters)
          
          # cat(paste("NA's in individual clustering?", any(is.na(res$cluster)), "\n"))
          
          # Compute NMI at the individual-level, which means that the original classes are the group plus individual identity
          orig_classes <- tmp$individual_ID
          
          # TKTK Coarse-grained individual level random chance is around 0.75
          NMI(orig_classes, orig_classes[sample(1:length(orig_classes), length(orig_classes), replace = FALSE)])
          
          return(NMI(orig_classes, res$cluster))
          
        }))
        
        nmi_results <- data.frame(
          social_envt_treatment = social_envts[z],
          information_encoding_treatment = ratios[i],
          iteration = n,
          group_information = information[["group_information"]][i], 
          individual_information = information[["individual_information"]][i],
          NMI_group = nmi_grp,
          NMI_individual_fine = nmi_ind_fg,
          NMI_individual_coarse_mean = mean(kmeans_ind_cg),
          NMI_individual_coarse_min = min(kmeans_ind_cg),
          NMI_individual_coarse_max = max(kmeans_ind_cg),
          neg_notes = neg_notes,
          one_notes = one_notes
        )
        
        ### Step 10: return NMI results
        return(nmi_results)
        
      }))
      
      ### Step 11: Write out the NMI results for the given treatment combination across iterations
      nmi_res_tmp %>% 
        write.csv(file.path(data_path, paste("NMI_results_", paste(social_envts[z], paste("Ratio", ratios[i], sep = "-"), sep = "_"), ".csv", sep = "")), row.names = FALSE)
      
    })
    
  }))
  
)

# On the Mac Mini this process took ~ 14 minutes with 3 social conditions, 3 information encoding ratios, and 1 iteration of each treatement combination

# On the Mac Mini this process took ~ 29 hours with 3 social conditions, 5 information encoding ratios, and 5 iterations of each treatement combination
# 01d 04h 52m 56s
# user    system   elapsed 
# 40655.65  39141.46 103975.72 

```

How often do the NMI calculations go below 0 or above 1?
```{r}

nmi_files <- list.files(path = data_path, pattern = "NMI_")
nmi_files

nmi_res <- data.table::rbindlist(pblapply(1:length(nmi_files), function(n){
  
  return(read.csv(file.path(data_path, nmi_files[n])))
  
}))

glimpse(nmi_res)

View(nmi_res)

```

```{r}

# Two group-level calculations go below 1
nmi_res %>% 
  dplyr::filter(
    NMI_group < 0
  )

# No other values go below 0 or over 1
nmi_res %>% 
  dplyr::filter(
    NMI_group > 1
  )

nmi_res %>% 
  dplyr::filter(
    NMI_individual < 0
  )


nmi_res %>% 
  dplyr::filter(
    NMI_individual > 1
  )

```


# Plot NMI results....needs to be updated

Generate plots of NMI values at the individual and group-level across the experimental call datasets. I added 95% CIs, but these don't make sense because they vary to go below 0 and above 1. I decided to use the interquartile range (the difference between the upper and lower quartiles) instead.
```{r}

nmi_files <- list.files(path = data_path, pattern = "nmi_")
nmi_files

nmi_res <- data.table::rbindlist(pblapply(1:length(nmi_files), function(n){
  
  return(read.csv(file.path(data_path, nmi_files[n])))
  
}))

glimpse(nmi_res)

# Calculate summary statistics (mean and interquartile range) across iterations
nmi_sum <- nmi_res %>%
  # Pivot longer to add a column by social level
  pivot_longer(
    cols = c("NMI_group", "NMI_individual"),
    names_to = "type",
    values_to = "NMI"
  ) %>%
  dplyr::mutate(
    social_level = type,
    social_level = gsub("NMI_", "", social_level)
  ) %>%
  dplyr::select(-c("type")) %>%
  dplyr::mutate(
    social_level = gsub("g", "G", social_level),
    social_level = gsub("ind", "Ind", social_level)
  ) %>% 
  # Group NMI results by ratio and social_level in order to calculate means and quartiles
  group_by(exptl_ratio, social_level) %>%
  dplyr::reframe(
    mean_nmi = round(mean(NMI), 3),
    Q1 = quantile(NMI, 0.25), # first quartile
    Q3 = quantile(NMI, 0.75) # third quartile
    # ci_lower = round(Rmisc::CI(NMI, ci = 0.95)[["lower"]], 3),
    # ci_upper = round(Rmisc::CI(NMI, ci = 0.95)[["upper"]], 3)
  )

glimpse(nmi_sum)

```

Create plots that represent call datasets at each social level (e.g. more group membership or individual identity information). Use a log-scale axis to spread out the x-axis more evenly.

Plotting aesthetics shared across plots.
```{r}

# Encode the NMI calculations at the two social levels with different linetypes
ltys <- c("dashed", "dotted")

```

More group membership information.
```{r}

# # Create custom underlined text labels for the original ratios for the group-specific call dataset
# parseLabel <- sprintf("underline(%s)",
#                       gsub(" ", "~", nmi_sum %>%
#                              dplyr::filter(
#                                exptl_ratio > 1
#                              ) %>%
#                              dplyr::filter(
#                                social_level == "Group"
#                              ) %>%
#                              dplyr::mutate(
#                                label = paste("Ratio: ", exptl_ratio, sep = "")
#                              ) %>%
#                              pull(label), fixed = TRUE))
# 
# length(parseLabel)

# Plot the data
nmi_sum %>%
  dplyr::filter(
    exptl_ratio > 1
  ) %>%
  ggplot(aes(x = log(exptl_ratio), y = mean_nmi)) +
  geom_line(aes(group = social_level, linetype = social_level), color = "black", linewidth = 1) +
  geom_errorbar(aes(ymin = Q1, ymax = Q3), linetype = "solid", color = "black", width = 0) +
  geom_point(color = "black", size = 3) +
  # geom_text(
  #   data =
  #     nmi_sum %>%
  #     dplyr::filter(
  #       exptl_ratio > 1
  #     ) %>%
  #     dplyr::filter(
  #       social_level == "Group"
  #     ) %>% 
  #     dplyr::mutate(
  #       label = parseLabel
#     ),
#   aes(x = log(exptl_ratio), y = 1.07, label = parseLabel), hjust = 0.5, parse = TRUE, size = 3.5) +
scale_linetype_manual(values = ltys) +
  xlab("Log ratio of group to individual information") +
  ylab("Normalized Mutual Information") +
  guides(linetype = guide_legend(title = "Social level", override.aes = list(linewidth = 1))) +
  ylim(c(0, 1)) +
  theme_bw() +
  theme(
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    legend.title = element_text(size = 24),
    legend.text = element_text(size = 22)
  )

ggsave(file.path(figure_path, "NMI_Results_Group-SpecificDataset.png"), units = "in", width = 8.2, height = 6, dpi = 300)

```

More individual identity information.
```{r}

# # Create custom underlined text labels for the original ratios for the group-specific call dataset
# parseLabel <- sprintf("underline(%s)",
#                       gsub(" ", "~", nmi_sum %>%
#                              dplyr::filter(
#                                exptl_ratio < 1
#                              ) %>%
#                              dplyr::filter(
#                                social_level == "Individual"
#                              ) %>% 
#                              dplyr::mutate(
#                                label = paste("Ratio: ", exptl_ratio, sep = "")
#                              ) %>% 
#                              pull(label), fixed = TRUE))
# 
# length(parseLabel)

# Plot the data
nmi_sum %>%
  dplyr::filter(
    exptl_ratio < 1
  ) %>%
  ggplot(aes(x = log(exptl_ratio), y = mean_nmi)) +
  geom_line(aes(group = social_level, linetype = social_level), linewidth = 1) +
  geom_errorbar(aes(ymin = Q1, ymax = Q3), linetype = "solid", color = "black", width = 0) +
  geom_point(color = "black", size = 3) +
  # geom_text(
  #   data =
  #     nmi_sum %>%
  #     dplyr::filter(
  #       exptl_ratio < 1
  #     ) %>%
  #     dplyr::filter(
  #       social_level == "Individual"
  #     ) %>% 
  #     dplyr::mutate(
  #       label = parseLabel
#     ),
#   aes(x = log(exptl_ratio), y = 1.05, label = parseLabel), hjust = 0.45, parse = TRUE, size = 3) +
scale_linetype_manual(values = ltys) +
  xlab("Log ratio of group to individual information") +
  ylab("Normalized Mutual Information") +
  guides(linetype = guide_legend(title = "Social level", override.aes = list(linewidth = 1))) +
  ylim(c(0, 1)) +
  theme_bw() +
  theme(
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    legend.title = element_text(size = 24),
    legend.text = element_text(size = 22)
  )

ggsave(file.path(figure_path, "NMI_Results_IndividuallyDistinctiveDataset.png"), units = "in", width = 8.2, height = 6, dpi = 300)

```
