---
title: "Information Encoding Experiments - Effect Size Calculations"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "2025-02-26"
---

Purpose: The following code was designed to calculate Cliff's Delta Effect Size for (1) SPCC v Edit distance accuracy measures across all Social Environment x Group Information Proportion X Information Level conditions and (2) Group vs Individual Information level accuracy measures across all Social Environment X Group Information Proportion X Method conditions. Before calculating these effect sizes, we check the distribution of our accuracy measures. They are not normally distributed, so we opt to calculate Cliff's Delta as the effect size.

Effect Sizes are calculated in Steps 3 and 4. This code saves the data table with all the Cliff's Delta values, 95% Confidence Intervals and effect size magnitudes. Magnitude is assessed through the effsize package, which uses thresholds provided in Romano, 2006. (|d|<0.147 "negligible", |d|<0.33 "small", |d|<0.474 "medium", otherwise "large")

These tables will be included in the manuscript and will be called in future figure scripts to plot average effect size values for each type of comparison. 

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# tktk update list
# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "pbapply", "stringdist", "tidyverse",  "data.table", "ggpubr", "effsize")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# TKTK we will not use the package installation for now, instead directly source the paRsynth functions from the GitHub repo
# TKTK once we start using the package again in package format, we need to add paRsynth:: before each function
# Install the paRsynth package from GitHub if you haven't installed it already
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### Manually update in every new coding session ##################################

# Initialize a base path (we may need a separate base path per user)
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
path <- "C:/Users/britt/Desktop" #Brittany's path

###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_synthetic_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){ 
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){ 
  dir.create(figure_path)
}

```

Step 1: Load the data files from the Accuracy Calculations results. These files are the results from the "Experiments_InformationEncoding_Accuracy" script. These need to be manually downloaded from google drive and stored in the data folder first 
```{r}

files <- list.files(path = data_path, pattern = "Accuracy_")
files

res <- data.table::rbindlist(pblapply(1:length(files), function(n){
  
  return(read.csv(file.path(data_path, files[n])))
  
}), fill = TRUE)

glimpse(res)

```

Step 2: Checking the normality of the accuracy measures (summed by level) before we run effect size analyses. For each measure, we create density and QQ plots to visualize the distribution of the data. Then we perform a Shapiro Wilks test of normality. 
```{r}

# Start with data frame "res"
glimpse(res)

# Need to set up new data frame so that there is a separate column for information level information, Same steps as in Step 3, just recovery Level information instead of Method
res_summ <- res %>%
    #Make data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>% 
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    accuracy_type = gsub(pattern = "_mean", replace = "", accuracy_type)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = accuracy_type, into = c(NA, "accuracy_method", "accuracy_level")) %>% 
  # Now, recover "level" as separate columns with pivot wider
  pivot_wider(
    names_from = accuracy_level, 
    values_from = accuracy_measurements,
    names_glue = "accuracy_{accuracy_level}_measurements"
  ) 

glimpse(res_summ)

# Now check normality of two accuracy measures (Group and Individual) using 3 methods: density plot, QQ plot, and Shaprio Wilks Normality Test
# First, accuracy_group_measurements
print(ggpubr::ggdensity(res_summ$accuracy_group_measurements, 
                  main = "Density plot of SPCC Group Accuracy", 
                  xlab = "Accuracy"))
print(ggpubr::ggqqplot(res_summ$accuracy_group_measurements))
print(shapiro.test(res_summ$accuracy_group_measurements))
# Density plot is left skewed and QQ plot is not aligned
# 	Shapiro-Wilk normality test
# data:  res_summ$accuracy_group_measurements
# W = 0.92249, p-value = 8.049e-12
# P value of <0.05 implies the data are significantly different from normal). NOT NORMALLY DISTRIBUTED

# Second, accuracy_individual_measurements
print(ggpubr::ggdensity(res_summ$accuracy_individual_measurements, 
                  main = "Density plot of SPCC Group Accuracy", 
                  xlab = "Accuracy"))
print(ggpubr::ggqqplot(res_summ$accuracy_individual_measurements))
# Density plot is left skewed and QQ plot is not aligned
# 	Shapiro-Wilk normality test
# data:  res_summ$accuracy_individual_measurements
# W = 0.94642, p-value = 2.201e-09
# P value of <0.05 implies the data are significantly different from normal). NOT NORMALLY DISTRIBUTED

```

Because the accuracy measures are not normally distributed, we will use Cliff's delta to calculate effect size. Cliff's D can be used to estimate the effect size for an experiment comparing two samples with ordinal data. See this page for an R tutorial: https://openpublishing.library.umass.edu/pare/article/id/1977/

Step 3: Calculating Effect Sizes for Group vs Individual Accuracy for all Social x Info Proportion combinations between Methods
```{r}

# Start with data frame "res_sum" created above
glimpse(res_summ)

# Calculate effect sizes of the difference between levels per treatment combination
eff_res_level <- res_summ %>% 
  # Group by the columns that have information about each experimental treatment
  # Operations like this are helpful for avoiding nested loops. This grouping should yield 32 groups
  dplyr::group_by(n_groups, group_information_proportion, accuracy_method) %>% 
  # Once the data frame is grouped, we can calculate effect size comparisons 
  # Because we call Group measurements before Individual measurements in this function, it means Group is the comparison group. Therefore, a negative eff_delta value means the distribution of Group measurements is smaller than Individual measurements. A positive value means it is bigger. Below, we save all the delta values, 95% confidence intervals, and the magnitudes of each effect size comparison. 
  dplyr::reframe(
    eff_delta = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["estimate"]],
    eff_CI_upper = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["conf.int"]][["upper"]],
    eff_CI_lower = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["conf.int"]][["lower"]],
    eff_magnitude = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["magnitude"]]
  ) 

# Warning message:
# There were 60 warnings in `dplyr::reframe()`.
# The first warning was:
# ℹ In argument: `eff_delta = ...[[]]`.
# ℹ In group 8: `n_groups = 2`, `group_information_proportion = 1`,
#   `accuracy_method = "edit"`.
# Caused by warning in `cliff.delta.default()`:
# ! The samples are fully disjoint, using approximate Confidence Interval estimation
# ℹ Run dplyr::last_dplyr_warnings() to see the 59 remaining
#   warnings. 
# This code throws several warnings:
# Running dplyr::last_dplyr_warnings() shows that this warning pops up for many other effect size calculations too, like group 17: `n_groups = 6`, `group_information_proportion = 0`,
  # `accuracy_method = "SPCC"`.
# See below for our investigation of these warnings

glimpse(eff_res_level)

# Print the results
eff_res_level %>%
  # The period indicates the current object
  print(n = nrow(.))

# Save the results as a .csv file as well
eff_res_level %>%
  write.csv(., file = file.path(data_path, "effect_sizes_byLevel.csv"), row.names = FALSE)
.
```

The warnings above mean that the distributions for the comparison throwing the warning are completely different from each other. To double check this is true, below we create density plots for each n_group and group info proportion combination for SPCC Accuracy measures and for Edit Distance Accuracy measure. This will be a Supplemental Figure in the Manuscript. 

TKTK Figure out how to get label for color?
TKTK decide if we like labeled or unlabeled facets, then change one of the graphs
```{r}

res_summ <- res_summ %>% 
  dplyr::mutate(
    n_groups = factor(n_groups),
    # Convert the x-axis column to factor to control axis ticks
    group_information_proportion = factor(round(group_information_proportion, 2))
  ) 

glimpse(res_summ)

# Rename Facet variables for labelling purposes
res_summ_rename <- res_summ %>% 
  dplyr::rename(
    Clusters = n_groups,
    Group_Information = group_information_proportion)

glimpse(res_summ_rename)

# Density plots for visualization of the warning above
res_summ_rename %>% 
  dplyr::filter(accuracy_method == "SPCC") %>% 
  ggplot() +
  geom_density(aes(x = accuracy_group_measurements), fill = alpha("#F6955EFF", 0.65)) +
  geom_density(aes(x = accuracy_individual_measurements), fill = alpha("#A8CDECFF", 0.65)) +
  facet_grid(
    Clusters ~ Group_Information,
    scales = "free",
    # label facets with variable name and value
    labeller = label_both) +
  labs(y = "Density", x = "Accuracy Score") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size=14),
    axis.title = element_text(size=16,face="bold"),
    # Change facet elements
    strip.text.x = element_text (size = 14),
    strip.text.y = element_text (size = 14),
    strip.background = element_rect(color = "black", fill = "white")
  )

res_summ %>% 
  dplyr::filter(accuracy_method == "edit") %>% 
  ggplot() +
  geom_density(aes(x = accuracy_group_measurements), fill = alpha("#F6955EFF", 0.65)) +
  geom_density(aes(x = accuracy_individual_measurements), fill = alpha("#A8CDECFF", 0.65)) +
  facet_grid(
    n_groups ~ group_information_proportion,
    scales = "free") +
  labs(y = "Density", x = "Accuracy Score") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size=14),
    axis.title = element_text(size=16,face="bold"),
    strip.text.x = element_text (size = 14),
    strip.text.y = element_text (size = 14),
    strip.background = element_rect(color = "black", fill = "white")
  )

```

