---
title: "Information Encoding Experiments"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "2024-07-08"
---

Purpose: The following code was designed to test the behavior of functions written to generate synthetic vocalizations that emphasize either individual identity or group membership information. These functions written by Ari generate individually distinctive or group-specific character strings that are converted to Parson's code and then audio files of frequency-modulated vocalizations using the `soundgen` package. The loops below iterate over varying ratios of how much of the initial character string is allocated to shared group membership versus unique individual identity. The output of each loop is the normalized mutual information (NMI) calculated between the original classes at both the individual and group levels compared to cluster labels obtained from k-means clustering on multidimensional scaling variables generated from a spectrographic cross-correlation (SPCC) matrix. 

The NMI calculations will allow us to address how much information about group membership versus individual identity is contained in patterns of acoustic variation across call datasets generated to emphasize either individual identity or group membership. For instance, when creating datasets of vocalizations that are more individually distinctive and less group-specific, the NMI for the individual-level should be high but low for the group-level, because patterns of acoustic variation should contain a lot of information about individual identity but less about individuals' group membership. Given that all calls contain individual identity and group membership information, we should also see some interesting patterns at intermediate ratios of the string allocated to individual identity versus group membership.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "aricode", "Rmisc", "warbleR", "stringdist")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# TKTK we will not use the package installation for now, instead directly source the paRsynth functions from the GitHub repo
# TKTK once we start using the package again in package format, we need to add paRsynth:: before eeach function
# Install the paRsynth package from GitHub if you haven't installed it already
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### MANULLY UPDATE EVERY TIME ##################################

# Initialize a base path (we may need a separate base path per user)
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
path <- "~/Desktop" # Grace's path
# path <- "" # Brittany's path

###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_synthetic_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){ 
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){ 
  dir.create(figure_path)
}

```

Source the paRsynth functions directly from the GitHub repository. 
```{r}

# Brittany's path should include "GitHub/paRsynth"
# repo_path <- "~/Desktop/R_packages/paRsynth/R" # Grace's path
repo_path <- "~/Desktop/GitHub_repos/paRsynth/R"

# Get all of the R files for each function in this directory
function_files <- list.files(repo_path, pattern = ".R$", full.names = TRUE)
function_files

# Iterate over these files to load each function, and silence the output
invisible(sapply(X = function_files, FUN = source))

```

Check out documentation for the paRsynth functions. These functions are written below in the order in which they should be used. TKTK this will only work when paRsynth is installed as a package 
```{r eval = FALSE}

# ?paRsynth::generate_strings
# ?paRsynth::parsons_code
# ?paRsynth::frequency_anchors
# ?paRsynth::write_audio

```

In the code below, I handled negative SPCC values by setting these to the minimum observed non-zero SPCC value in the whole matrix. I handled values of 1 off of the diagonal by setting these to the maximum observed value less than 1 in the full matrix.

TKTK need to add an edit distance analysis!! To the NMI, for "true" information recovery at the string step compared to the bioacoustics signal step

Add a function to calculate NMI following Kershenbaum et al. 2013 in PLOS One. I've been getting strange results from aricode::NMI, and those results are also different from when I use the function below.
```{r}

nmi <- function(X, class_col_nm, cluster_col_nm){
  
  # Get the total number of vocalizations
  N <- nrow(X)
  
  # Find the unique combinations of classes and clusters
  tmp <- X %>% 
    distinct(!!sym(class_col_nm), !!sym(cluster_col_nm))
  
  # n_i is the number of vocalizations from class (individual or group) i
  # n_j is the number of vocalizations in cluster j
  # n_ji is the number of vocalizations from individual i in cluster j
  # N is the number of total vocalizations
  
  numerator <- sum(unlist(lapply(1:nrow(tmp), function(z){
    
    class <- tmp[[class_col_nm]][z]
    cluster <- tmp[[cluster_col_nm]][z]
    
    # Get the number of vocalizations from the current class
    n_i <- X %>% 
      dplyr::filter(!!sym(class_col_nm) == class) %>%
      nrow(.)
    
    # Get the number of vocalizations from the current cluster
    n_j <- X %>% 
      dplyr::filter(!!sym(cluster_col_nm) == cluster) %>% 
      nrow(.)
    
    # Get the number of vocalizations from class i that are in cluster j
    n_ji <- X %>% 
      dplyr::filter(!!sym(class_col_nm) == class) %>% 
      dplyr::filter(!!sym(cluster_col_nm) == cluster) %>% 
      nrow(.)
    
    numerators <- n_ji * log( ((N * n_ji) / (n_j * n_i) ))
    
    # Set the calculation to 0 if the calculation above leads to an NaN value, which happens when n_ji is 0
    if(is.na(numerators)) numerators <- 0
    
    return(numerators)
    
  })))
  
  
  # Calculate information in clusters and classes separately (each half of the denominator that goes into the square root expression)
  classes <- unique(X[[class_col_nm]])
  clusters <- unique(X[[cluster_col_nm]])
  
  sum_clusters <- sum(unlist(lapply(1:length(clusters), function(j){
    
    # Get the number of vocalizations from cluster j
    tmp_cluster <- clusters[j] # passing clusters[j] directly to the conditional statement sometimes fails
    n_j <- X %>% 
      dplyr::filter(!!sym(cluster_col_nm) == tmp_cluster) %>% 
      nrow(.)
    
    return( n_j * log( n_j / N ) )
    
  })))
  
  sum_classes <- sum(unlist(lapply(1:length(classes), function(i){
    
    # Get the number of vocalizations from class i
    tmp_class <- classes[i]
    
    n_i <- X %>% 
      dplyr::filter(!!sym(class_col_nm) == tmp_class) %>% 
      nrow(.)
    
    return( n_i * log( n_i / N ) )
    
  })))
  
  # denominator <- sqrt( sum_clusters * sum_classes )
  if(numerator == 0 | (sqrt( sum_clusters * sum_classes )) == 0){
    
    nmi <- 0
    
  } else {
    
    nmi <- numerator / sqrt( sum_clusters * sum_classes )
    
  }
  
  return( nmi )  
  
}


```

Testing the NMI function above.
```{r}

# Testing: NMI should be 1, looks good
X <- data.frame(classes = rep(seq(1, 5, 1), each = 2), clusters = rep(seq(1, 5, 1), each = 2))
X

nmi(X, class_col_nm = "classes", cluster_col_nm = "clusters")

# Testing: NMI should be also be 1, looks good
X <- data.frame(classes = rep(seq(1, 5, 1), each = 2), clusters = rev(rep(seq(1, 5, 1), each = 2)))
X

nmi(X, class_col_nm = "classes", cluster_col_nm = "clusters")

# Testing: NMI should be 0, looks good
X <- data.frame(classes = rep(seq(1, 5, 1), each = 2), clusters = rep(1, 10))
X

nmi(X, class_col_nm = "classes", cluster_col_nm = "clusters")

# Testing: NMI should be closer to 1 when the number of clusters is close to the number of classes, even if the clusters were randomly assigned and classes are split between clusters.
X <- data.frame(classes = rep(seq(1, 256, 1), each = 2), clusters = sample(1:256, 512, replace = TRUE))
X

nmi(X, class_col_nm = "classes", cluster_col_nm = "clusters")

# I get different NMI results using the aricode package
aricode::NMI(X$classes, X$clusters, variant = "sqrt") # this is the variant that should be the same as my function above
aricode::NMI(X$classes, X$clusters, variant = "max")

# Testing: NMI should be closer to 0 when the number of clusters is not close to the number of classes, and when the clusters were randomly assigned
X <- data.frame(classes = rep(seq(1, 256, 1), each = 2), clusters = sample(1:10, 512, replace = TRUE))
X

nmi(X, class_col_nm = "classes", cluster_col_nm = "clusters")

# I get the same NMI result using the aricode package
aricode::NMI(X$classes, X$clusters, variant = "sqrt")

```


# Synthetic experiments over varying social environment characteristics and information encoding rules

How well can we recover the information that was originally encoded over two social levels? Here we generate synthetic vocal identity signals over varying social environment characteristics and information encoding rules. Then we use traditional bioacoustics tools and Normalized Mutual Information to decode information encoded at the group and individual levels.

Iterate over each treatment a number of times so that we can calculate a 95% confidence interval around each NMI calculation. Update the loop so that a selection table is made and SPCC is performed each time a new call dataset is generated. Then save the selection table and SPCC matrix but remove audio files before initiating the subsequent iteration. The duration of the audio files impacts the computational time (files over 400 ms take a long time to generate). The number of calls that will be compared in SPCC also increases computational time, as well as the number of treatments and the number of iterations per treatment.
```{r}

#################### Social environment treatments #################### 

# Initialize varying values of the number of groups and individuals. Here, each group size and number of individuals will travel together per treatment to create 3 social environment treatments (few individuals, dozens of individuals, many individuals)
social_envts <- c("Sparse", "Intermediate", "Dense")
n_groups <- c(2, 4, 8)
n_individuals <- c(2, 4, 8)

# Keep the number of calls per individual constant across iterations
n_calls <- 2

# Check the total number of call comparisons in the largest social environment treatment, which will need to run 5 times (one per information encoding treatment)
# Here the total number of calls is 512
(max(n_groups) * max(n_individuals) ) * n_calls


#################### Information encoding treatments #################### 

# Ratios of group : individual information in a string
# Here these ratios are written as proportions from 0 to 1, such that 0 indicates 0:1 (no group membership and all individual information), and 1 indicates 1:0 (all group membership information)
ratios <- c(0, 0.2, 0.4, 0.8, 1)
# ratios <- c(0.2, 0.4, 0.8) # fewer social conditions for preliminary results

# The total length of the individual and group information together should be constant across strings
encoding_length <- 30

# Check the string lengths that will be assigned to group and individual information across the ratios above
information <- data.table::rbindlist(lapply(1:length(ratios), function(i){
  
  if(ratios[i] < 1){
    
    group_information <- ratios[i] * encoding_length
    
  } else {
    
    group_information <- encoding_length / ratios[i]
    
  }
  
  individual_information <- encoding_length - group_information
  
  return(
    data.frame(
      group_information = group_information,
      individual_information = individual_information
    )
  )
  
}))

information

# The length of the global header and tail should be the same across strings
globals <- 12 # 6 characters for the global head, 6 for the global tail

# Create variation within individuals, and this will be the same across strings
random_variation <- 6

# Initialize the total string length
string_length <- (globals + encoding_length + random_variation)
string_length # 46

# Initialize the number of iterations for each combination of information encoding and social environment treatments (15 total treatments)
iteratns <- 3
# iteratns <- 1 # fewer iterations for preliminary results

# Testing one iteration of each loop
# z <- 3 # social environments
# i <- 5 # information encoding treatments
# n <- 1 # replicates or iterations

# Iterate over the social environment and information encoding treatments to assess how well the original information encoded about group and individual identity can be recovered across these treatments.

system.time(
  
  # Iterate over social environment treatments
  invisible(pblapply(1:length(social_envts), function(z){
    
    # Iterate over information encoding treatments
    lapply(1:length(ratios), function(i){
      
      cat(paste("social condition =", social_envts[z], "\n", sep = " "))
      cat(paste("ratio = ", ratios[i], "\n", sep = ""))
      
      # Iterating over the number of replicates per treatment combination
      nmi_res_tmp <- data.table::rbindlist(lapply(1:iteratns, function(n){
        
        ### Step 1: Generate the string for each call
        calls <- suppressMessages(
          generate_strings(
            n_groups = n_groups[z], 
            n_individuals = n_individuals[z], 
            n_calls = n_calls, 
            string_length = string_length, 
            group_information = information[["group_information"]][i], 
            individual_information = information[["individual_information"]][i],
            random_variation = random_variation
          )
        )
        
        # glimpse(calls)
        
        ### Step 2: Convert the strings to Parsons code
        calls_parsons <- parsons_code(
          df = calls, 
          string_col = "Call",
          global_head_col = "Global_head",
          group_head_col = "Group_head", 
          individual_middle_col = "Individual_middle", 
          group_tail_col = "Group_tail", 
          global_tail_col = "Global_tail",
          random_variation_col = "Random_variation",
          mapping = list(A = "up", B = "down", C = "constant")
        )
        
        # glimpse(calls_parsons)
        
        ### Step 3: Convert the Parsons code to frequency values
        calls_parsons_frequencies <- frequency_anchors(
          df = calls_parsons, 
          parsons_col = "Call_Parsons_Code", 
          group_id_col = "Group", 
          individual_id_col = "Individual", 
          call_id_col = "Call_ID", 
          call_string_col = "Call",
          starting_frequency = 4000, 
          frequency_shift = 1000, 
          section_transition = "continuous_trajectory"
        )
        
        # glimpse(calls_parsons_frequencies)
        
        # ### Step 4: Select a single call per individual to reduce computational time
        # calls_parsons_frequencies_filt <- calls_parsons_frequencies %>% 
        #   group_by(Group, Individual) %>% 
        #   dplyr::slice_sample(n = 1) %>% 
        #   ungroup()
        
        # glimpse(calls_parsons_frequencies_filt)
        
        ### Step 4: For each call or string, use these frequency vectors to generate synthetic audio files with paRsynth and the soundgen package
        
        synthetic_call_metadata <- write_audio(
          df = calls_parsons_frequencies, 
          save_path = data_path, 
          sampling_rate = 44100,
          sylLen = 400,
          temperature = 0,
          prefix = paste(social_envts[z], paste("Ratio", ratios[i], sep = "-"), sep = "_"),
          invalidArgAction = "ignore" # This argument fixes the variable sampling rates that soundgen assigns in the background
        )
        
        # glimpse(synthetic_call_metadata)
        
        wavs <- list.files(
          path = data_path, 
          pattern = paste(paste(social_envts[z], paste("Ratio", ratios[i], sep = "-"), sep = "_"), "_", sep = "")
        )
        
        cat(paste("Number of audio files = ", length(wavs), "\n"))
        
        # Information recovery pipeline with traditional bioacoustics tools
        
        ### Step 5: Generate a selection table for the warbleR package
        # w <- 1 # testing
        
        sel_tbl <- data.table::rbindlist(lapply(1:length(wavs), function(w){
          
          # Read in the given audio file
          tmp <- tuneR::readWave(file.path(data_path, wavs[w]))
          
          # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
          metadats_tmp <- synthetic_call_metadata %>%
            dplyr::filter(grepl(wavs[w], audio_file_name))
          
          # glimpse(metadats_tmp)
          
          # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
          if(nrow(metadats_tmp) > 0){
            
            # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
            # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
            res <- data.frame(
              sound.files = wavs[w], 
              selec = 1,
              start = 0.1, 
              end = seewave::duration(tmp) - 0.1,
              duration = seewave::duration(tmp),
              group_ID = metadats_tmp[["Group"]],
              individual_ID = metadats_tmp[["Individual"]],
              call_ID = metadats_tmp[["Call_ID"]],
              call_string = metadats_tmp[["Call"]], 
              sampling_rate = tmp@samp.rate,
              group_information = information[["group_information"]][i], 
              individual_information = information[["individual_information"]][i],
              social_envt = social_envts[z],
              information_encoding_ratio = ratios[i]
            )
            
          } else {
            
            res <- data.frame(
              sound.files = wavs[w], 
              selec = 1, 
              start = 0.1, 
              end = seewave::duration(tmp) - 0.1,
              duration = seewave::duration(tmp),
              group_ID = NA,
              individual_ID = NA,
              call_ID = NA,
              call_string = NA,
              sampling_rate = tmp@samp.rate,
              group_information = NA, 
              individual_information = NA,
              social_envt = NA,
              information_encoding_ratio = NA
            )
            
          }
          
          return(res)
          
        }))
        
        # See the selection table in warbleR format with all useful metadata for the synthetic experiment
        # glimpse(sel_tbl)
        
        # And there is now a single sampling rate, as expected
        # unique(sel_tbl$sampling_rate)
        
        # All files should have the same sampling rate, otherwise the analyses below will fail
        if(length(unique(sel_tbl$sampling_rate)) > 1){
          stop("Variable sampling rates detected across synthetic audio files, and downstream analyses will fail")
        }
        
        ### Step 6: Perform SPCC using a default window length and a general bandpass filter
        xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 10), wn = "hanning", cor.method = "pearson", parallel = cores, na.rm = FALSE, type = "spectrogram", path = data_path)
        # str(xc_mat)
        
        # Get the percentage of values that are negative
        neg_values <- ((length(xc_mat[xc_mat < 0])/length(xc_mat))) * 100
        
        # Set all negative values to the minimum positive value in the SPCC matrix to represent the fact that these calls are very structurally different from one another
        if(neg_values > 0){
          
          # Initialize a record of what was changed to save to the final results
          neg_notes <- paste(round(neg_values, 8), "% of all SPCC cells or", length(xc_mat[xc_mat < 0])/2,"unique comparisons were negative and were changed to the minimum positive SPCC value of", round(min(xc_mat[xc_mat > 0]), 8), sep = " ")
          
          xc_mat[xc_mat < 0] <- round(min(xc_mat[xc_mat > 0]), 8)
          
        } else {
          
          neg_notes <- ""
          
        }
        
        # Continue with downstream analyses only if there are no 1's off of the diagonal, otherwise MDS will fail. Record NA values if there are 1's off of the diagonal (e.g. two calls of the same structure will present values of 1 as if the same call were compared to itself)
        
        # Make sure to calculate the true number of values in the symmetric matrix (multiply the number of unique values that are 1 by 2)
        ones <- ((length(which(xc_mat[lower.tri(xc_mat)] == 1))*2)/length(xc_mat)) * 100
        
        if(ones > 0){
          
          # Get the maximum similarity value after 1 in the matrix
          max_vals <- xc_mat[lower.tri(xc_mat)]
          
          # This line would sometimes fail when using a value 1 in the conditional statement
          sec_max_val <- max(max_vals[max_vals < 0.9999999])
          
          # Initialize a record of what was changed to save to the final results
          one_notes <- paste(round(ones, 8), "% of all SPCC cells or", length(which(xc_mat[lower.tri(xc_mat)] == 1)), "unique comparisons were had an original SPCC value of 1 and were changed to the next maximum SPCC value of", round(sec_max_val, 8), sep = " ")
          
          # Then set the values of 1 off of the diagonal (in both the upper and lower triangle) to the next highest similarity value in this matrix
          xc_mat[lower.tri(xc_mat)][xc_mat[lower.tri(xc_mat)] == 1] <- round(sec_max_val, 8)
          xc_mat[upper.tri(xc_mat)][xc_mat[upper.tri(xc_mat)] == 1] <- round(sec_max_val, 8)
          
        } else {
          
          one_notes <- ""
          
        }
        
        # Update the dimension names of the matrix
        dimnames(xc_mat) <- list(wavs, wavs)
        
        ### Step 7: Remove .wav files to free up storage space
        rem_files <- file.path(data_path, wavs)
        invisible(file.remove(rem_files))
        
        ### Step 8: Calculate the edit distance amongst all strings
        
        # For each pairwise comparison in the same order as SPCC, calculate the edit distance for the original strings, then assemble this vector into a matrix
        edit_dists <- unlist(lapply(1:nrow(xc_mat), function(i){
          lapply(1:ncol(xc_mat), function(j){
            
            return(
              stringdist(
                a = sel_tbl %>% 
                  dplyr::filter(
                    sound.files == dimnames(xc_mat)[[1]][i]
                  ) %>% 
                  pull(call_string),
                b = sel_tbl %>% 
                  dplyr::filter(
                    sound.files == dimnames(xc_mat)[[2]][j]
                  ) %>% 
                  pull(call_string),
                method = "lv"
              )
            )
            
          })
        }))
        
        edit_mat <- matrix(edit_dists, nrow = nrow(xc_mat), ncol = ncol(xc_mat), byrow = TRUE)
        
        # These dimension names are helpful to check specific loop iterations above
        # dimnames(edit_dist_mat) <- list(dimnames(xc_mat)[[1]], dimnames(xc_mat)[[2]])
        
        # Checking, looks good
        # edit_dist_mat[1:5, 1:5]
        
        
        ### Step 9: Perform MDS on SPCC and edit distance matrices
        
        # Convert the SPCC similarity matrix to a distance matrix and dist object for isoMDS
        spcc_dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
        
        # str(1 - xc_mat)
        # str(spcc_dist_mat)
        
        # Convert the edit distance matrix to a dist object for isoMDS
        edit_dist_mat <- stats::as.dist(edit_mat, diag = TRUE, upper = TRUE)
        
        # Reduce dimensionality of the SPCC and edit matrices using multidimensional scaling (MDS). Use the a different number of total MDS dimensions per treatment combination in order to reduce the stress of the final solution
        if(social_envts[z] == "Sparse"){
          k <- 2
        } else {
          k <- 10
        }
        
        # Perform MDS to obtain SPCC feature space
        iso_spcc <- invisible(MASS::isoMDS(spcc_dist_mat, k = k, maxit = 1000, trace = FALSE))
        # str(iso_spcc)
        
        iso_edit <- invisible(MASS::isoMDS(spcc_dist_mat, k = k, maxit = 1000, trace = FALSE))
        # str(iso_edit)
        
        # Make a data frame of the first two SPCC MDS dimensions and call metadata
        mds_spcc <- data.frame(sound.files = dimnames(iso_spcc$points)[[1]]) %>%
          dplyr::mutate(
            X = iso_spcc$points[, 1],
            Y = iso_spcc$points[, 2]
          ) %>%
          inner_join(
            sel_tbl %>%
              dplyr::select(sound.files, group_ID, individual_ID, call_ID),
            by = c("sound.files")
          )
        
        # glimpse(mds_spcc)
        
        # Make a data frame of the first two edit distance MDS dimensions and call metadata
        mds_edit <- data.frame(sound.files = dimnames(iso_edit$points)[[1]]) %>%
          dplyr::mutate(
            X = iso_edit$points[, 1],
            Y = iso_edit$points[, 2]
          ) %>%
          inner_join(
            sel_tbl %>%
              dplyr::select(sound.files, group_ID, individual_ID, call_ID),
            by = c("sound.files")
          )
        
        # glimpse(mds_edit)
        
        ### Step 10: Perform clustering and Normalized Mutual Information (NMI) calculation
        # In order to compute NMI at two social levels (individual and group), we need to run clustering at these two levels
        
        ### Group-level clustering and NMI calculations
        
        # Set the number of clusters to the number of unique groups
        num_clusters <- length(unique(mds_df$group_ID))
        
        # Perform k-means clustering with this number of clusters on the SPCC and edit distance feature spaces
        # Ensure that the kmeans algorithm uses only the MDS variables, so that it uses information from the patterns of acoustic variation only in order to detect clusters
        spcc_kmeans_grp <- kmeans(mds_spcc[, grep("X|Y", names(mds_spcc))], centers = num_clusters)
        # str(spcc_kmeans_grp)
        
        # Compute NMI at the group-level with k-means clustering on SPCC MDS features
        tmp_mds_spcc <- mds_spcc %>% 
          dplyr::mutate(
            clusters = spcc_kmeans_grp$cluster
          )
        
        spcc_nmi_grp <- nmi(X = tmp_mds_spcc, class_col_nm = "group_ID", cluster_col_nm = "clusters")
        
        # Compute NMI at the group-level with k-means clustering on edit distance MDS features
        edit_kmeans_grp <- kmeans(mds_edit[, grep("X|Y", names(mds_edit))], centers = num_clusters)
        # str(edit_kmeans_grp)
        
        # Compute NMI at the group-level with k-means clustering on SPCC MDS features
        tmp_mds_edit <- mds_edit %>% 
          dplyr::mutate(
            clusters = edit_kmeans_grp$cluster
          )
        
        edit_nmi_grp <- nmi(X = tmp_mds_edit, class_col_nm = "group_ID", cluster_col_nm = "clusters")
        
        # NMI should be 1 when comparing the same vector to itself, looks good
        nmi(X = tmp_mds_spcc, class_col_nm = "group_ID", cluster_col_nm = "group_ID")
        nmi(X = tmp_mds_spcc, class_col_nm = "clusters", cluster_col_nm = "clusters")
        nmi(X = tmp_mds_edit, class_col_nm = "group_ID", cluster_col_nm = "group_ID")
        nmi(X = tmp_mds_edit, class_col_nm = "clusters", cluster_col_nm = "clusters")
        
        # TKTK CONTINUE
        
        ### Individual-level clustering and NMI calculation
        
        # Set the number of clusters to the number of unique individuals within each group
        num_clusters <- mds_df %>% 
          distinct(individual_ID) %>% 
          nrow()
        
        # Perform k-means clustering with this number of clusters within each group, so iterate over groups for the NMI calculation
        # n <- 2 # testing
        kmeans_ind_cg <- unlist(lapply(1:n_groups[z], function(n){
          
          tmp <- mds_df[mds_df$group_ID == n, ]
          
          # Checking, looks good
          unique(tmp$group_ID)
          all(tmp$group_ID == n)
          
          # Perform clustering using the MDS coordinates as input
          res <- kmeans(tmp[, grep("X|Y", names(tmp))], centers = num_clusters)
          
          tmp_mds <- tmp %>% 
            dplyr::mutate(
              clusters = res$cluster
            )
          
          # glimpse(tmp_mds)
          
          # Compute NMI at the individual-level, which means that the original classes are the group plus individual identity
          return(nmi(X = tmp_mds, class_col_nm = "individual_ID", cluster_col_nm = "clusters"))
          
        }))
        
        nmi_results <- data.frame(
          social_envt_treatment = social_envts[z],
          information_encoding_treatment = ratios[i],
          iteration = n,
          group_information = information[["group_information"]][i], 
          individual_information = information[["individual_information"]][i],
          NMI_group = nmi_grp,
          NMI_individual_mean = mean(kmeans_ind_cg),
          NMI_individual_min = min(kmeans_ind_cg),
          NMI_individual_max = max(kmeans_ind_cg),
          notes = paste(neg_notes, one_notes, sep = "; ")
        )
        
        # nmi_results
        
        ### Step 11: return NMI results
        return(nmi_results)
        
      }))
      
      ### Step 12: Write out the NMI results for the given treatment combination across iterations
      nmi_res_tmp %>% 
        write.csv(file.path(data_path, paste("NMI_results_", paste(social_envts[z], paste("Ratio", ratios[i], sep = "-"), sep = "_"), ".csv", sep = "")), row.names = FALSE)
      
    })
    
  }))
  
)

# On my laptop 3 social conditions and 5 information treatments with 1 iteration took about 8 minutes. I decreased the number of social groups and individuals per group in the Intermediate and Dense conditions
# user  system elapsed 
# 491.132 275.017 262.716 

# On my laptop 3 social conditions and 5 information treatments with 3 iterations took about 32 minutes. I decreased the number of social groups and individuals per group in the Intermediate and Dense conditions
# user   system  elapsed 
# 1955.841 1064.957 1022.187

# On the Mac Mini this process took ~ 14 minutes with 3 social conditions, 3 information encoding ratios, and 1 iteration of each treatement combination

# On the Mac Mini this process took ~ 29 hours with 3 social conditions, 5 information encoding ratios, and 5 iterations of each treatement combination
# 01d 04h 52m 56s
# user    system   elapsed 
# 40655.65  39141.46 103975.72 

```

Checking the NMI results.
```{r}

nmi_files <- list.files(path = data_path, pattern = "NMI_")
nmi_files

nmi_res <- data.table::rbindlist(pblapply(1:length(nmi_files), function(n){
  
  return(read.csv(file.path(data_path, nmi_files[n])))
  
}), fill = TRUE)

glimpse(nmi_res)

# View(nmi_res)

# Checking that there are no NMI values above 1, looks good
any(nmi_res$NMI_group > 1)
any(nmi_res$NMI_individual_max > 1)

```
