---
title: "Information Encoding Experiments"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "2024-07-08"
---

Purpose: The following code was designed to test the behavior of functions written to generate synthetic vocalizations that emphasize either individual identity or group membership information. These functions written by Ari generate individually distinctive or group-specific character strings that are converted to Parson's code and then audio files of frequency-modulated vocalizations using the `soundgen` package. The loops below iterate over varying ratios of how much of the initial character string is allocated to shared group membership versus unique individual identity. The output of each loop is the percent recovery of the original classes at both the individual and group levels compared to cluster labels obtained from clustering with Gaussian mixture models (performed on multidimensional scaling variables generated from the edit distance obtained from character string comparisons or the spectrographic cross-correlation (SPCC) matrix obtained from comparing synthetic acoustic signals). 

Below we iterate over social conditions and group versus individual information encoding at two social levels in character strings that will influence the distinctiveness or uniqueness of the strings and the resulting synthetic vocalizations at either social level. 

The pipeline below will allow us to indirectly address or compare how much information about group membership versus individual identity is contained in patterns of acoustic variation across character strings and their corresponding synthetic vocalizations that represent vocal identity signals. For instance, when creating datasets of vocalizations that are more individually distinctive and less group-specific, the percentage of original individual-level labels recovered by clustering should be high, but low for the group-level, because patterns of acoustic variation should contain a lot of information about individual identity but less about group membership.

TKTK updates to work on here:

- Outline the research question better in the narrative text above
- Remove all NMI function calls and results
- Replace k-means clustering with Gaussian mixture models
- Set the total number of clusters higher than the original number of classes per social level to avoid limiting clustering to the true number of classes
- Calculate the percent recovery of original labels at each social level (how many original labels were predicted correctly and how many were not?), for both the edit distance and SPCC analyses
- Then calculate the effect size of either the difference or the correlation between percent recovery by the edit distance and the SPCC analyses
- Consider removing the information theory angle in the narrative text below since we will address the information theory side directly in another paper 

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "aricode", "Rmisc", "warbleR", "stringdist")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# TKTK we will not use the package installation for now, instead directly source the paRsynth functions from the GitHub repo
# TKTK once we start using the package again in package format, we need to add paRsynth:: before eeach function
# Install the paRsynth package from GitHub if you haven't installed it already
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### MANULLY UPDATE EVERY TIME ##################################

# Initialize a base path (we may need a separate base path per user)
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
path <- "~/Desktop" # Grace's path
# path <- "C:/Users/britt/Desktop" #Brittany's path

###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_synthetic_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){ 
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){ 
  dir.create(figure_path)
}

```

Source the paRsynth functions directly from the GitHub repository. 
```{r}

###################### MANULLY UPDATE EVERY TIME ##################################

# Brittany's path should include "GitHub/paRsynth"
# repo_path <- "~/Desktop/R_packages/paRsynth/R" # Grace's path
repo_path <- "~/Desktop/GitHub_repos/paRsynth/R"

# Get all of the R files for each function in this directory
function_files <- list.files(repo_path, pattern = ".R$", full.names = TRUE)
function_files

# Iterate over these files to load each function, and silence the output
invisible(sapply(X = function_files, FUN = source))

###################################################################################

```

Check out documentation for the paRsynth functions. These functions are written below in the order in which they should be used. TKTK this will only work when paRsynth is installed as a package 
```{r eval = FALSE}

# ?paRsynth::generate_strings
# ?paRsynth::parsons_code
# ?paRsynth::frequency_anchors
# ?paRsynth::write_audio

```

In the code below, I handled negative SPCC values by setting these to the minimum observed non-zero SPCC value in the whole matrix. I handled values of 1 off of the diagonal by setting these to the maximum observed value less than 1 in the full matrix. I used similar guidelines for values of 0 off of the diagonal for the edit distance.

# Synthetic experiments over varying social environment characteristics and information encoding rules

How well can we recover the information that was originally encoded over two social levels? Here we generate synthetic vocal identity signals over varying social environment characteristics and information encoding rules. Then we use the percent recovery of original labels by clustering algorithms (performed on MDS feature spaces derived from the edit distance computed amongst strings and spectrographic cross-correlation computed amongst synthetic vocalizations) to ask how well we "recovered" information encoded at the group and individual levels.

Iterate over each treatment a number of times so that we can calculate a 95% confidence interval around each percent recovery calculations. In the looping structure below, a selection table is made and the edit distance and SPCC are performed each time a new call dataset is generated. Audio files are written to a directory associated with the project and removed before initiating the subsequent iteration. The duration of the audio files significantly impacts the computational time (files over 400 ms take a long time to generate). Also, long strings written to short duration audio files do not sound or look biologically relevant, so we are using a short string length below. The number of calls that will be compared by the edit distance and SPCC also increases computational time, as well as the number of treatments (social conditions, information encoding) and the number of iterations per treatment.
```{r}

#################### Information encoding and social environment treatments #################### 

# Initialize varying values of the number of groups and individuals. Here, each group size and number of individuals will travel together per treatment to create 4 social environment treatments (few individuals, intermediate numbers of individuals, dozens of individuals, many individuals) that follow predictions for how many unique vocal signatures can be created at each social level from an information theory perspective (which will be addressed directly in another project/paper).

individual_information <- c(0, 2, 4, 6)
group_information <- rev(individual_information)

individual_information
group_information

# Choose a sparse social condition in which we expect to have highly distinguishable group and individual signatures even with small amounts of information encoding
# Then choose an intermediate social conditions that will require more positions devoted to information encoding to generate sufficiently distinguishable signatures at each social level as the number of individuals increases
# Finally choose dense social conditions that max out the number of unique signatures possible with lower amounts of information encoding. In other words, as there are more groups or individuals within groups, more positions within a string need to be devoted to group and individual information encoding in order to ensure that each group or individual is more likely to have a unique signature. At small amounts of information encoding, the number of possible unique signatures will be fully maxed out when there are many groups and individuals within groups
social_envts <- c("Sparse", "Intermediate", "Crowded", "Dense")
n_groups <- c(2, 6, 10, 20)
n_individuals <- c(2, 6, 10, 20)

# Keep the number of calls per individual constant across iterations
# Using a single call per individual would increase computational efficiency, but it is helpful to include within-individual variation in our downstream analyses of how well original information was "recovered"
n_calls <- 2

# Check the total number of call comparisons in the largest social environment treatment, which will need to run 5 times (one per information encoding treatment)
# Here the total number of calls that will compared in any one iteration is 200, which is not a concern in terms of computational efficiency
(max(n_groups) * max(n_individuals) ) * n_calls

# All call comparisons for each social condition treatment
(n_groups * n_individuals) * n_calls

# Number of symbols that we are using in Parsons code
symbols <- 3

# Create a data frame that combines information about the total possible number of unique signatures at each social level with the different social conditions
# i <- 1
information <- data.table::rbindlist(pblapply(1:length(social_envts), function(j){
  
  tmp2 <- data.table::rbindlist(lapply(1:length(individual_information), function(i){
    
    tmp <- data.frame(
      social_envt = social_envts[j],
      group_information = group_information[i],
      individual_information = individual_information[i],
      # These values represent how much of the total social information encoding length is taken up by information encoding at either social level. When this value is 1, all 6 characters are used to encode group information. When this value is less than 0.5, more characters are devoted to individual information encoding. When this value is 0, all characters are used for individual information encoding. These two columns can be used as the x-axis in figures below (and maybe we can have one x-axis on the bottom, one on the top)
      group_information_proportion = group_information[i] / max(group_information),
      individual_information_proportion = individual_information[i] / max(individual_information)
    )
    
    return(tmp)
    
  }))
  
  return(tmp2)
  
}))

View(information)

# Then set other parameters for creating synthetic vocal identity signals
# The length of the global header and tail should be the same across strings
globals <- 12 # 6 characters for the global head, 6 for the global tail

# Create variation within individuals, and this will be the same across strings created for the same individual
random_variation <- 2

# Initialize the total string length
string_length <- (globals + max(group_information) + random_variation)
string_length # 20

# Initialize the number of iterations for each combination of information encoding and social environment treatments (15 total treatments)
iteratns <- 8
# iteratns <- 1 # fewer iterations for preliminary results

# Testing one iteration of each loop
# z <- 3 # social environments
# i <- 1 # information encoding treatments
# n <- 1 # replicates or iterations

# Iterate over the social environment and information encoding treatments to assess how well the original information encoded about group and individual identity can be recovered across these treatments.

system.time(
  
  # Iterate over social environment treatments
  invisible(pblapply(1:length(social_envts), function(z){
    
    # Iterate over information encoding treatments
    lapply(1:length(group_information), function(i){
      
      cat(paste("social condition =", social_envts[z], "\n", sep = " "))
      cat(paste("group_information = ", group_information[i], "\n", sep = ""))
      cat(paste("individual_information = ", individual_information[i], "\n", sep = ""))
      
      # Iterating over the number of replicates per treatment combination
      res_tmp <- data.table::rbindlist(lapply(1:iteratns, function(n){
        
        ### Step 1: Generate strings that represent calls
        calls <- suppressMessages(
          generate_strings(
            n_groups = n_groups[z], 
            n_individuals = n_individuals[z], 
            # Generate more calls than what we need to ensure that we use n_calls with different strings per individual (see below)
            n_calls = n_calls * 5, 
            string_length = string_length, 
            group_information = group_information[i], 
            individual_information = individual_information[i],
            random_variation = random_variation
          )
        )
        
        # glimpse(calls)
        
        
        ### Step 2: Calculate the edit distance among strings generated for each unique individual, and retain only the number of calls per individual set by n_calls that have an edit distance > 0 (such that calls for the same individual are not the exact same string)
        
        # Iterate over each individual to compare the edit distance amongst their calls, and return only n_calls with edit distance > 0
        unique_indivs <- unique(paste(calls$Group, calls$Individual, sep = "-"))
        # unique_indivs
        
        # Testing
        # m <- 2
        # p <- 1
        # q <- 2
        # Note that this solution will not generalize well whenever n_calls is greater than 2
        calls_filt <- data.table::rbindlist(lapply(1:length(unique_indivs), function(m){
          
          tmp_indiv <- unique_indivs[m]
          # tmp_indiv
          
          tmp <- calls %>% 
            dplyr::filter(paste(Group, Individual, sep = "-") == tmp_indiv)
          
          
          call_comps <- data.table::rbindlist(lapply(1:ncol(tmp), function(p){
            
            res <- data.table::rbindlist(lapply(1:ncol(tmp), function(q){
              
              edit_dist <- stringdist(
                a = tmp %>% 
                  slice(p) %>% 
                  pull(Call),
                b = tmp %>% 
                  slice(q) %>% 
                  pull(Call),
                method = "lv"
              )
              
              if(edit_dist > 0){
                return(
                  data.frame(
                    individual = tmp_indiv,
                    call_ID_1 = tmp %>% 
                      slice(p) %>% 
                      pull(Call_ID),
                    call_ID_2 = tmp %>% 
                      slice(q) %>% 
                      pull(Call_ID)
                  )
                )
              }
              
            }))
            
            return(res)
            
          }))
          
          # call_comps
          
          # Then randomly select a single comparison representing 2 calls or strings with an edit distance > 0
          retain_calls <- call_comps[sample(1:nrow(call_comps), size = n_calls/2), ]
          
          # Use this output to filter the calls data frame for the given individual to return only the calls we will use in downstream analyses
          return(
            tmp %>% 
              dplyr::filter(Call_ID == retain_calls$call_ID_1 | Call_ID == retain_calls$call_ID_2)
          )
        
        }))
        
        # glimpse(calls_filt)
        
        ### Step 2: Convert the strings to Parsons code
        calls_parsons <- parsons_code(
          df = calls_filt, 
          string_col = "Call",
          global_head_col = "Global_head",
          group_head_col = "Group_head", 
          individual_middle_col = "Individual_middle", 
          group_tail_col = "Group_tail", 
          global_tail_col = "Global_tail",
          random_variation_col = "Random_variation",
          mapping = list(A = "up", B = "down", C = "constant")
        )
        
        # glimpse(calls_parsons)
        
        ### Step 3: Convert the Parsons code to frequency values
        calls_parsons_frequencies <- frequency_anchors(
          df = calls_parsons, 
          parsons_col = "Call_Parsons_Code", 
          group_id_col = "Group", 
          individual_id_col = "Individual", 
          call_id_col = "Call_ID", 
          call_string_col = "Call",
          starting_frequency = 4000, 
          frequency_shift = 1000, 
          section_transition = "continuous_trajectory"
        )
        
        # glimpse(calls_parsons_frequencies)
        
        ### Step 4: For each call or string, use these frequency vectors to generate synthetic audio files with paRsynth and the soundgen package
        
        synthetic_call_metadata <- write_audio(
          df = calls_parsons_frequencies, 
          save_path = data_path, 
          sampling_rate = 44100,
          sylLen = 200,
          temperature = 0,
          prefix = paste(social_envts[z], paste("groupInfo", group_information[i], sep = "-"), sep = "_"),
          invalidArgAction = "ignore" # This argument fixes the variable sampling rates that soundgen assigns in the background
        )
        
        # glimpse(synthetic_call_metadata)
        
        wavs <- list.files(
          path = data_path, 
          pattern = paste(paste(social_envts[z], paste("groupInfo", group_information[i], sep = "-"), sep = "_"), "_", sep = "")
        )
        
        cat(paste("Number of audio files = ", length(wavs), "\n"))
        
        
        ###### Information recovery pipeline with traditional bioacoustics tools
        
        ### Step 5: Generate a selection table for the warbleR package
        # w <- 1 # testing
        
        sel_tbl <- data.table::rbindlist(lapply(1:length(wavs), function(w){
          
          # Read in the given audio file
          tmp <- tuneR::readWave(file.path(data_path, wavs[w]))
          
          # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
          metadats_tmp <- synthetic_call_metadata %>%
            dplyr::filter(grepl(wavs[w], audio_file_name))
          
          # glimpse(metadats_tmp)
          
          # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
          if(nrow(metadats_tmp) > 0){
            
            # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
            # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
            res <- data.frame(
              sound.files = wavs[w], 
              selec = 1,
              start = 0.1, 
              end = seewave::duration(tmp) - 0.1,
              duration = seewave::duration(tmp),
              group_ID = metadats_tmp[["Group"]],
              individual_ID = metadats_tmp[["Individual"]],
              call_ID = metadats_tmp[["Call_ID"]],
              call_string = metadats_tmp[["Call"]], 
              sampling_rate = tmp@samp.rate,
              group_information = group_information[i], 
              individual_information = individual_information[i],
              social_envt = social_envts[z],
              possible_unique_group_signatures = (symbols ^ group_information[i]),
              possible_unique_individual_signatures = (symbols ^ individual_information[i])
            )
            
          } else {
            
            res <- data.frame(
              sound.files = wavs[w], 
              selec = 1, 
              start = 0.1, 
              end = seewave::duration(tmp) - 0.1,
              duration = seewave::duration(tmp),
              group_ID = NA,
              individual_ID = NA,
              call_ID = NA,
              call_string = NA,
              sampling_rate = tmp@samp.rate,
              group_information = NA, 
              individual_information = NA,
              social_envt = NA,
              possible_unique_group_signatures = NA,
              possible_unique_individual_signatures = NA
            )
            
          }
          
          return(res)
          
        }))
        
        # See the selection table in warbleR format with all useful metadata for the synthetic experiment
        # glimpse(sel_tbl)
        
        # And there is now a single sampling rate, as expected
        # unique(sel_tbl$sampling_rate)
        
        # All files should have the same sampling rate, otherwise the analyses below will fail
        if(length(unique(sel_tbl$sampling_rate)) > 1){
          stop("Variable sampling rates detected across synthetic audio files, and downstream analyses will fail")
        }
        
        ### Step 6: Perform SPCC using a default window length and a general bandpass filter
        xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 10), wn = "hanning", cor.method = "pearson", parallel = cores, na.rm = FALSE, type = "spectrogram", path = data_path)
        # str(xc_mat)
        
        # Get the percentage of values that are negative
        neg_values <- ((length(xc_mat[xc_mat < 0])/length(xc_mat))) * 100
        
        # Set all negative values to the minimum positive value in the SPCC matrix to represent the fact that these calls are very structurally different from one another
        if(neg_values > 0){
          
          # Initialize a record of what was changed to save to the final results
          neg_notes <- paste(round(neg_values, 8), "% of all SPCC cells or", length(xc_mat[xc_mat < 0])/2,"unique comparisons were negative and were changed to the minimum positive SPCC value of", round(min(xc_mat[xc_mat > 0]), 8), sep = " ")
          
          xc_mat[xc_mat < 0] <- round(min(xc_mat[xc_mat > 0]), 8)
          
        } else {
          
          neg_notes <- ""
          
        }
        
        # Continue with downstream analyses only if there are no 1's off of the diagonal, otherwise MDS will fail. Record NA values if there are 1's off of the diagonal (e.g. two calls of the same structure will present values of 1 as if the same call were compared to itself)
        
        # Make sure to calculate the true number of values in the symmetric matrix (multiply the number of unique values that are 1 by 2)
        ones <- ((length(which(xc_mat[lower.tri(xc_mat)] == 1))*2)/length(xc_mat)) * 100
        
        if(ones > 0){
          
          # Get the maximum similarity value after 1 in the matrix
          max_vals <- xc_mat[lower.tri(xc_mat)]
          
          # Use a value just under one to catch floating point numbers that are visually represented as 1
          sec_max_val <- max(max_vals[max_vals < 0.9999999])
          
          # Initialize a record of what was changed to save to the final results
          one_notes <- paste(round(ones, 8), "% of all SPCC cells or", length(which(xc_mat[lower.tri(xc_mat)] == 1)), "unique comparisons were had an original SPCC value of 1 and were changed to the next maximum SPCC value of", round(sec_max_val, 8), sep = " ")
          
          # Then set the values of 1 off of the diagonal (in both the upper and lower triangle) to the next highest similarity value in this matrix
          xc_mat[lower.tri(xc_mat)][xc_mat[lower.tri(xc_mat)] == 1] <- round(sec_max_val, 8)
          xc_mat[upper.tri(xc_mat)][xc_mat[upper.tri(xc_mat)] == 1] <- round(sec_max_val, 8)
          
        } else {
          
          one_notes <- ""
          
        }
        
        # Update the dimension names of the matrix
        dimnames(xc_mat) <- list(wavs, wavs)
        
        ### Step 7: Remove .wav files to free up storage space
        rem_files <- file.path(data_path, wavs)
        invisible(file.remove(rem_files))
        
        ### Step 8: Calculate the edit distance amongst all strings
        
        # For each pairwise comparison in the same order as SPCC, calculate the edit distance for the original strings, then assemble this vector into a matrix
        edit_dists <- unlist(lapply(1:nrow(xc_mat), function(m){
          lapply(1:ncol(xc_mat), function(p){
            
            return(
              stringdist(
                a = sel_tbl %>% 
                  dplyr::filter(
                    sound.files == dimnames(xc_mat)[[1]][m]
                  ) %>% 
                  pull(call_string),
                b = sel_tbl %>% 
                  dplyr::filter(
                    sound.files == dimnames(xc_mat)[[2]][p]
                  ) %>% 
                  pull(call_string),
                method = "lv"
              )
            )
            
          })
        }))
        
        edit_mat <- matrix(edit_dists, nrow = nrow(xc_mat), ncol = ncol(xc_mat), byrow = TRUE)
        
        # There is an earlier check built in above to avoid edit distance values of 0 for calls compared within an individual. But as the number of groups and individuals increases, the likelihood of generating the same call strings across individuals or groups increases, so the code below replaces edit distance values of 0 off of the diagonal with the minimum edit distance value in the matrix

        # Check if there are values of 0 off of the diagonal in the edit distance matrix, which will happen by chance when the exact same strings are generated within an individual (even with the random variation)
        # Make sure to calculate the true number of values in the symmetric matrix (multiply the number of unique values that are 1 by 2)
        zeroes <- ((length(which(edit_mat[lower.tri(edit_mat)] == 0))*2)/length(edit_mat)) * 100

        if(zeroes > 0){

          # Get the minimum non-zero similarity value in the matrix
          min_vals <- edit_mat[lower.tri(edit_mat)]

          sec_min_val <- min(min_vals[min_vals > 0])

          # Initialize a record of what was changed to save to the final results
          zero_notes <- paste(round(zeroes, 8), "% of all edit distance cells or", length(which(edit_mat[lower.tri(edit_mat)] == 0)), "unique comparisons were had an original edit distance value of 0 and were changed to the next minimum edit distance value of", round(sec_min_val, 8), sep = " ")

          # Then set the values of 1 off of the diagonal (in both the upper and lower triangle) to the next highest similarity value in this matrix
          edit_mat[lower.tri(edit_mat)][edit_mat[lower.tri(edit_mat)] == 0] <- round(sec_min_val, 8)
          edit_mat[upper.tri(edit_mat)][edit_mat[upper.tri(edit_mat)] == 0] <- round(sec_min_val, 8)

        } else {

          zero_notes <- ""

        }
        
        # These dimension names are helpful below
        dimnames(edit_mat) <- list(dimnames(xc_mat)[[1]], dimnames(xc_mat)[[2]])
        
        # str(edit_mat)
        
        ### Step 9: Perform MDS on SPCC and edit distance matrices
        
        # Convert the SPCC similarity matrix to a distance matrix and dist object for isoMDS
        spcc_dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
        
        # str(1 - xc_mat)
        # str(spcc_dist_mat)
        
        # Convert the edit distance matrix to a dist object for isoMDS
        # Do not subtract the edit distance values from 1 because these are already distances and also are not proximity values
        edit_dist_mat <- stats::as.dist(edit_mat, diag = TRUE, upper = TRUE)
        
        # str(edit_dist_mat)
        
        # Reduce dimensionality of the SPCC and edit matrices using multidimensional scaling (MDS). Use the a different number of total MDS dimensions per treatment combination in order to reduce the stress of the final solution
        if(social_envts[z] == "Sparse"){
          k <- 2
        } else {
          k <- 10
        }
        
        # Perform MDS to obtain SPCC feature space
        iso_spcc <- invisible(MASS::isoMDS(spcc_dist_mat, k = k, maxit = 1000, trace = FALSE))
        # str(iso_spcc)
        
        # Perform MDS to obtain edit distance feature space
        iso_edit <- invisible(MASS::isoMDS(edit_dist_mat, k = k, maxit = 1000, trace = FALSE))
        # str(iso_edit)
        
        # Make a data frame of the first two SPCC MDS dimensions and call metadata
        mds_spcc <- data.frame(sound.files = dimnames(iso_spcc$points)[[1]]) %>%
          dplyr::mutate(
            X = iso_spcc$points[, 1],
            Y = iso_spcc$points[, 2]
          ) %>%
          inner_join(
            sel_tbl %>%
              dplyr::select(sound.files, group_ID, individual_ID, call_ID),
            by = c("sound.files")
          )
        
        # glimpse(mds_spcc)
        
        # Make a data frame of the first two edit distance MDS dimensions and call metadata
        mds_edit <- data.frame(sound.files = dimnames(iso_edit$points)[[1]]) %>%
          dplyr::mutate(
            X = iso_edit$points[, 1],
            Y = iso_edit$points[, 2]
          ) %>%
          inner_join(
            sel_tbl %>%
              dplyr::select(sound.files, group_ID, individual_ID, call_ID),
            by = c("sound.files")
          )
        
        # glimpse(mds_edit)
        
        ### Step 10: Perform clustering and percent recovery calculations
        # In order to calculate percent recovery at two social levels (individual and group), we need to run clustering at these two levels
        
        ### Group-level clustering and percent recovery calculations
        
        # Set the number of clusters to the number of unique groups
        num_clusters <- length(unique(mds_spcc$group_ID))
        # num_clusters
        
        # TKTK change to GMMs
        # Perform k-means clustering with this number of clusters on the SPCC and edit distance feature spaces
        # Ensure that the kmeans algorithm uses only the MDS variables, so that it uses information from the patterns of acoustic variation only in order to detect clusters
        spcc_kmeans_grp <- kmeans(mds_spcc[, grep("X|Y", names(mds_spcc))], centers = num_clusters)
        # str(spcc_kmeans_grp)
        
        # Calculate percent recovery of original group-level labels with k-means clustering on SPCC MDS features
        tmp_mds_spcc <- mds_spcc %>% 
          dplyr::mutate(
            clusters = spcc_kmeans_grp$cluster
          )
        
        spcc_nmi_grp <- nmi(X = tmp_mds_spcc, class_col_nm = "group_ID", cluster_col_nm = "clusters")
        
        # Calculate percent recovery of original group-level labels with k-means clustering on edit distance MDS features
        edit_kmeans_grp <- kmeans(mds_edit[, grep("X|Y", names(mds_edit))], centers = num_clusters)
        # str(edit_kmeans_grp)
        
        tmp_mds_edit <- mds_edit %>% 
          dplyr::mutate(
            clusters = edit_kmeans_grp$cluster
          )
        
        edit_nmi_grp <- nmi(X = tmp_mds_edit, class_col_nm = "group_ID", cluster_col_nm = "clusters")
        
        ### Individual-level clustering and NMI calculation
        
        # Set the number of clusters to the number of unique individuals within each group
        num_clusters <- mds_spcc %>% 
          distinct(individual_ID) %>% 
          nrow()
        
        # num_clusters
        
        # Perform k-means clustering with this number of clusters within each group, so iterate over groups for the percent recovery calculations. Use SPCC MDS features here
        # n <- 1 # testing
        spcc_kmeans_ind_cg <- unlist(lapply(1:n_groups[z], function(m){
          
          tmp <- mds_spcc[mds_spcc$group_ID == m, ]
          
          # Checking, looks good
          # unique(tmp$group_ID)
          # all(tmp$group_ID == m)
          
          # Perform clustering using the MDS coordinates as input
          res <- kmeans(tmp[, grep("X|Y", names(tmp))], centers = num_clusters)
          
          tmp_mds <- tmp %>% 
            dplyr::mutate(
              clusters = res$cluster
            )
          
          # glimpse(tmp_mds)
          
          # Calculate percent recovery of original individual-level labels, which means that the original classes are the group plus individual identity
          return(nmi(X = tmp_mds, class_col_nm = "individual_ID", cluster_col_nm = "clusters"))
          
        }))
        
        
        # Perform k-means clustering with this number of clusters within each group, so iterate over groups for the percent recovery calculation. Use edit distance MDS features here
        # n <- 2 # testing
        edit_kmeans_ind_cg <- unlist(lapply(1:n_groups[z], function(m){
          
          tmp <- mds_edit[mds_edit$group_ID == m, ]
          
          # Checking, looks good
          # unique(tmp$group_ID)
          # all(tmp$group_ID == m)
          
          # Perform clustering using the MDS coordinates as input
          res <- kmeans(tmp[, grep("X|Y", names(tmp))], centers = num_clusters)
          
          tmp_mds <- tmp %>% 
            dplyr::mutate(
              clusters = res$cluster
            )
          
          # glimpse(tmp_mds)
          
          # Calculate percent recovery of original individual-level labels, which means that the original classes are the group plus individual identity
          return(nmi(X = tmp_mds, class_col_nm = "individual_ID", cluster_col_nm = "clusters"))
          
        }))
        
        # edit_kmeans_ind_cg
        
        
        results <- data.frame(
          social_envt_treatment = social_envts[z],
          group_information = group_information[i], 
          individual_information = individual_information[i],
          iteration = n,
          group_information_proportion = group_information[i] / max(group_information),
          individual_information_proportion = individual_information[i] / max(individual_information),
          possible_unique_group_signatures = (symbols ^ group_information[i]),
          possible_unique_individual_signatures = (symbols ^ individual_information[i]),
          NMI_SPCC_group = spcc_nmi_grp,
          NMI_edit_group = edit_nmi_grp,
          NMI_SPCC_individual_mean = mean(spcc_kmeans_ind_cg),
          NMI_edit_individual_mean = mean(edit_kmeans_ind_cg),
          notes = paste(neg_notes, one_notes, sep = "; ")
        )
        
        # results
        
        ### Step 11: return results
        return(results)
        
      }))
      
      ### Step 12: Write out the results for the given treatment combination across iterations
      res_tmp %>% 
        write.csv(file.path(data_path, paste("Percent_recovery_results_", paste(social_envts[z], paste("groupInfo", group_information[i], sep = "-"), sep = "_"), ".csv", sep = "")), row.names = FALSE)
      
    })
    
  }))
  
)

# On my laptop 3 social conditions and 4 information treatments with 1 iteration took about 11 minutes. 

# Started a run of 4 social conditions, 4 information encoding treatments with 8 iterations each at 8:05 on 06 Feb 2025. The largest number of calls that will be compared in any one iteration will be 800 for the Dense social condition.

```

Checking the percent recovery results.
```{r}

files <- list.files(path = data_path, pattern = "Percent_recovery_")
files

res <- data.table::rbindlist(pblapply(1:length(files), function(n){
  
  return(read.csv(file.path(data_path, files[n])))
  
}), fill = TRUE)

glimpse(res)

View(res)

# Checking that there are no percent recovery values above 1
any(res$group > 1)
any(res$individual_max > 1)

```

Making NMI plots (Brittany edition)
TKTK instead of geom_smooth, use geom_ribbon where you can specific upper and lower bounds for CI?
Jan 31, tried geom_ribbon with individual min and max value, looks weird. Not sure what is going on. 
TKTK need to make prettier with colors, export in a better way
```{r}
install.packages('ggpubr')
library(ggpubr)

NMI_Group_plot <- ggplot(nmi_res, aes(x = information_encoding_treatment, y = NMI_group, color = social_envt_treatment)) +
  geom_point() + 
  geom_smooth()

NMI_Individ_plot <- ggplot(nmi_res, aes(x = information_encoding_treatment, y = NMI_individual_mean, color = social_envt_treatment, shape = social_envt_treatment)) +
  geom_ribbon(aes(ymin = NMI_individual_min, ymax = NMI_individual_max, fill = social_envt_treatment), color = NA, alpha = .25) +  
  geom_point()


ggpubr::ggarrange(NMI_Group_plot, NMI_Individ_plot,
                  labels = "AUTO", 
                  common.legend = TRUE, 
                  legend = "bottom")


```

