---
title: "Information Encoding Experiments - Effect Size Figures"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "2025-02-26"
---

Purpose: The following code was designed to create a figure displaying the average effect size delta values for the comparisons between level (Group and Individual) accuracy measures.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# tktk update list
# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### Manually update in every new coding session ##################################

# Initialize a base path (we may need a separate base path per user)
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
path <- "C:/Users/britt/Desktop" #Brittany's path

###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_synthetic_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){ 
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){ 
  dir.create(figure_path)
}

```

Plotting Group vs Individual Effect Sizes for all Social x Info Proportion x Method combinations
```{r}
# Effect Size Comparisons (between SPCC and Edit Distance) for each social X information proportion treatment at each information level 

# Load in data file 
eff_res_level <- read.csv(file.path(data_path, "effect_sizes_byLevel.csv"))

glimpse(eff_res_level)

# Setting up for plotting
eff_res_level_gg <- eff_res_level %>%
# Reorganize social_envt_treatment, so that legend scale goes in order from Sparse to Dense
# mutate() creates new columns and can be used to modify/overwrite exist columns, like below when reorganizing factor levels
dplyr::mutate(
    # Convert the x-axis column to factor to control axis ticks
    group_information_proportion = factor(round(group_information_proportion, 2)),
    # convert accuracy_level to factor
    accuracy_method = factor(accuracy_method),
    # Convert n_groups to a factor
    n_groups = factor(n_groups)
  )

# there should be 32 rows in eff_res and 6 colums, but I can't get the results of eff size to save as columns  
glimpse(eff_res_level_gg)  

# defining colors, fill colors and shapes
cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 0.2) # only use if you want fill colors to be slightly transparent
shps <- c(21, 22, 24, 25) 

# Renaming the Accuracy Information Level labels
method_labs <- c("SPCC", "Edit Distance")
names(method_labs) <- c("SPCC", "edit")

# Now to make plots of the effect size estimates and the CIs
eff_res_level_gg %>% 
  ggplot(aes(x = group_information_proportion, y = eff_delta, color = n_groups, fill = n_groups, shape = n_groups)) +
  geom_hline(aes(yintercept = 0), color = "grey") +
  geom_hline(aes(yintercept = .474), linetype = "longdash", color = "grey") +
  geom_hline(aes(yintercept = -.474), linetype = "longdash", color = "grey") +
  geom_pointrange(aes(ymin = eff_CI_lower, ymax = eff_CI_upper), linewidth = .85, stroke = .85, position = position_dodge(width = .5)) +
  facet_grid(~accuracy_method, labeller = labeller(accuracy_method = method_labs)) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_shape_manual(values = shps) +
  guides(color = guide_legend(title = "Number of Original Classes", override.aes = list(size = .6)), fill = guide_legend(title = "Number of Original Classes"),
         shape = guide_legend(title = "Number of Original Classes")) +
  labs(y = "Average Cliff's Detla and 95% CI", x = "Proportion of Group Information") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size=14),
    axis.title = element_text(size=16,face="bold"),
    legend.position = "top",
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    strip.text.x = element_text (size = 14, face = "bold"),
    strip.text.y = element_text (size = 14, face = "bold"),
    strip.background = element_rect(color = "black", fill = "white")
  )

# save as tiff file
ggsave(filename = "EffSize_Level_PointRange", path = figure_path, width = 6, height = 6, device = "tiff", dpi = 700)

```
