---
title: 'Supplementary figures: Acoustic space plots'
author: Grace Smith-Vidaurre
output: html_document
date: "2025-04-08"
---

Purpose: Here we use build acoustic space plots for supplementary figures. Acoustic space plots are generated using multidimensional scaling coordinates from spectrographic cross-correlation and edit distance analyses.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "warbleR", "paletteer")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Install the paRsynth package from GitHub if you haven't installed it already
# remove.packages("paRsynth")
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/raneemsamman/Desktop" # Raneem's path
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "/Users/summe/OneDrive/Desktop/" #Summer's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where images for figures will be written out/read in
figures_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figures_path <- file.path(path, analysis_dir, figures_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figures_path)){ 
  dir.create(figures_path)
}

```

Read in the synthetic call metadata, and MDS coordinates. Set cores for parallel processing.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))
glimpse(synthetic_call_metadata)

mds_coords <- read.csv(file.path(analysis_path, "MDS_coordinates.csv"))
glimpse(mds_coords)

cores <- parallel::detectCores() - 4
cores

```

# Generate low-dimensional acoustic space plots for supplementary figures

Create a plot of calls from both datasets in the same universal acoustic space (edit distance or SPCC). This plot should have 4 panels: datasets plotted with polygons at both social levels.

Create two plots (SPCC and edit distance) with convex hull polygons by group. These plots should be organized with edit distance on the top and SPCC on the bottom, so the edit distance plot will have a legend. These plots will be combined with a small collection of spectrograms in one main figure.

## Group-level polygons

Start with aesthetics.
```{r}

# Get colors for groups from the same palette used for spectrograms in lexicons
cols <- paletteer::paletteer_d("nationalparkcolors::Arches")
cols

# Combine MDS results from the SPCC and edit distance pipelines
mds_spcc_grp <- mds_coords %>%
  # Filter by the group membership calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Group Membership", method == "SPCC"
  ) %>%
  # Convert strings to factors for plotting
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID)
  )

glimpse(mds_spcc_grp)

mds_edit_grp <- mds_coords %>%
  # Filter by the group membership calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Group Membership", method == "edit"
  ) %>% 
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID)
  )

glimpse(mds_edit_grp)

levels(mds_spcc_grp$group_ID)
levels(mds_spcc_grp$individual_ID)

# Colors by group (five)
cols_grp <- cols[1:length(levels(mds_spcc_grp$group))]
cols_grp

# Fills by unique individual
fills <- rep(cols_grp, each = length(levels(mds_spcc_grp$individual_ID)))
fills

# Shapes by individual within groups
shps <- c(7, 8, 10, 4, 16, 17, 21, 23, 24, 6)

```

## Edit distance, group membership dataset and group-level polygons

Use the same plot included in the main figure.

## SPCC, group membership dataset and group-level polygons

Use the same plot included in the main figure.

## Edit distance, group membership dataset and individual-level polygons

Edit distance first with a legend. Use the same continuous x and y-axis scales as the main figures.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_edit_grp, "unique_individuals", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_edit_grp %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = unique_individuals), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = fills) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", nrow = 1), fill = "none") +
  # Uncomment this line to turn off the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-5, -1.8), breaks = seq(-5, -2, 0.5), labels = sprintf("%.2f", round(seq(-5, -2, 0.5), 2))) +
  scale_y_continuous(limits = c(-4.5, 4), breaks = seq(-4, 4, 1), labels = sprintf("%.2f", round(seq(-4, 4, 1), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(linewidth = 0.25),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines"),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# This is the image size that will be written to create a legend for the composite figure created in other software
ggsave(filename = file.path(figures_path, "AcousticSpace_edit_GroupMembership_IndividualPolygons_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

## SPCC, group membership dataset and individual-level polygons

SPCC with a legend. Use the same continuous x and y-axis scales as the main figures.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_spcc_grp, "unique_individuals", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_spcc_grp %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = unique_individuals), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = fills) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", nrow = 1), fill = "none") +
  # Uncomment this line to turn off the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.3, 0), breaks = seq(-0.3, 0, 0.05), labels = sprintf("%.2f", round(seq(-0.3, 0, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.35, 0.25), breaks = seq(-0.35, 0.25, 0.1), labels = sprintf("%.2f", round(seq(-0.35, 0.25, 0.1), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(linewidth = 0.25),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines"),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# This is the image size that will be written to create a legend for the composite figure created in other software
ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_GroupMembership_IndividualPolygons.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

## Individual-level polygons

Start with aesthetics.
```{r}

# Get colors for groups from the same palette used for spectrograms in lexicons
cols <- paletteer::paletteer_d("nationalparkcolors::Arches")
cols

# Combine MDS results from the SPCC and edit distance pipelines
mds_spcc_ind <- mds_coords %>%
  # Filter by the individual identity dataset calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Individual Identity", method == "SPCC"
  ) %>%
  # Convert strings to factors for plotting
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID)
  )

glimpse(mds_spcc_ind)

mds_edit_ind <- mds_coords %>%
  # Filter by the individual identity dataset calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Individual Identity", method == "edit"
  ) %>% 
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID)
  )

glimpse(mds_edit_ind)

levels(mds_spcc_ind$group_ID)
levels(mds_spcc_ind$individual_ID)

# Colors by group (five)
cols_grp <- cols[1:length(levels(mds_spcc_ind$group))]
cols_grp

# Shapes by individual within groups
shps <- c(7, 8, 10, 4, 16, 17, 21, 23, 24, 6)
```

## Edit distance, individual identity dataset and individual-level polygons

Use the same plot included in the main figure.

## SPCC, individual identity dataset and individual-level polygons

Use the same plot included in the main figure.

## Edit distance, individual identity dataset and group-level polygons

Edit distance first with a legend. Use the same continuous x and y-axis scales as the main figures.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_edit_ind, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_edit_ind %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = cols_grp) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", nrow = 1), fill = "none") +
  # Uncomment this line to turn off the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(2, 4.5), breaks = seq(2, 4.5, 0.5), labels = sprintf("%.2f", round(seq(2, 4.5, 0.5), 2))) +
  scale_y_continuous(limits = c(-4.1, 4), breaks = seq(-4, 4, 2), labels = sprintf("%.2f", round(seq(-4, 4, 2), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(linewidth = 0.25),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines"),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# This is the image size that will be written to create a legend for the composite figure created in other software
ggsave(filename = file.path(figures_path, "AcousticSpace_edit_IndividualIdentity_GroupPolygons_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

## SPCC, individual identity dataset and group-level polygons

SPCC with a legend. Use the same continuous x and y-axis scales as the main figures.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_spcc_ind, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_spcc_ind %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = cols_grp) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", nrow = 1), fill = "none") +
  # Uncomment this line to turn off the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(0, 0.5), breaks = seq(0, 0.5, 0.1), labels = sprintf("%.2f", round(seq(0, 0.5, 0.1), 2))) +
  scale_y_continuous(limits = c(-0.25, 0.35), breaks = seq(-0.25, 0.35, 0.1), labels = sprintf("%.2f", round(seq(-0.25, 0.35, 0.1), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(linewidth = 0.25),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines"),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# This is the image size that will be written to create a legend for the composite figure created in other software
ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_IndividualIdentity_GroupPolygons_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```