---
title: "Main figures: Acoustic space plots"
author: Grace Smith-Vidaurre
output: html_document
date: "2024-11-20"
---

Purpose: Here we use build acoustic space plots for main figures. Acoustic space plots are generated using multidimensional scaling coordinates from spectrographic cross-correlation and edit distance analyses.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "warbleR", "paletteer")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Install the paRsynth package from GitHub if you haven't installed it already
# remove.packages("paRsynth")
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/raneemsamman/Desktop" # Raneem's path
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "/Users/summe/OneDrive/Desktop/" #Summer's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where images for figures will be written out/read in
figures_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figures_path <- file.path(path, analysis_dir, figures_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figures_path)){ 
  dir.create(figures_path)
}

```

Read in the synthetic call metadata, and MDS coordinates. Set cores for parallel processing.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))
glimpse(synthetic_call_metadata)

mds_coords <- read.csv(file.path(analysis_path, "MDS_coordinates.csv"))
glimpse(mds_coords)

cores <- parallel::detectCores() - 4
cores

```

# Generate low-dimensional acoustic space plots for main figures

## Group membership dataset: 

Create two plots (SPCC and edit distance) with convex hull polygons by group. These plots should be organized with edit distance on the top and SPCC on the bottom, so the edit distance plot will have a legend. These plots will be combined with a small collection of spectrograms in one main figure.

Start with aesthetics.
```{r}

# Get colors for groups from the same palette used for spectrograms in lexicons
cols <- paletteer::paletteer_d("nationalparkcolors::Arches")
cols

# Combine MDS results from the SPCC and edit distance pipelines
mds_spcc_grp <- mds_coords %>%
  # Filter by the group membership calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Group Membership", method == "SPCC"
  ) %>%
  # Convert strings to factors for plotting
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID)
  )

glimpse(mds_spcc_grp)

mds_edit_grp <- mds_coords %>%
  # Filter by the group membership calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Group Membership", method == "edit"
  ) %>% 
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID)
  )

glimpse(mds_edit_grp)

levels(mds_spcc_grp$group_ID)
levels(mds_spcc_grp$individual_ID)

# Colors by group (five)
cols_grp <- cols[1:length(levels(mds_spcc_grp$group))]

# Shapes by individual within groups
shps <- c(7, 8, 10, 4, 16, 17, 21, 23, 24, 6)

```

Create the group membership plots. Edit distance first with a legend.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_edit_grp, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_edit_grp %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = group_ID, color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = cols_grp) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", nrow = 1), fill = guide_legend(title = "Group", order = 1)) +
  # Uncomment this line to turn off the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-5, -1.8), breaks = seq(-5, -2, 0.5), labels = sprintf("%.2f", round(seq(-5, -2, 0.5), 2))) +
  scale_y_continuous(limits = c(-4.5, 4), breaks = seq(-4, 4, 1), labels = sprintf("%.2f", round(seq(-4, 4, 1), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(linewidth = 0.25),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines"),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# Save this plot as an image file
# This is the image size that will be written without a legend
# ggsave(filename = file.path(figures_path, "AcousticSpace_edit_GroupMembership.tiff"), width = 6, height = 4, units = "in", dpi = 300)

# This is the image size that will be written to create a legend for the composite figure created in other software
ggsave(filename = file.path(figures_path, "AcousticSpace_edit_GroupMembership_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

SPCC next, no legend.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_spcc_grp, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_spcc_grp %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = group_ID, color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = cols_grp) +
  xlab("") + ylab("") + 
  # guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", override.aes = list(size = 3), nrow = 1), fill = guide_legend(title = "Group", override.aes = list(size = 3), order = 1)) +
  # Uncomment this line to turn off the legend
  guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.3, 0), breaks = seq(-0.3, 0, 0.05), labels = sprintf("%.2f", round(seq(-0.3, 0, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.35, 0.25), breaks = seq(-0.35, 0.25, 0.1), labels = sprintf("%.2f", round(seq(-0.35, 0.25, 0.1), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines"),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# Save this plot as an image file
# This is the image size that will be written without a legend
ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_GroupMembership.tiff"), width = 6, height = 4, units = "in", dpi = 300)

# This is the image size that will be written to create a legend for the composite figure created in other software
# ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_GroupMembership_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

## Individual identity dataset

Create two plots (SPCC and edit distance) with convex hull polygons by individual. These plots should be organized with edit distance on the top and SPCC on the bottom, so the edit distance plot will have a legend. These plots will be combined with a small collection of spectrograms in one main figure.

Start with aesthetics.
```{r}

# Combine MDS results from the SPCC and edit distance pipelines
mds_spcc_ind <- mds_coords %>%
  # Filter by the group membership calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Individual Identity", method == "SPCC"
  ) %>%
  # Convert strings to factors for plotting
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID),
    unique_individuals = factor(unique_individuals)
  )

glimpse(mds_spcc_ind)

mds_edit_ind <- mds_coords %>%
  # Filter by the group membership calls and MDS coordinates from SPCC
  dplyr::filter(
    dataset == "Individual Identity", method == "edit"
  ) %>%
  # Convert strings to factors for plotting
  dplyr::mutate(
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID),
    unique_individuals = factor(unique_individuals)
  )

glimpse(mds_edit_ind)

levels(mds_spcc_ind$group_ID)
levels(mds_spcc_ind$individual_ID)
levels(mds_spcc_ind$unique_individuals)

# Get colors for groups from the same palette used for spectrograms in lexicons
cols <- paletteer::paletteer_d("nationalparkcolors::Arches")
cols

# Colors by group
grp_cols <- cols[1:length(levels(mds_spcc_grp$group))]
grp_cols

# Border colors by group (five) repeated per individual
# icols <- rep(grp_cols, each = length(levels(mds_spcc_ind$individual_ID)))
# icols

# Fills by unique individual
fills <- rep(grp_cols, each = length(levels(mds_spcc_ind$individual_ID)))
fills

# Shapes by individual within groups
# shps <- rep(c(7, 8, 10, 4, 16, 17, 21, 23, 24, 6), length(levels(mds_spcc_ind$group_ID)))
shps <- c(7, 8, 10, 4, 16, 17, 21, 23, 24, 6)

```

Edit distance first with a legend.
```{r}

# glimpse(mds_edit_ind)

hulls <- plyr::ddply(mds_edit_ind, "unique_individuals", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

glimpse(mds_edit_ind)

mds_edit_ind %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = unique_individuals), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  # facet_wrap(~ group_ID) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = grp_cols) +
  scale_fill_manual(values = fills) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", override.aes = list(size = 3), nrow = 1), fill = "none") +
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(2, 4.5), breaks = seq(2, 4.5, 0.5), labels = sprintf("%.2f", round(seq(2, 4.5, 0.5), 2))) +
  scale_y_continuous(limits = c(-4.1, 4), breaks = seq(-4, 4, 2), labels = sprintf("%.2f", round(seq(-4, 4, 2), 2))) +
  theme_bw() +
  theme(
    legend.position = "top",
    legend.key.spacing = unit(0.2, "line"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_edit_IndividualIdentity_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

SPCC next without a legend.
```{r}

# glimpse(mds_edit_ind)

hulls <- plyr::ddply(mds_spcc_ind, "unique_individuals", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_spcc_ind %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = unique_individuals), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  # facet_wrap(~ group_ID) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = grp_cols) +
  scale_fill_manual(values = fills) +
  xlab("") + ylab("") + 
  # guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", override.aes = list(size = 3), nrow = 1), fill = "none") +
  guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(0, 0.5), breaks = seq(0, 0.5, 0.1), labels = sprintf("%.2f", round(seq(0, 0.5, 0.1), 2))) +
  scale_y_continuous(limits = c(-0.25, 0.35), breaks = seq(-0.25, 0.35, 0.1), labels = sprintf("%.2f", round(seq(-0.25, 0.35, 0.1), 2))) +
  theme_bw() +
  theme(
    legend.position = "top",
    legend.key.spacing = unit(0.2, "line"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    # margin() arguments: top, right, bottom, left
    plot.margin = margin(0, 3, -3, -3, unit = "pt"),
    legend.margin = margin(2, -3, -5, -3, unit = "pt")
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_IndividualIdentity.tiff"), width = 6, height = 4, units = "in", dpi = 300)

```