---
title: "Information Encoding Experiments - Accuracy Figures"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "2024-07-08"
---

Purpose: The following code was designed to create figures for the manuscript. This figure uses output from the script "Experiments_InformationEncoding_Accuracy". The following code creates a data frame which is used to create plots of average accuracy for SPCC and Edit methods by Group Info Proportion and Social Environment Treatments. Plots are separate for information level (group or individual).

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# tktk update list
# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "Rmisc", "warbleR", "stringdist", "ggpubr", "paletteer", "effsize")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# TKTK we will not use the package installation for now, instead directly source the paRsynth functions from the GitHub repo
# TKTK once we start using the package again in package format, we need to add paRsynth:: before each function
# Install the paRsynth package from GitHub if you haven't installed it already
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### Manually update in every new coding session ##################################

# Initialize a base path (we may need a separate base path per user)
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "C:/Users/britt/Desktop" #Brittany's path

# Initialize a path for the local GitHub repo for this manuscript, for saving final figures here
# git_path <- "C:/Users/britt/Documents/GitHub/paRsynth-methods-paper/figures" # Britt's path
git_path <- file.path(path, "GitHub_repos/paRsynth-methods-paper/figures") # Grace's path

###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_synthetic_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){
  dir.create(figure_path)
}

```

Load files
```{r}

files <- list.files(path = data_path, pattern = "^Accuracy_")
files

res <- data.table::rbindlist(pblapply(1:length(files), function(n){
  
  return(read.csv(file.path(data_path, files[n])))
  
}), fill = TRUE)

glimpse(res)

# View(res)

# Check that there are no accuracy values above 1, looks good
sapply(res %>%
         dplyr::select(names(.)[grep("accuracy", names(.))]),
       function(X){
         any(X > 1)
       }
)

# Check that there are no accuracy values below 0, looks good
sapply(res %>%
         dplyr::select(names(.)[grep("accuracy", names(.))]),
       function(X){
         any(X < 0)
       }
)

```

The following code creates a data frame from "res" called "res_sum", which is used to create plots of average accuracy for SPCC and Edit methods by Group Info Proportion and Social Environment Treatments. Plots are separate for information level (group or individual)

If updating, please save plot as "Accuracy_Average_Pointrange"
```{r}

# Average Accuracy Measures by Encoding treatment and social condition

# Check that the number of rows matches the number of treatments and iterations
# 4 social and 4 information treatments by 10 iterations should be 160 rows, looks good
glimpse(res)

# Summarize the results from the synthetic experiments to calculate the mean and 95% CI per treatment combination (social condition and information encoding condition)

res_summ <- res %>%
  # Make the data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>%
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    tmp = accuracy_type,
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    tmp = gsub(pattern = "_mean", replace = "", tmp)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = tmp, into = c(NA, "accuracy_method", "accuracy_level"), sep = "_") %>%
  # View()
  # Group by the columns that have information about each experimental treatment
  # Operations like this are helpful for avoiding nested loops. This grouping should yield 16 groups across the two experimental treatments (4 x 4), plus the two methods and social levels for accuracy calculations
  dplyr::group_by(n_groups, group_information_proportion, accuracy_method, accuracy_level) %>%
  # Once a data frame is grouped, you can calculate summary statistics by each group
  dplyr::summarise(
    mean_accuracy = mean(accuracy_measurements),
    # Calculate the 95% CI measurements and extract the upper 95% CI value
    upper_95_CI = Rmisc::CI(accuracy_measurements, ci = 0.95)[["upper"]],
    lower_95_CI = Rmisc::CI(accuracy_measurements, ci = 0.95)[["lower"]]
  ) %>%
  # Make sure to ungroup before plotting, and the columns used for grouping will be retained
  ungroup() %>%
  # Reorganize scoial_envt_treatment, so that legend scale goes in order from Sparse to Dense
  # mutate() creates new columns and can be used to modify/overwrite exist columns, like below when reorganizing factor levels
  dplyr::mutate(
    n_groups = factor(n_groups),
    # Convert the x-axis column to factor to control axis ticks
    group_information_proportion = factor(round(group_information_proportion, 2))
  )

# There should be 4 social conditions * 4 information encoding conditions * 2 accuracy methods * 2 social levels in rows, or 64 rows, looks good
glimpse(res_summ)

# The levels for the social condition treatment column looks good
levels(res_summ$n_groups)

# Looks good
unique(res_summ$accuracy_method)
unique(res_summ$accuracy_level)

# Then, make color list that contains 1 ,2 4, and 5th color hex codes from paletteer_packages:Arches
# paletteer_d("nationalparkcolors::Arches")
#A8CDECFF #F6955EFF #682C37FF #9B6981FF #7887A4FF #A89F8EFF
# Use #A8CDECFF #F6955EFF #9B6981FF #7887A4FF

cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 0.2)
shps <- c(21, 24) # Encode accuracy method by shape. See the points function for options

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
class_labs <- c("Classes: 2", "Classes: 4", "Classes: 6", "Classes: 8")
names(class_labs) <- c("2", "4", "6", "8")

# Renaming the Accuracy Information Level labels
level_labs <- c("Group-level accuracy", "Individual-level accuracy")
names(level_labs) <- c("group", "individual")

# Aaking this in case we want to make the facet background a very very light grey
ngrey <- scales::alpha("grey", 0.2)

# Make the faceted plot without ggarrange(), no need to make separate plots unless you need more flexibility
res_summ %>%
  ggplot(aes(x = group_information_proportion, y = mean_accuracy, color = accuracy_method, fill = accuracy_method, shape = accuracy_method)) +
  # linewidth controls the width of the errorbar lines, stroke controls the width of the symbol border
  geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI), linewidth = 0.5, stroke = 0.5, position = position_dodge(width = 0.5), size = 0.75) +
  facet_grid(
    accuracy_level ~ n_groups,
    labeller = labeller(accuracy_level = level_labs, n_groups = class_labs)
  ) +
  scale_y_continuous(limits = c(0, 1.05)) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fillcols) +
  scale_shape_manual(values = shps) +
  # Change the legend titles, make sure to do this for all legend aesthetic layers. You can also override aesthetics set in the main plot
  guides(color = guide_legend(title = "Method", override.aes = list(size = 0.8)), fill = guide_legend(title = "Method"),
         shape = guide_legend(title = "Method")) +
  labs(y = "Average accuracy", x = "Proportion of group information") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.margin = margin(t = 0, r = 0, b = -0.25, l = 0, unit = "line"),
    strip.text.x = element_text (size = 11, face = "plain"),
    strip.text.y = element_text (size = 11, face = "plain"),
    strip.background = element_rect(color = "black", fill = ngrey)
  )

# save as tiff file
ggsave(filename = file.path(git_path, "AverageAccuracy_PointRange.tiff"), width = 7.25, height = 5.25, units = "in", dpi = 300)

# This is a good reference to walk through customizing facet aes https://www.datanovia.com/en/blog/how-to-change-ggplot-facet-labels/

```

Make a plot that could be a main figure in the manuscript to highlight how effect sizes were calculated. Density plots of the accuracy distributions to highlight how effect sizes were calculated.

Make one main figure that has class sizes of 2 and 8 only. Make 2 supplementary figures of all classes but edit distance and SPCC only.

Main figure.
```{r}

eff_res <- read.csv(file.path(data_path, "effect_sizes_byLevel.csv"))
glimpse(eff_res)

cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 1)
shps <- c(21, 24) # Encode accuracy level. See the points function for options

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
class_labs <- c("Classes: 2", "Classes: 8")
names(class_labs) <- c("2", "8")

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
method_labs <- c("Edit", "SPCC")
names(method_labs) <- c("edit", "SPCC")

prop_labs <- c("Proportion of\n group information: 0", "0.33", "0.67", "1")
names(prop_labs) <- unique(res$group_information_proportion)

# Aaking this in case we want to make the facet background a very very light grey
ngrey <- scales::alpha("grey", 0.1)

glimpse(res)

# Make the faceted plot without ggarrange(), no need to make separate plots unless you need more flexibility
res_density_values <- res %>%
  # Make the data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>%
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    tmp = accuracy_type,
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    tmp = gsub(pattern = "_mean", replace = "", tmp)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = tmp, into = c(NA, "accuracy_method", "accuracy_level"), sep = "_") %>% 
  # Change social level labels to be capitalized
  dplyr::mutate(
    accuracy_level = gsub("group", "Group", accuracy_level),
    accuracy_level = gsub("individual", "Individual", accuracy_level)
  )

glimpse(res_density_values)

# Generate means for vertical dashed lines
means <- res_density_values %>%
  dplyr::filter(n_groups %in% c(2, 8)) %>%
  group_by(accuracy_level, accuracy_method, n_groups, group_information_proportion) %>%
  dplyr::summarize(
    mean_val = mean(accuracy_measurements)
  ) %>%
  dplyr::select(
    accuracy_level, accuracy_method, n_groups, group_information_proportion, mean_val
  ) %>%
  ungroup()

glimpse(means)

# Make labels of the effect size value and the 95% CI
glimpse(eff_res)

eff_res_label <- eff_res %>% 
  dplyr::filter(n_groups %in% c(2, 8)) %>%
  group_by(n_groups, accuracy_method, group_information_proportion) %>% 
  dplyr::mutate(
    eff_label = paste(c(sprintf("%.02f", round(eff_delta, 2)), " (", paste(c(sprintf("%.02f", round(eff_CI_lower, 2)), sprintf("%.02f", round(eff_CI_upper, 2))), collapse = ", "), ")"), collapse = "")
  ) %>% 
  # Add a label to create bolded text for large effect sizes (>= 0.474)
  dplyr::mutate(
    eff_magnitude = ifelse(abs(eff_delta) >= 0.474, "large", "not large"),
    eff_fontface = ifelse(abs(eff_delta) >= 0.474, "bold", "plain")
  ) %>% 
  ungroup()

glimpse(eff_res_label)

# Use the means to generate coordinates for where bars to indicate effect size calculations should start and end
bar_coords <- means %>%
  pivot_wider(
    values_from = "mean_val",
    names_from = "accuracy_level"
  ) %>% 
  # Add information for coloring these bars by which information had greater accuracy
  dplyr::mutate(
    stronger_encoding = ifelse(Group > Individual, "Group", "Individual")
  ) %>% 
  # Join with the effect size results to get information about which of these bars or segments correspond to large effect sizes
  inner_join(
    eff_res_label %>% 
      dplyr::select(accuracy_method, group_information_proportion, n_groups, eff_magnitude),
    by = c("accuracy_method", "group_information_proportion", "n_groups")
  )

glimpse(bar_coords)

res_density_values %>%
  dplyr::filter(n_groups %in% c(2, 8)) %>%
  ggplot() +
  # Density curves for group level (blue)
  geom_density(data = res_density_values %>%
                 dplyr::filter(n_groups %in% c(2, 8)) %>%
                 dplyr::filter(accuracy_level == "Group"), color = scales::alpha(fillcols[1], 0), fill = scales::alpha(fillcols[1], 0.65), aes(x = accuracy_measurements)) +
  # Add a mean line using geom_segment to control height: mean line for group level
  geom_segment(data = means %>%
                 dplyr::filter(accuracy_level == "Group"), aes(x = mean_val, xend = mean_val, y = 0, yend = 40), linewidth = 0.75, color = fillcols[1], linetype = "dashed") +
  # Density curves for individual level (orange)
  geom_density(data = res_density_values %>%
                 dplyr::filter(n_groups %in% c(2, 8)) %>%
                 dplyr::filter(accuracy_level == "Individual"), color = scales::alpha(fillcols[2], 0), fill = scales::alpha(fillcols[2], 0.65), aes(x = accuracy_measurements)) +
  # Add a mean line using geom_segment to control height: mean line for individual level
  geom_segment(data = means %>%
                 dplyr::filter(accuracy_level == "Individual"), aes(x = mean_val, xend = mean_val, y = 0, yend = 40), linewidth = 0.75, color = fillcols[2], linetype = "dashed") +
  # Add horizontal bars or segments between the means of each density curve that represent each effect size calculation. These bars are colored by the social level with higher accuracy, and the transparency folows the strength of the effect size (large effect sizes are more opaque)
  geom_segment(data = bar_coords, aes(x = Group, xend = Individual, y = 40, yend = 40, color = stronger_encoding, alpha = eff_magnitude), linewidth = 2) +
  facet_grid(
    n_groups ~ accuracy_method ~ group_information_proportion,
    scales = "fixed",
    labeller = labeller(accuracy_method = method_labs, n_groups = class_labs, group_information_proportion = prop_labs)
  ) +
  # Add the effect size values plus the 95% CIs. Add bolded text for large effect sizes
  geom_text(data = eff_res_label, aes(label = eff_label, y = 50, x = 0.65, fontface = eff_fontface), size = 3) +
  scale_y_continuous(limits = c(0, 55)) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fillcols) +
  scale_shape_manual(values = shps) +
  scale_alpha_manual(values = c(1, 0.5)) +
  # Change the legend titles, make sure to do this for all legend aesthetic layers. You can also override aesthetics set in the main plot
  guides(color = guide_legend(title = "Social level", override.aes = list(size = 0.8)), fill = guide_legend(title = "Social level"), alpha = "none") +
  labs(y = "Density of accuracy values at either social social", x = "Accuracy measurements") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    legend.position = "top",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.margin = margin(t = 0, r = 0, b = -0.25, l = 0, unit = "line"),
    strip.text.x = element_text (size = 10, face = "plain"),
    strip.text.y = element_text (size = 10, face = "plain"),
    strip.background = element_rect(color = "black", fill = ngrey)
  )

# save as tiff file
ggsave(filename = file.path(git_path, "AccuracyDensityPlots_EffectSizes.tiff"), width = 7.25, height = 5.25, units = "in", dpi = 300)

```


Supplementary figures.
```{r}

cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 0.2)
shps <- c(21, 24) # Encode accuracy level. See the points function for options

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
class_labs <- c("Classes: 2", "4", "6", "8")
names(class_labs) <- c("2", "4", "6", "8")

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
method_labs <- c("Edit", "SPCC")
names(method_labs) <- c("edit", "SPCC")

prop_labs <- c("Proportion of group information: 0", "0.33", "0.67", "1")
names(prop_labs) <- unique(res$group_information_proportion)

# Aaking this in case we want to make the facet background a very very light grey
ngrey <- scales::alpha("grey", 0.2)

glimpse(res)

# Make the faceted plot without ggarrange(), no need to make separate plots unless you need more flexibility
res_density_values <- res %>%
  # Make the data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>%
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    tmp = accuracy_type,
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    tmp = gsub(pattern = "_mean", replace = "", tmp)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = tmp, into = c(NA, "accuracy_method", "accuracy_level"), sep = "_")

glimpse(res_density_values)

# Generate means
means <- res_density_values %>%
  group_by(accuracy_level, accuracy_method, n_groups, group_information_proportion) %>%
  dplyr::summarize(
    mean_val = mean(accuracy_measurements)
  ) %>%
  dplyr::select(
    accuracy_level, accuracy_method, n_groups, group_information_proportion, mean_val
  )

res_density_values %>%
  ggplot(aes(x = accuracy_measurements)) +
  geom_density(data = res_density_values %>%
                 dplyr::filter(accuracy_level == "group"), color = cols[1], fill = fillcols[1]) +
  geom_vline(data = means %>%
               dplyr::filter(accuracy_level == "group"), aes(xintercept = mean_val), color = cols[1], linetype = "dashed") +
  geom_density(data = res_density_values %>%
                 dplyr::filter(accuracy_level == "individual"), color = cols[2], fill = fillcols[2]) +
  geom_vline(data = means %>%
               dplyr::filter(accuracy_level == "individual"), aes(xintercept = mean_val), color = cols[2], linetype = "dashed") +
  facet_grid(
    accuracy_method ~ n_groups ~ group_information_proportion,
    scales = "free",
    labeller = labeller(accuracy_method = method_labs, n_groups = class_labs, group_information_proportion = prop_labs)
  ) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fillcols) +
  scale_shape_manual(values = shps) +
  # Change the legend titles, make sure to do this for all legend aesthetic layers. You can also override aesthetics set in the main plot
  guides(color = guide_legend(title = "Method", override.aes = list(size = 0.8)), fill = guide_legend(title = "Method"),
         shape = guide_legend(title = "Accuracy level", order = 1, override.aes = list(size = 0.8))) +
  labs(y = "Density", x = "Accuracy measurements") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    legend.position = "top",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.margin = margin(t = 0, r = 0, b = -0.25, l = 0, unit = "line"),
    strip.text.x = element_text (size = 10, face = "plain"),
    strip.text.y = element_text (size = 10, face = "plain"),
    strip.background = element_rect(color = "black", fill = ngrey)
  )

# save as tiff file
ggsave(filename = file.path(git_path, "DensityPlot_EffectSizeAide.tiff"), width = 7.25, height = 5.25, units = "in", dpi = 300)

# This is a good reference to walk through customizing facet aes https://www.datanovia.com/en/blog/how-to-change-ggplot-facet-labels/

```


Updates for MSU EEB presentation - just display classes = 4 condition, put edit and spcc on the same plot
```{r}

# Average Accuracy Measures by Encoding treatment and social condition

# TKTK check that the number of rows matches the number of treatments and iterations
# TKTK 4 social and 4 information treatments by 10 iterations should be 160 rows
glimpse(res)

# Summarize the results from the synthetic experiments to calculate the mean and 95% CI per treatment combination (social condition and information encoding condition)

res_summ <- res %>%
  # Make the data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>%
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    tmp = accuracy_type,
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    tmp = gsub(pattern = "_mean", replace = "", tmp)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = tmp, into = c(NA, "accuracy_method", "accuracy_level")) %>%
  # glimpse()
  # Group by the columns that have information about each experimental treatment
  # Operations like this are helpful for avoiding nested loops. This grouping should yield 16 groups across the two experimental treatments (4 x 4), plus the two methods and social levels for accuracy calculations
  dplyr::group_by(n_groups, group_information_proportion, accuracy_method, accuracy_level) %>%
  # Once a data frame is grouped, you can calculate summary statistics by each group
  dplyr::summarise(
    mean_accuracy = mean(accuracy_measurements),
    # Calculate the 95% CI measurements and extract the upper 95% CI value
    upper_95_CI = Rmisc::CI(accuracy_measurements, ci = 0.95)[["upper"]],
    lower_95_CI = Rmisc::CI(accuracy_measurements, ci = 0.95)[["lower"]]
  ) %>%
  # Make sure to ungroup before plotting, and the columns used for grouping will be retained
  ungroup() %>%
  # Reorganize scoial_envt_treatment, so that legend scale goes in order from Sparse to Dense
  # mutate() creates new columns and can be used to modify/overwrite exist columns, like below when reorganizing factor levels
  dplyr::mutate(
    n_groups = factor(n_groups),
    # Convert the x-axis column to factor to control axis ticks
    group_information_proportion = factor(round(group_information_proportion, 2))
  )

# There should be 4 social conditions * 4 information encoding conditions * 2 accuracy methods * 2 social levels in rows, or 64 rows
glimpse(res_summ)

# The levels for the social condition treatment column looks good
levels(res_summ$n_groups)

# Looks good
unique(res_summ$accuracy_method)
unique(res_summ$accuracy_level)

# Then, make color list that contains 1 ,2 4, and 5th color hex codes from paletteer_packages:Arches
# paletteer_d("nationalparkcolors::Arches")
#A8CDECFF #F6955EFF #682C37FF #9B6981FF #7887A4FF #A89F8EFF
# Use #A8CDECFF #F6955EFF #9B6981FF #7887A4FF

cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 0.2)
shps <- c(21, 22, 24, 25) # Also encode social conditions by shape. See the points function for options

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
method_labs <- c("Edit Distance", "SPCC")
names(method_labs) <- c("edit", "SPCC")

# Renaming the Accuracy Information Level labels
level_labs <- c("Group Information", "Individual Information")
names(level_labs) <- c("group", "individual")

#making this in case we want to make the facet background a very very light grey
ngrey <- scales::alpha("grey", .2)

# Make the faceted plot without ggarrange(), no need to make separate plots unless you need more flexibility
res_summ %>%
  dplyr::filter(n_groups == 4) %>%
  dplyr::filter(accuracy_method == "edit") %>%
  ggplot(aes(x = group_information_proportion, y = mean_accuracy)) +
  # linewidth controls the width of the errorbar lines, stroke controls the width of the symbol border
  geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI), linewidth = .85, stroke = .85, position = position_dodge(width = .5)) +
  # Can also use facet_grid()
  # facet_wrap(accuracy_level ~ accuracy_method) +
  facet_grid(
    rows = vars(accuracy_level),
    labeller = labeller(accuracy_level = level_labs, accuracy_method = method_labs)
  ) +
  labs(y = "Average Accurary", x = "Proportion of Group Information") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size=14),
    axis.title = element_text(size=16,face="bold"),
    legend.position = "top",
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    strip.text.x = element_text (size = 14, face = "bold"),
    strip.text.y = element_text (size = 14, face = "bold"),
    strip.background = element_rect(color = "black", fill = "white")
  )

# save as tiff file
ggsave(filename = file.path(git_path, "AverageAccuracy_PointRange_class4_edit.tiff"), width = 5.4, height = 6.4, units = "in", dpi = 300)

# This is a good reference to walk through customizing facet aes https://www.datanovia.com/en/blog/how-to-change-ggplot-facet-labels/

```

MSU EEB presentation: Make a plot of the accuracy values for the edit distance on a single panel, as main results but also in a format that can be used to walk people through the effect size calculations.
```{r}

glimpse(res_summ)

res_summ %>%
  # Filter by edit distance accuracy values for 4 classes
  dplyr::filter(
    accuracy_method == "edit",
    n_groups == 4
  ) %>%
  # Capitalize the group and individual level labels
  dplyr::mutate(
    accuracy_level = gsub("group", "Group", accuracy_level),
    accuracy_level = gsub("individual", "Individual", accuracy_level)
  ) %>%
  ggplot(aes(x = group_information_proportion, y = mean_accuracy, fill = accuracy_level)) +
  # linewidth controls the width of the errorbar lines, stroke controls the width of the symbol border
  geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI), linewidth = 0.85, stroke = 0.85, shape = 21, size = 1) +
  labs(y = "Average Accuracy", x = "Proportion of Group Information") +
  scale_y_continuous(limits = c(0, 1.05)) +
  scale_fill_manual(values = c("white", "gray")) +
  guides(fill = guide_legend(title = "Accuracy Level")) +
  theme_bw() +
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 14),
    # axis.title = element_text(size = 16),
    legend.position = "none",
    # legend.position = "top",
    # legend.title = element_text(size = 16),
    # legend.text = element_text(size = 14),
    strip.background = element_rect(color = "black", fill = "white")
  )

ggsave(filename = file.path(git_path, "MSU_EEB_Accuracy_class4_edit.tiff"), width = 6, height = 2.9, units = "in", dpi = 300)

```


MSU EEB presentation: Make a plot of the accuracy values for the edit distance on a single panel, as main results but also in the same format as above.
```{r}

res_summ %>%
  # Filter by SPCC accuracy values for 4 classes
  dplyr::filter(
    accuracy_method == "SPCC",
    n_groups == 4
  ) %>%
  # Capitalize the group and individual level labels
  dplyr::mutate(
    accuracy_level = gsub("group", "Group", accuracy_level),
    accuracy_level = gsub("individual", "Individual", accuracy_level)
  ) %>%
  ggplot(aes(x = group_information_proportion, y = mean_accuracy, fill = accuracy_level)) +
  # linewidth controls the width of the errorbar lines, stroke controls the width of the symbol border
  geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI), linewidth = 0.85, stroke = 0.85, shape = 21, size = 1) +
  labs(y = "Average Accuracy", x = "Proportion of Group Information") +
  scale_y_continuous(limits = c(0, 1.05)) +
  scale_fill_manual(values = c("white", "gray")) +
  guides(fill = guide_legend(title = "Accuracy Level")) +
  theme_bw() +
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 14),
    # axis.title = element_text(size = 16),
    legend.position = "none",
    # legend.position = "top",
    # legend.title = element_text(size = 16),
    # legend.text = element_text(size = 14),
    strip.background = element_rect(color = "black", fill = "white")
  )

ggsave(filename = file.path(git_path, "MSU_EEB_Accuracy_class4_SPCC.tiff"), width = 6, height = 2.9, units = "in", dpi = 300)

```

MSU EEB presentation: Make effect size plots by method using the same colors as above. This code relies on a different script that writes out the effect size data.
```{r}

eff_res <- read.csv(file.path(data_path, "effect_sizes_byLevel.csv"))
glimpse(eff_res)

# Setting up for plotting
eff_res_level_gg <- eff_res_level %>%
  # Reorganize social_envt_treatment, so that legend scale goes in order from Sparse to Dense
  # mutate() creates new columns and can be used to modify/overwrite exist columns, like below when reorganizing factor levels
  dplyr::mutate(
    # Convert the x-axis column to factor to control axis ticks
    group_information_proportion = factor(round(group_information_proportion, 2)),
    # convert accuracy_level to factor
    accuracy_method = factor(accuracy_method),
    # Convert n_groups to a factor
    n_groups = factor(n_groups)
  )

eff_res_level_gg %>%
  # Filter by edit distance accuracy values for 4 classes
  dplyr::filter(
    accuracy_method == "edit",
    n_groups == 4
  ) %>%
  ggplot(aes(x = group_information_proportion, y = eff_delta)) +
  geom_hline(aes(yintercept = 0), color = "grey") +
  geom_hline(aes(yintercept = 0.474), linetype = "longdash", color = "grey") +
  geom_hline(aes(yintercept = -0.474), linetype = "longdash", color = "grey") +
  geom_pointrange(aes(ymin = eff_CI_lower, ymax = eff_CI_upper), linewidth = 0.85, stroke = 0.85, shape = 24, color = "black", fill = "white", size = 1) +
  labs(y = "Average Cliff's Delta and 95% CI", x = "Proportion of Group Information") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 14),
    # axis.title = element_text(size = 16),
    legend.position = "none",
    # legend.position = "top",
    # legend.title = element_text(size = 16),
    # legend.text = element_text(size = 14),
    strip.text.x = element_text (size = 14, face = "bold"),
    strip.text.y = element_text (size = 14, face = "bold"),
    strip.background = element_rect(color = "black", fill = "white")
  )

# save as tiff file
ggsave(filename = file.path(git_path, "MSU_EEB_EffectSize_class4_edit.tiff"), width = 6, height = 2.9, units = "in", dpi = 300)


```

Same effect size plot but with SPCC data.
```{r}

eff_res_level_gg %>%
  # Filter by edit distance accuracy values for 4 classes
  dplyr::filter(
    accuracy_method == "SPCC",
    n_groups == 4
  ) %>%
  ggplot(aes(x = group_information_proportion, y = eff_delta)) +
  geom_hline(aes(yintercept = 0), color = "grey") +
  geom_hline(aes(yintercept = 0.474), linetype = "longdash", color = "grey") +
  geom_hline(aes(yintercept = -0.474), linetype = "longdash", color = "grey") +
  geom_pointrange(aes(ymin = eff_CI_lower, ymax = eff_CI_upper), linewidth = 0.85, stroke = 0.85, shape = 24, color = "black", fill = "white", size = 1) +
  labs(y = "Average Cliff's Delta and 95% CI", x = "Proportion of Group Information") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 14),
    # axis.title = element_text(size = 16),
    legend.position = "none",
    # legend.position = "top",
    # legend.title = element_text(size = 16),
    # legend.text = element_text(size = 14),
    strip.text.x = element_text (size = 14, face = "bold"),
    strip.text.y = element_text (size = 14, face = "bold"),
    strip.background = element_rect(color = "black", fill = "white")
  )

# save as tiff file
ggsave(filename = file.path(git_path, "MSU_EEB_EffectSize_class4_SPCC.tiff"), width = 6, height = 2.9, units = "in", dpi = 300)


```
