---
title: "Spectrographic cross-correlation and acoustic space"
author: Grace Smith-Vidaurre
output: html_document
date: "2024-11-20"
---

Purpose: Here we use the `warbleR` package to run spectrographic cross-correlation (SPCC) and generate figures of acoustic variation in two dimensional acoustic space. We perform these analyses for synthetic vocal identity signal datasets that contain more group than individual information, and more individual than group information, respectively.

You can run the chunks in this script in order whenever you need to run SPCC from scratch. Once SPCC has been performed, the resulting matrix will be uploaded to the same shared location where audio files are held. You can download this matrix and run the intital chunks through Step 1, then skip Step 2 and continue with subsequent steps to build acoustic space plots.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "warbleR", "paletteer")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Install the paRsynth package from GitHub if you haven't installed it already
# remove.packages("paRsynth")
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/raneemsamman/Desktop" # Raneem's path
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
path <- "~/Desktop" # Grace's path
# path <- "/Users/summe/OneDrive/Desktop/" #Summer's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where audio will be written out/read in
audio_dir <- "audio"

# Combine the base path, the analysis directory, and the audio directory into a single path
audio_path <- file.path(path, analysis_dir, audio_dir)

# Create the audio directory if it doesn't already exist on your computer
if(!dir.exists(audio_path)){ 
  dir.create(audio_path)
}

# Specify a folder inside the analysis directory where images will be written out/read in
images_dir <- "images"

# Combine the base path, the analysis directory, and the data directory into a single path
images_path <- file.path(path, analysis_dir, images_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(images_path)){ 
  dir.create(images_path)
}

# Specify a folder inside the analysis directory where images for figures will be written out/read in
figures_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figures_path <- file.path(path, analysis_dir, figures_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figures_path)){ 
  dir.create(figures_path)
}

```

Read in the synthetic call metadata and set cores for parallel processing.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))
glimpse(synthetic_call_metadata)

cores <- parallel::detectCores() - 4
cores

# Find the maximum frequency anchor value across all vocalizations
freq_cols <- synthetic_call_metadata[, grepl("Frequency", names(synthetic_call_metadata))]
glimpse(freq_cols)

max_freq <- max(sapply(freq_cols, max))
max_freq

```

# Step 1: Create a warbleR selection table
```{r}

# Create a vector of all of the audio files in the analysis path
wavs <- list.files(path = audio_path, pattern = ".wav$", full.names = FALSE)
length(wavs)
head(wavs)

# Iterate over the audio files to create one row of the selection table at a time. warbleR selection tables have a very specific format that must be used for downstream analysis.
sel_tbl <- data.table::rbindlist(pblapply(1:length(wavs), function(w){
  
  tmp <- tuneR::readWave(file.path(audio_path, wavs[w]))
  
  # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
  metadats_tmp <- synthetic_call_metadata %>%
    dplyr::filter(grepl(wavs[w], audio_file_name))
  
  # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
  if(nrow(metadats_tmp) > 0){
    
    # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
    # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1,
      start = 0.1, 
      end = seewave::duration(tmp) - 0.1,
      sampling_rate = tmp@samp.rate,
      group_ID = metadats_tmp[["Group"]],
      individual_ID = metadats_tmp[["Individual"]],
      call = metadats_tmp[["Call"]],
      call_ID = metadats_tmp[["Call_ID"]],
      dataset = metadats_tmp[["dataset"]]
    )
    
  } else {
    
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1, 
      start = 0.1, 
      end = seewave::duration(tmp) + 0.1,
      sampling_rate = NA,
      group_ID = NA,
      individual_ID = NA,
      call = NA,
      call_ID = NA,
      dataset = NA
    )
    
  }
  
  return(res)
  
}))

# See the selection table in warbleR format with useful metadata for acoustic space plots
glimpse(sel_tbl)

# Looks good, a single sampling rate across files
unique(sel_tbl$sampling_rate)

```

# Step 2. Perform spectrographic cross-correlation (SPCC) to measure acoustic similarity of all calls in dataset (pairwise similarity matrix)

If the `temperature` argument used by `soundgen` is set to 0 (for no stochasticity in sound generation), then you will need to filter out any calls that have duplicated strings prior to running cross-correlation. Otherwise you will have values of 1 outside of the diagonal representing comparisons among calls of exactly the same structure or duplicates, and multidimensional scaling will fail.

Here SPCC is performed across both synthetic vocalization datasets, so that the acoustic space shown below will be a universal space across figures.

```{r}

# When generating the synthetic vocalizations, increasing the temperature from 0 to 0.025 reduced the number of ones off of the diagonal to 1. I just increased temperature to 0.05 and there was still a single 1 off of the diagonal
# (max_freq/1000): The maximum frequency in the bandwidth argument was 7 kHz, add 2 kHz for a buffer
xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 9), wn = "hanning", cor.method = "pearson", parallel = cores, na.rm = FALSE, type = "spectrogram", path = audio_path)

str(xc_mat)
dim(xc_mat)

# Checking, get the percentage of unique values that are negative
neg_values <- length(xc_mat[xc_mat < 0]) / (dim(xc_mat)[1] * dim(xc_mat)[2])
neg_values # No negative values, looks good

# No values of 1 off of the diagonal, looks good
ones <- ((length(which(xc_mat[lower.tri(xc_mat)] > 0.999999))*2) / length(xc_mat)) * 100
ones

# Update the dimension names of the matrix
dimnames(xc_mat) <- list(sel_tbl$sound.files, sel_tbl$sound.files)

# Save this matrix since it can take a long time to generate when there are many vocalizations
saveRDS(xc_mat, file.path(analysis_path, "xc_mat.RDS"))

```

# Step 3: Calculate the edit distance amongst all strings
```{r}

xc_mat <- readRDS(file.path(analysis_path, "xc_mat.RDS"))

# For each pairwise comparison in the same order as SPCC, calculate the edit distance for the original strings, then assemble this vector into a matrix
edit_dists <- unlist(lapply(1:nrow(xc_mat), function(m){
  lapply(1:ncol(xc_mat), function(p){
    
    return(
      stringdist(
        a = sel_tbl %>% 
          dplyr::filter(
            sound.files == dimnames(xc_mat)[[1]][m]
          ) %>% 
          pull(call),
        b = sel_tbl %>% 
          dplyr::filter(
            sound.files == dimnames(xc_mat)[[2]][p]
          ) %>% 
          pull(call),
        method = "lv"
      )
    )
    
  })
}))

edit_mat <- matrix(edit_dists, nrow = nrow(xc_mat), ncol = ncol(xc_mat), byrow = TRUE)
dim(edit_mat)

# Check for values of 0 off of the diagonal. This will happen by chance when the exact same strings are generated within an individual (even with the random variation, and especially when there are few characters devoted to encoding random variation for within-individual variation).
zeroes <- ((length(which(edit_mat[lower.tri(edit_mat)] == 0))*2)/length(edit_mat)) * 100
zeroes

# hist(edit_mat[lower.tri(edit_mat)])

# The code below replaces edit distance values of 0 off of the diagonal with a small number close to 0. The lowest non-zero value in the edit distance matrix is 1. Replace zeroes off of the diagonal with 1/10th of this value, or 0.1.

# Get the minimum non-zero similarity value in the matrix
min_vals <- edit_mat[lower.tri(edit_mat)]

# Then get the smallest non-zero value, which should be 1. Looks good
sec_min_val <- min(min_vals[min_vals > 0])
# sec_min_val

# Then set the values of 1 off of the diagonal (in both the upper and lower triangle) to 1/10th of 1, the smallest non-zero value in this matrix
edit_mat[lower.tri(edit_mat)][edit_mat[lower.tri(edit_mat)] == 0] <- round(sec_min_val/10, 8)
edit_mat[upper.tri(edit_mat)][edit_mat[upper.tri(edit_mat)] == 0] <- round(sec_min_val/10, 8)

# Update the dimension names of the matrix
dimnames(edit_mat) <- list(sel_tbl$sound.files, sel_tbl$sound.files)

# Save this matrix since it can take a long time to generate when there are many vocalizations
saveRDS(edit_mat, file.path(analysis_path, "edit_mat.RDS"))

```

# Step 4: Reduce the dimensionality of the SPCC and edit distance matrices with multidimensional scaling.
```{r}

xc_mat <- readRDS(file.path(analysis_path, "xc_mat.RDS"))
str(xc_mat)

# Convert to a distance matrix and dist object for isoMDS
dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
str(dist_mat)

# Perform multidimensional scaling (MDS) over many dimensions to reduce stress using a rule of thumb that 5% (or 5 in the stress result below) is "low" stress. Then use the first two dimensions of the resulting solution to build an acoustic space plot
iso_spcc <- invisible(MASS::isoMDS(dist_mat, k = 15, maxit = 1000, trace = FALSE))
str(iso_spcc)

str(iso_spcc$points)
# View(iso_spcc$points)

# Create a data frame for plotting that contains the coordinates per call in each the two dimensions in the new low-dimensional space as well as useful metadata 
mds_spcc <- data.frame(
  sound.files = dimnames(xc_mat)[[1]],
  X = as.vector(iso_spcc$points[, 1]), 
  Y = as.vector(iso_spcc$points[, 2])
) %>% 
  inner_join(
    sel_tbl %>% 
      dplyr::select(sound.files, group_ID, individual_ID, dataset),
    by = c("sound.files")
  ) %>%
  dplyr::mutate(
    unique_individuals = paste(group_ID, individual_ID, sep = " - "),
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID),
    unique_individuals = factor(unique_individuals),
    dataset = gsub("_", " ", dataset),
    dataset = factor(dataset)
  )

glimpse(mds_spcc)

```

```{r}

edit_mat <- readRDS(file.path(analysis_path, "edit_mat.RDS"))
str(edit_mat)

# Convert to a dist object for isoMDS (this is already a distance matrix and should not be subtracted from 1)
dist_mat <- stats::as.dist(edit_mat, diag = TRUE, upper = TRUE)
str(dist_mat)

# Perform multidimensional scaling (MDS) over many dimensions to reduce stress using a rule of thumb that 5% (or 5 in the stress result below) is "low" stress. Then use the first two dimensions of the resulting solution to build an acoustic space plot
iso_edit <- invisible(MASS::isoMDS(dist_mat, k = 15, maxit = 1000, trace = FALSE))
str(iso_edit)

# Create a data frame for plotting that contains the coordinates per call in each the two dimensions in the new low-dimensional space as well as useful metadata 
mds_edit <- data.frame(
  sound.files = dimnames(edit_mat)[[1]],
  X = as.vector(iso_edit$points[, 1]), 
  Y = as.vector(iso_edit$points[, 2])
) %>% 
  inner_join(
    sel_tbl %>% 
      dplyr::select(sound.files, group_ID, individual_ID, dataset),
    by = c("sound.files")
  ) %>%
  dplyr::mutate(
    unique_individuals = paste(group_ID, individual_ID, sep = " - "),
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID),
    unique_individuals = factor(unique_individuals),
    dataset = gsub("_", " ", dataset),
    dataset = factor(dataset)
  )

glimpse(mds_edit)

```

# Step 5: Generate low-dimensional acoustic space plots

Calls from both datasets in the same universal acoustic space (SPCC). Start with aesthetics.
```{r}

mds_df_all <- mds_spcc %>%
  # Create a column that combines dataset and group
  dplyr::mutate(
    dataset_group = paste(dataset, group_ID, sep = "-"),
    dataset_group = factor(dataset_group)
  )

length(levels(mds_df_all$dataset_group))
length(levels(mds_df_all$group))

# Get colors for groups from the same palette used for spectrograms in lexicons
cols <- paletteer::paletteer_d("nationalparkcolors::Arches")
cols

# Colors by group (five) per dataset (two), ten total
cols <- rep(cols[1:length(levels(mds_df_all$group))], length(levels(mds_df_all$dataset)))
cols

# Shapes by dataset across groups
# The solid circles (19) are the group membership dataset vocalizations
shps <- rep(c(19, 23), length(levels(mds_df_all$group_ID)))

length(cols)
length(shps)

hulls <- plyr::ddply(mds_df_all, "dataset_group", function(x){
  x[chull(x$X, x$Y), ]
})

glimpse(hulls)

```

Create plots of both datasets with group-level polygons in SPCC and edit distance acoustic space, these will be supplementary figures.
```{r}

mds_df_all %>% 
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = dataset_group), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = dataset), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  # The legend is currently on but should be modified downstream as needed
  guides(color = guide_legend(title = "Group ID", override.aes = list(size = 3)), shape = guide_legend(title = "Dataset", override.aes = list(size = 3)), fill = guide_legend(title = "Group ID", override.aes = list(size = 3))) +
  # Uncomment this line to remove the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  # scale_x_continuous(limits = c(-0.5, 0.5), breaks = seq(-0.5, 0.5, 0.05), labels = sprintf("%.2f", round(seq(-0.5, 0.5, 0.05), 2))) +
  # scale_y_continuous(limits = c(-0.5, 0.5), breaks = seq(-0.5, 0.5, 0.05), labels = sprintf("%.2f", round(seq(-0.5, 0.5, 0.05), 2))) +
  # facet_wrap(~ dataset) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(linewidth = 0.25),
    legend.position = "top",
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    legend.key.spacing = unit(0.15, "lines"),
    legend.box.spacing =  unit(0.1, "lines"),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_bothDatasets.tiff"), width = 6, height = 4, units = "in", dpi = 300)

```

The same plot, but the edit distance.
```{r}

mds_df_all <- mds_edit %>%
  # Create a column that combines dataset and group
  dplyr::mutate(
    dataset_group = paste(dataset, group_ID, sep = "-"),
    dataset_group = factor(dataset_group)
  )

hulls <- plyr::ddply(mds_df_all, "dataset_group", function(x){
  x[chull(x$X, x$Y), ]
})

mds_df_all %>% 
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = dataset_group), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = dataset), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  # The legend is currently on but should be modified downstream as needed
  guides(color = guide_legend(title = "Group ID", override.aes = list(size = 3)), shape = guide_legend(title = "Dataset", override.aes = list(size = 3)), fill = guide_legend(title = "Group ID", override.aes = list(size = 3))) +
  # Uncomment this line to remove the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  # scale_x_continuous(limits = c(-0.35, 0.4), breaks = seq(-0.35, 0.4, 0.05), labels = sprintf("%.2f", round(seq(-0.35, 0.4, 0.05), 2))) +
  # scale_y_continuous(limits = c(-0.25, 0.35), breaks = seq(-0.25, 0.35, 0.05), labels = sprintf("%.2f", round(seq(-0.25, 0.35, 0.05), 2))) +
  # facet_wrap(~ dataset) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    legend.key.spacing = unit(0.15, "lines"),
    legend.box.spacing =  unit(0.1, "lines"),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_edit_bothDatasets.tiff"), width = 6, height = 4, units = "in", dpi = 300)

```

# Main figures

Group membership, two plots (SPCC and edit distance, one above the other) with convex hull polygons by group. Start with aesthetics.
```{r}

# Get colors for groups from the same palette used for spectrograms in lexicons
cols <- paletteer::paletteer_d("nationalparkcolors::Arches")
cols

# Combine MDS results from the SPCC and edit distance pipelines
mds_spcc_grp <- mds_spcc %>%
  # Create a column to indicate the method
  dplyr::mutate(
    method = "Spectrographic cross-correlation"
  ) %>%
  # Filter by the group membership calls
  dplyr::filter(
    dataset == "Group Membership"
  )

glimpse(mds_spcc_grp)

mds_edit_grp <- mds_edit %>%
  # Create a column to indicate the method
  dplyr::mutate(
    method = "Edit distance"
  ) %>%
  # Filter by the group membership calls
  dplyr::filter(
    dataset == "Group Membership"
  )

glimpse(mds_edit_grp)

levels(mds_spcc_grp$group_ID)
levels(mds_spcc_grp$individual_ID)
levels(mds_spcc_grp$unique_individuals)

# Colors by group (five)
cols_grp <- cols[1:length(levels(mds_spcc_grp$group))]

# Shapes by individual within groups
shps <- rep(c(0, 1, 2, 4, 16, 17, 21, 23, 24, 6), length(levels(mds_spcc_grp$group_ID)))

```

Create the group membership plots. Edit distance first with a legend.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_edit_grp, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_edit_grp %>%
  ggplot(aes(x = X, y = Y, color = group_ID)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID, color = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = group_ID, color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = cols_grp) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", nrow = 1), fill = guide_legend(title = "Group", order = 1)) +
  # Uncomment this line to turn off the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-5, -1.8), breaks = seq(-5, -2, 1), labels = sprintf("%.2f", round(seq(-5, -2, 1), 2))) +
  scale_y_continuous(limits = c(-4.5, 4), breaks = seq(-4, 4, 1), labels = sprintf("%.2f", round(seq(-4, 4, 1), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines")
  )

# Save this plot as an image file
# This is the image size that will be written without a legend
# ggsave(filename = file.path(figures_path, "AcousticSpace_edit_GroupMembership.tiff"), width = 6, height = 4, units = "in", dpi = 300)

# This is the image size that will be written to create a legend for the composite figure created in other software
ggsave(filename = file.path(figures_path, "AcousticSpace_edit_GroupMembership_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

SPCC next, no legend.
```{r}

# Convex hull polygons per group
hulls <- plyr::ddply(mds_spcc_grp, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_spcc_grp %>%
  ggplot(aes(x = X, y = Y, color = group_ID)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID, color = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = group_ID, color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols_grp) +
  scale_fill_manual(values = cols_grp) +
  xlab("") + ylab("") + 
  # guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", override.aes = list(size = 3), nrow = 1), fill = guide_legend(title = "Group", override.aes = list(size = 3), order = 1)) +
  # Uncomment this line to turn off the legend
  guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.3, 0), breaks = seq(-0.3, 0, 0.05), labels = sprintf("%.2f", round(seq(-0.3, 0, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.35, 0.25), breaks = seq(-0.35, 0.25, 0.1), labels = sprintf("%.2f", round(seq(-0.35, 0.25, 0.1), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3),
    legend.position = "top",
    legend.key.spacing = unit(0.2, "lines")
  )

# Save this plot as an image file
# This is the image size that will be written without a legend
ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_GroupMembership.tiff"), width = 6, height = 4, units = "in", dpi = 300)

# This is the image size that will be written to create a legend for the composite figure created in other software
# ggsave(filename = file.path(figures_path, "AcousticSpace_SPCC_GroupMembership_Legend.tiff"), width = 8, height = 4, units = "in", dpi = 300)

```

Individual identity. Two plots (SPCC and edit distance) with convex hull polygons by individual. Start with aesthetics.
```{r}

# Combine MDS results from the SPCC and edit distance pipelines
mds_spcc_ind <- mds_spcc %>%
  # Create a column to indicate the method
  dplyr::mutate(
    method = "Spectrographic cross-correlation"
  ) %>% 
  # Filter by the group membership calls
  dplyr::filter(
    dataset == "Individual Identity"
  )

glimpse(mds_spcc_ind)

mds_edit_ind <- mds_edit %>%
  # Create a column to indicate the method
  dplyr::mutate(
    method = "Edit distance"
  ) %>%
  # Filter by the group membership calls
  dplyr::filter(
    dataset == "Individual Identity"
  )

glimpse(mds_edit_ind)

levels(mds_spcc_ind$group_ID)
levels(mds_spcc_ind$individual_ID)
levels(mds_spcc_ind$unique_individuals)

# Border colors by group (five)
# cols <- scales::alpha(c("navy", "orange", "forestgreen", "firebrick", "grey5"), 0.65)

# Get colors for groups from the same palette used for spectrograms in lexicons
cols <- paletteer::paletteer_d("nationalparkcolors::Arches")
cols

# Colors by group (five) repeated per individual
cols <- cols[1:length(levels(mds_spcc_grp$group))]
cols

# Fills by unique individual
levels(mds_edit_ind$unique_individuals)
fills <- rep(cols, each = 10)

# Shapes by individual within groups
shps <- rep(c(7, 8, 10, 4, 16, 17, 21, 23, 24, 6), length(levels(mds_spcc_ind$group_ID)))

```

TKTK fixed the polygons but need to add labels to strip legends and fix the legend falling off the edge in the image file.

Edit distance first with a legend.
```{r}

# glimpse(mds_edit_ind)

hulls <- plyr::ddply(mds_edit_ind, "unique_individuals", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

glimpse(mds_edit_ind)

mds_edit_ind %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = unique_individuals), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  # facet_wrap(~ group_ID) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fills) +
  xlab("") + ylab("") + 
  guides(color = guide_legend(title = "Group", override.aes = list(size = 3), order = 1), shape = guide_legend(title = "Individual", override.aes = list(size = 3), nrow = 1), fill = guide_legend(title = "Group", override.aes = list(size = 3), order = 1)) +
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(2, 4.5), breaks = seq(2, 4.5, 1), labels = sprintf("%.2f", round(seq(2, 4.5, 1), 2))) +
  scale_y_continuous(limits = c(-4.1, 4), breaks = seq(-4, 4, 2), labels = sprintf("%.2f", round(seq(-4, 4, 2), 2))) +
  theme_bw() +
  theme(
    legend.position = "top",
    legend.key.spacing = unit(0.2, "line"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_edit_IndividualIdentity_Legend.tiff"), width = 6, height = 4, units = "in", dpi = 300)

```

SPCC next without a legend.