---
title: "Generate spectrogram image files"
output: html_document
date: "2024-11-20"
---

Purpose: Here we generate spectrogram image files for two synthetic datasets of vocal identity signals with more group than individual information an vice versa. We use the `warbleR` package to generate spectrograms. These original spectrogram image files can be read back into R for further modification (e.g. resizing, adding color borders) prior to creating composite figures of lexicons in Inkscape.

For this script to work, you will need to either run the script `Generate_SyntheticDatasets.Rmd` to create the synthetic vocal identity signals, or you will need to access files we have already created that are stored in a shared location. If you want to reproduce the same results, then we recommend using the files stored in a shared location.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "warbleR", "ggpubr", "paletteer")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/raneemsamman/Desktop" # Raneem's path
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
path <- "C:/Users/britt/Desktop" #Brittany's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where audio will be written out/read in
audio_dir <- "audio"

# Combine the base path, the analysis directory, and the audio directory into a single path
audio_path <- file.path(path, analysis_dir, audio_dir)

# Create the audio directory if it doesn't already exist on your computer
if(!dir.exists(audio_path)){ 
  dir.create(audio_path)
}

# Specify a folder inside the analysis directory where images will be written out/read in
images_dir <- "images"

# Combine the base path, the analysis directory, and the data directory into a single path
images_path <- file.path(path, analysis_dir, images_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(images_path)){ 
  dir.create(images_path)
}

```

Read in the synthetic call metadata.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))

glimpse(synthetic_call_metadata)

```

# Step 1: Create a warbleR selection table
```{r}

# Create a vector of all of the audio files in the analysis path
wavs <- list.files(path = audio_path, pattern = ".wav$", full.names = FALSE)
length(wavs)
head(wavs)

# Iterate over the audio files to create one row of the selection table at a time. warbleR selection tables have a very specific format that must be used for downstream analysis.
sel_tbl <- data.table::rbindlist(pblapply(1:length(wavs), function(w){
  
  tmp <- tuneR::readWave(file.path(audio_path, wavs[w]))
  
  # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
  metadats_tmp <- synthetic_call_metadata %>%
    dplyr::filter(grepl(wavs[w], audio_file_name))
  
  # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
  if(nrow(metadats_tmp) > 0){
    
    # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
    # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1,
      start = 0.1, 
      end = seewave::duration(tmp) - 0.1,
      sampling_rate = tmp@samp.rate,
      group_ID = metadats_tmp[["Group"]],
      individual_ID = metadats_tmp[["Individual"]],
      call_ID = metadats_tmp[["Call"]]
    )
    
  } else {
    
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1, 
      start = 0.1, 
      end = seewave::duration(tmp) + 0.1,
      sampling_rate = NA,
      group_ID = NA,
      individual_ID = NA,
      call_ID = NA
    )
    
  }
  
  return(res)
  
}))

# See the selection table in warbleR format with all useful metadata for the synthetic experiment
glimpse(sel_tbl)

# Looks good, a single sampling rate across files
unique(sel_tbl$sampling_rate)

```

# Step 2: Create spectrogram image files of each audio file
```{r}

warbleR::spectrograms(sel_tbl, wl = 512, flim = c(0, 12), wn = "hanning", pal = reverse.gray.colors.2,ovlp = 90, inner.mar = c(5, 4, 4, 2), outer.mar = c(0, 0, 0, 0), picsize = 1, res = 100, cexlab = 1, propwidth = FALSE, xl = 1, osci = FALSE, gr = FALSE, sc = FALSE, line = FALSE, mar = 0.05, it = "jpeg", parallel = 1, path = audio_path, pb = TRUE, fast.spec = FALSE, by.song = NULL, sel.labels = NULL, title.labels = NULL, dest.path = images_path, box = TRUE, axis = TRUE)

# Rename the image files to remove the -1 appended after the extension
imgs <- list.files(images_path)
imgs

new_nms <- gsub(".wav-1", "", imgs)
new_nms

invisible(file.rename(file.path(images_path, imgs), file.path(images_path, new_nms)))

```

# Step 3: Manually upload the original image files to a shared location

The image files were uploaded to a shared Google Drive folder that also contains the audio files.


# Step 4: Select Spectrograms to use.
We need calls from two datasets: Group Dataset and Individual Dataset. For each dataset, we need vocalizations from two sample groups. We will sample from 2 individuals in those two groups, and samples 2 vocalizations per individual. In total, we need 8 vocalizations per dataset, 16 vocalizations total.

I (Brittany) chose the following:

Group dataset
Group1: Individual 1 (calls 1 and 3), Individual 3 (calls 1 and 3)
Group 2: Individual 4 (calls 1 and 2), Individual 6 (calls 1 and 2)

Individual Information Dataset
Group 4: Individual 6 (calls 2 and 4), Individual 10 (calls 1 and 3)
Group 5: Individual 9 (calls 4 and 5), Individual 10 (calls 4 and 5)

So, Group Data Set
GroupMembership_Group1_Indiv1_Call1
GroupMembership_Group1_Indiv1_Call3
GroupMembership_Group1_Indiv3_Call1
GroupMembership_Group1_Indiv3_Call3

GroupMembership_Group2_Indiv4_Call1
GroupMembership_Group2_Indiv4_Call2
GroupMembership_Group2_Indiv6_Call1
GroupMembership_Group2_Indiv6_Call2

Individual Data Set
IndividualIdentity_Group4_Indiv6_Call2
IndividualIdentity_Group4_Indiv6_Call4
IndividualIdentity_Group4_Indiv10_Call1
IndividualIdentity_Group4_Indiv10_Call3

IndividualIdentity_Group5_Indiv9_Call4
IndividualIdentity_Group5_Indiv9_Call5
IndividualIdentity_Group5_Indiv10_Call4
IndividualIdentity_Group5_Indiv10_Call5


#Step 5: Read the spectrogram image files back in for resizing to make publication quality

TKTK Brittany working here. 

Step 2: generate new image files of spectros using ggspectro (150 - 200 in the example code). These should have correct text on x and y axis (numbers: time (s) frequency (KHz)), not necessarily titles. text also needs to be correct font size. 

Iterate loop over the 16 files selected, pull from selection table (in each iteration pull the name from the selection table). next step, read in the audio file for that call. Then run ggspectro code (189-198 in example code).

gg <- ggspectro(wave = WAV, f = WAV@samp.rate, ovlp = 90)+ 
^^WAV here stands for the object i create when reading in audio file for selected call
doublecheck axis limits and brteaks in those limits (for example file is closer to .8 (in limits specified))

```{r}

## First make the spectrograms for the Group Information Lexicon 

#generate new image files of spectros using ggspectro. These should have correct text on x and y axis (numbers: time (s) frequency (KHz)), not necessarily titles. text also needs to be correct font size. 
#x label formatter
s_formatter <- function(x){
  # lab <- paste0(x, " s")
  lab <- sprintf("%0.2f", x)
}

# y label formatter
khz_formatter <- function(y){
  lab <- paste0(y)
  # lab <- paste0(y, " kHz")
}

#kept this loop the same from code Grace used previously, setting should transfer over to these spectros (thigs like font size ect)
oscillo_theme_dark <- theme(
  panel.grid.major.y = element_blank(),
  panel.grid.major.x = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill = "transparent"),
  panel.border = element_rect(linetype = "solid", fill = NA, color = "grey"),
  axis.line = element_line(size = 0.15),
  legend.position = "none",
  plot.background = element_rect(fill = "white"),
  plot.margin = unit(c(0, 0, 0.1, 0.1), "lines"), # top, right, bottom, left
  axis.title = element_blank(),
  axis.text = element_text(size = 6.5, color = "black", vjust = 0),
  axis.ticks = element_line(color = "black", size = 0.15)
)

gray_colors <- reverse.gray.colors.2(12)

x11()

# TKTK HELP, I can't figure out how to pull form the selection table or how to iterate this
#Iterate loop over the 16 files selected, pull from selection table (in each iteration pull the name from the selection table). next step, read in the audio file for that call. Then run ggspectro code (189-198 in example code).

# attributes(synthetic_call_metadata) #audio_file_name


# The native range calls, x-axis limits up to 0.24 s
invisible(pblapply(1:nrow(tmp_est_nat), function(w){
  
  gg <- ggspectro(wave = attr(tmp_est_nat, "wave.objects")[[w]], f = attr(tmp_est_nat, "wave.objects")[[w]]@samp.rate, ovlp = 90)+ 
    scale_x_continuous(limits = c(0.04, 0.26), breaks = seq(from = 0.04, to = 0.24, by = 0.04), labels = s_formatter, expand = c(0, 0))+
    scale_y_continuous(limits = c(0.5, 6.75), breaks = seq(from = 1, to = 6, by = 1), expand = c(0, 0), labels = khz_formatter, position = "left")+
    geom_raster(aes(fill = amplitude), hjust = 0, vjust = 0, interpolate = TRUE) +
    scale_fill_gradientn(colours = gray_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-30, 0)) +
    oscillo_theme_dark
  
  print(gg)
  
  ggsave(file.path(gpath, paste(tmp_est_nat$sound.files[w], "-1.jpeg", sep = "")), dpi = 300, units = "px", width = 425, height = 300)
  
}))
```

#Step 6: Adding border to individuals and groups

Color Palette should be paletteer ("nationalparkcolors::Arches")
6 colors, hex codes: #A8CDECFF #F6955EFF #682C37FF #9B6981FF #7887A4FF #A89F8EFF TKTK need to add this chunk to figure codes so that all figures use the same scheme

```{r}

#my_col <- paletteer::paletteer_d("nationalparkcolors::Arches")
#print (my_col)

```
 

