---
title: "Spectrographic cross-correlation and acoustic space"
output: html_document
date: "2024-11-20"
---

Purpose: Here we use the `warbleR` package to run spectrographic cross-correlation and generate figures of acoustic variation in two dimensional acoustic space. We perform these analyses for synthetic vocal identity signal datasets that contain more group than individual information, and more individual than group information, respectively.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "warbleR", "paletteer")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Install the paRsynth package from GitHub if you haven't installed it already
# remove.packages("paRsynth")
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
# X <- c(X, "paRsynth")

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/raneemsamman/Desktop" # Raneem's path
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
path <- "~/Desktop" # Grace's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where audio will be written out/read in
audio_dir <- "audio"

# Combine the base path, the analysis directory, and the audio directory into a single path
audio_path <- file.path(path, analysis_dir, audio_dir)

# Create the audio directory if it doesn't already exist on your computer
if(!dir.exists(audio_path)){ 
  dir.create(audio_path)
}

# Specify a folder inside the analysis directory where images will be written out/read in
images_dir <- "images"

# Combine the base path, the analysis directory, and the data directory into a single path
images_path <- file.path(path, analysis_dir, images_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(images_path)){ 
  dir.create(images_path)
}


# Specify a folder inside the analysis directory where images for figures will be written out/read in
figures_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figures_path <- file.path(path, analysis_dir, figures_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figures_path)){ 
  dir.create(figures_path)
}

```

Read in the synthetic call metadata and set cores for parallel processing.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))

glimpse(synthetic_call_metadata)

cores <- parallel::detectCores() - 2
cores

```

# Step 1: Create a warbleR selection table
```{r}

# Create a vector of all of the audio files in the analysis path
wavs <- list.files(path = audio_path, pattern = ".wav$", full.names = FALSE)
length(wavs)
head(wavs)

# Iterate over the audio files to create one row of the selection table at a time. warbleR selection tables have a very specific format that must be used for downstream analysis.
sel_tbl <- data.table::rbindlist(pblapply(1:length(wavs), function(w){
  
  tmp <- tuneR::readWave(file.path(audio_path, wavs[w]))
  
  # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
  metadats_tmp <- synthetic_call_metadata %>%
    dplyr::filter(grepl(wavs[w], audio_file_name))
  
  # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
  if(nrow(metadats_tmp) > 0){
    
    # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
    # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1,
      start = 0.1, 
      end = seewave::duration(tmp) - 0.1,
      sampling_rate = tmp@samp.rate,
      group_ID = metadats_tmp[["Group"]],
      individual_ID = metadats_tmp[["Individual"]],
      call_ID = metadats_tmp[["Call"]],
      dataset = metadats_tmp[["dataset"]]
    )
    
  } else {
    
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1, 
      start = 0.1, 
      end = seewave::duration(tmp) + 0.1,
      sampling_rate = NA,
      group_ID = NA,
      individual_ID = NA,
      call_ID = NA,
      dataset = NA
    )
    
  }
  
  return(res)
  
}))

# See the selection table in warbleR format with useful metadata for acoustic space plots
glimpse(sel_tbl)

# Looks good, a single sampling rate across files
unique(sel_tbl$sampling_rate)

```

# Step 2. Perform spectrogrphic cross-correlation (SPCC) to measure acoustic similarity of all calls in dataset (pairwise similarity matrix)

If the `temperature` argument used by `soundgen` is set to 0 (for no stochasticity in sound generation), then you will need to filter out any calls that have duplicated strings prior to running cross-correlation. Otherwise you will have values of 1 outside of the diagonal representing comparisons among calls of exactly the same structure or duplicates, and multidimensional scaling will fail.

Here SPCC is performed across both synthetic vocalization datasets, so that the acoustic space shown below will be a universal space across figures.
```{r}

xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 20), wn = "hanning", cor.method = "pearson", parallel = 1, na.rm = FALSE, type = "spectrogram", path = audio_path)

str(xc_mat)
dim(xc_mat)

# Get the percentage of values that are negative
neg_values <- length(xc_mat[xc_mat<0])/(dim(xc_mat)[1]*dim(xc_mat)[2])

# Stop if the percentage of negative values is > 0%
if(neg_values > 0){
  stop("Negative values are present in the spectrographic cross-correlation matrix")
}

# Update the dimension names of the matrix
dimnames(xc_mat) <- list(sel_tbl$sound.files, sel_tbl$sound.files)

# Save this matrix since it can take a long time to generate when there are many vocalizations
saveRDS(xc_mat, file.path(analysis_path, "xc_mat.RDS"))

```

# Step 3: Consider creating heatmaps to visually represent the similarities and differences across categories at different levels

Here the question would be: are we creating the expected patterns of acoustic variation. Complementary to acoustic space plots

# Step 4: Reduce the dimensionality of the SPCC matrix with multidimensional scaling.
```{r}

xc_mat <- readRDS(file.path(analysis_path, "xc_mat.RDS"))
str(xc_mat)

# Convert to a distance matrix and dist object for isoMDS
dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
str(dist_mat)

# Perform multidimensional scaling (MDS) over many dimensions to reduce stress using a rule of thumb that 5% (or 5 in the stress result below) is "low" stress. Then use the first two dimensions of the resulting solution to build an acoustic space plot
iso <- invisible(MASS::isoMDS(dist_mat, k = 15, maxit = 1000, trace = FALSE))
str(iso)

# Create a data frame for plotting that contains the coordinates per call in each the two dimensions in the new low-dimensional space as well as useful metadata 
mds_df <- data.frame(
  sound.files = dimnames(xc_mat)[[1]],
  X = as.vector(iso$points[, 1]), 
  Y = as.vector(iso$points[, 2])
) %>% 
  inner_join(
    sel_tbl %>% 
      dplyr::select(sound.files, group_ID, individual_ID, dataset),
    by = c("sound.files")
  ) %>%
  dplyr::mutate(
    unique_individuals = paste(group_ID, individual_ID, sep = " - "),
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID),
    unique_individuals = factor(unique_individuals),
    dataset = gsub("_", " ", dataset),
    dataset = factor(dataset)
  )

glimpse(mds_df)

```

# Step 5: Generate low-dimensional acoustic space plots

Calls from both datasets in the same universal acoustic space. Start with aesthetics.
```{r}

mds_df_all <- mds_df %>%
  # Create a column that combines dataset and group
  dplyr::mutate(
    dataset_group = paste(dataset, group_ID, sep = "-"),
    dataset_group = factor(dataset_group)
  )

length(levels(mds_df_all$dataset_group))

# Colors by group (five) per dataset (two), ten total
cols <- rep(scales::alpha(c("navy", "orange", "forestgreen", "firebrick", "grey5"), 0.65), length(levels(mds_df_all$dataset)))

# Shapes by dataset across groups
# The solid circles (19) are the group membership dataset vocalizations
shps <- rep(c(19, 23), length(levels(mds_df_all$group_ID)))

length(cols)
length(shps)

hulls <- plyr::ddply(mds_df_all, "dataset_group", function(x){
  x[chull(x$X, x$Y), ]
})

glimpse(hulls)

```

Create the plot.
```{r}

mds_df_all %>% 
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = dataset_group), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = dataset), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  # The legend is currently on but should be modified downstream as needed
  guides(color = guide_legend(title = "Group ID", override.aes = list(size = 3)), shape = guide_legend(title = "Dataset", override.aes = list(size = 3)), fill = guide_legend(title = "Group ID", override.aes = list(size = 3))) +
  # Uncomment this line to remove the legend
  # guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    legend.position = "top",
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    legend.key.spacing = unit(0.15, "lines"),
    legend.box.spacing =  unit(0.1, "lines"),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_bothDatasets.tiff"), width = 6, height = 4, units = "in", dpi = 300)

```

Group membership, two panels (convex hull polygons by group then individual). Start with aesthetics.
```{r}

mds_df_grp <- mds_df %>%
  # Filter by the group membership calls
  dplyr::filter(
    dataset == "Group Membership"
  )

levels(mds_df_grp$group_ID)
levels(mds_df_grp$individual_ID)
levels(mds_df_grp$unique_individuals)

# Colors by group (five)
cols <- scales::alpha(c("navy", "orange", "forestgreen", "firebrick", "grey5"), 0.65)

# Fill colors by individuals across groups. One color per group and individuals are coded in hues
fills <- c(
  paletteer_c("ggthemes::Blue", length(levels(mds_df_grp$individual_ID))),
  paletteer_c("ggthemes::Brown", length(levels(mds_df_grp$individual_ID))),
  paletteer_c("ggthemes::Green", length(levels(mds_df_grp$individual_ID))),
  paletteer_c("ggthemes::Red", length(levels(mds_df_grp$individual_ID))),
  paletteer_c("ggthemes::Gray", length(levels(mds_df_grp$individual_ID)))
)

# Shapes by individual within groups
shps <- rep(c(0, 1, 2, 4, 16, 17, 21, 23, 24, 6), length(levels(mds_df_grp$group_ID)))

```

Create the group membership plots.
```{r}

# Panel A: Convex hull polygons per group

hulls <- plyr::ddply(mds_df_grp, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_df_grp %>%
  ggplot(aes(x = X, y = Y, color = group_ID)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID, color = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = group_ID, color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_GroupMembership_GroupPolygons.tiff"), width = 6, height = 4, units = "in", dpi = 300)


# Panel B: Convex hull polygons per individual

# Regenerate the convex hull polygons by a different social level
hulls <- plyr::ddply(mds_df_grp, "unique_individuals", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_df_grp %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = unique_individuals), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = unique_individuals), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fills) +
  xlab("") + ylab("") + 
  guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_GroupMembership_IndivPolygons.tiff"), width = 6, height = 4, units = "in", dpi = 300)

```

Individual identity, two panels (convex hull polygons by group then individual). Start with aesthetics.
```{r}

mds_df_ind <- mds_df %>%
  # Filter by the group membership calls
  dplyr::filter(
    dataset == "Individual Identity"
  )

levels(mds_df_ind$group_ID)
levels(mds_df_ind$individual_ID)
levels(mds_df_ind$unique_individuals)

# Border colors by group (five)
cols <- scales::alpha(c("navy", "orange", "forestgreen", "firebrick", "grey5"), 0.65)

# Fill colors by individuals across groups. One color per group and individuals are coded in hues
fills <- c(
  paletteer_c("ggthemes::Blue", length(levels(mds_df_ind$individual_ID))),
  paletteer_c("ggthemes::Brown", length(levels(mds_df_ind$individual_ID))),
  paletteer_c("ggthemes::Green", length(levels(mds_df_ind$individual_ID))),
  paletteer_c("ggthemes::Red", length(levels(mds_df_ind$individual_ID))),
  paletteer_c("ggthemes::Gray", length(levels(mds_df_ind$individual_ID)))
)

# Shapes by individual within groups
shps <- rep(c(0, 1, 2, 4, 16, 17, 21, 23, 24, 6), length(levels(mds_df_ind$group_ID)))

```

Create the plots with polygons at the two social levels.
```{r}

# Panel C: convex hull polygons by groups
hulls <- plyr::ddply(mds_df_ind, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

mds_df_ind %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = unique_individuals), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_IndividualIdentity_GroupPolygons.tiff"), width = 6, height = 4, units = "in", dpi = 300)

# Panel D: Convex hull polygons per individual within groups

hulls <- plyr::ddply(mds_df_ind, "unique_individuals", function(x){
  x[chull(x$X, x$Y), ]
})

# glimpse(hulls)

mds_df_ind %>%
  ggplot(aes(x = X, y = Y)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = unique_individuals), alpha = 0.2, linewidth = 0.2, show.legend = FALSE) +
  geom_point(aes(color = group_ID, shape = unique_individuals), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fills) +
  xlab("") + ylab("") + 
  guides(color = "none", shape = "none", fill = "none") +
  # Specify the x and y-axis limits so that these are the same across plots
  # Also make sure that each label retains two decimal places even when there is a trailing zero
  scale_x_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  scale_y_continuous(limits = c(-0.15, 0.15), breaks = seq(-0.15, 0.15, 0.05), labels = sprintf("%.2f", round(seq(-0.15, 0.15, 0.05), 2))) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3)
  )

# Save this plot as an image file
ggsave(filename = file.path(figures_path, "AcousticSpace_IndividualIdentity_IndivPolygons.tiff"), width = 6, height = 4, units = "in", dpi = 300)

```
