---
title: "Generate calls, spectrograms, acoustic space"
output: html_document
date: "2024-11-20"
---

Purpose: In this script, we will develop a traditional pipeline to create spectrograms and build spectrographic cross-correlation acoustic space for synthetic calls. We will generate synthetic vocal signals with strong group membership information encoding. We will generate a synthetic dataset of 2 groups, 4 individuals per group, and 3 calls per individual (group information can outweigh individual information by a factor of at least 10 or higher). 

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "warbleR")

# Install the packages in X if not already installed, TKTK change to remove require statement
for (pkg in X) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg)
  }
}

# Install the paRsynth package from GitHub if you haven't installed it already
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/raneemsamman/Desktop" # Raneem's path
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where audio will be written out/read in
audio_dir <- "audio"

# Combine the base path, the analysis directory, and the audio directory into a single path
audio_path <- file.path(path, analysis_dir, audio_dir)

# Create the audio directory if it doesn't already exist on your computer
if(!dir.exists(audio_path)){ 
  dir.create(audio_path)
}

# Specify a folder inside the analysis directory where images will be written out/read in
images_dir <- "images"

# Combine the base path, the analysis directory, and the data directory into a single path
images_path <- file.path(path, analysis_dir, images_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(images_path)){ 
  dir.create(images_path)
}

```

Check out documentation for the paRsynth functions. These functions are written below in the order in which they should be used.
```{r eval = FALSE}

?paRsynth::generate_strings
?paRsynth::parsons_code
?paRsynth::frequency_anchors
?paRsynth::write_audio

```

# Step 1: Create character strings representing vocal signals with more group membership information than individual information
```{r}

# Set the seed for reproducibility
set.seed(123)

# Initialize the values of group_information and individual_information, which correspond to the length of the string that will be allocated to encoding group membership or individual identity information
# Group information can outweigh individual information by a factor of at least 10 or higher
factor_ratio <- 10
individual_information <- 2
group_information <- individual_information * factor_ratio

# Initialize the values of the number of groups, individuals, calls, and string length
n_groups <- 2
n_individuals <- 4
n_calls <- 3
string_length <- 28

### Generate the string for each call
calls <- paRsynth::generate_strings(
  n_groups = n_groups, 
  n_individuals = n_individuals, 
  n_calls = n_calls, 
  string_length = string_length, 
  group_information = group_information, 
  individual_information = individual_information
)

glimpse(calls)

```

# Step 2: Convert the strings to Parsons code
```{r}

calls_parsons <- paRsynth::parsons_code(
  df = calls, 
  string_col = "Call", 
  mapping = list("A" = "up", "B" = "down", "C" = "constant")
)

glimpse(calls_parsons)

```

# Step 3: Convert the Parsons code to frequency values
```{r}

calls_parsons_frequencies <- frequency_anchors(
  df = calls_parsons, 
  parsons_col = "Parsons_Code", 
  group_id_col = "Group", 
  individual_id_col = "Individual", 
  call_id_col = "Call_ID", 
  call_string_col = "Call", 
  starting_frequency = 4000, 
  frequency_shift = 1000
)

glimpse(calls_parsons_frequencies)

```

# Step 4: For each call or string, use these frequency vectors to generate synthetic audio files with the soundgen package
```{r}

synthetic_call_metadata <- write_audio(
  df = calls_parsons_frequencies, 
  save_path = audio_path, 
  sampling_rate = 150000, 
  sylLen = 400, 
  prefix = "GroupMembership"
)

glimpse(synthetic_call_metadata)

```

# Step 5: Save the metadata for the synthetic audio files to a CSV file
```{r}

# Add extra metadata for upcoming image files names and rearrange columns
synthetic_call_metadata %>%
  # dplyr::mutate(
  #   image_file_name = gsub(".wav", ".jpeg", audio_file_name)
  # ) %>% 
  # dplyr::select(audio_file_name, image_file_name, Group, Individual, Call_ID, Call, Parsons_Code, names(.)[grepl("Frequency", names(.))]) %>% 
  write.csv(., file = file.path(analysis_path, "synthetic_call_metadata.csv"), row.names = FALSE) 

```

# Step 6: Create a warbleR selection table
```{r}

# Create a vector of all of the audio files in the analysis path
wavs <- list.files(path = audio_path, pattern = ".wav$", full.names = FALSE)
length(wavs)
head(wavs)

# w <- 1 # testing

sel_tbl <- data.table::rbindlist(lapply(1:length(wavs), function(w){
  
  tmp <- tuneR::readWave(file.path(audio_path, wavs[w]))
  
  # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
  metadats_tmp <- synthetic_call_metadata %>%
    dplyr::filter(grepl(wavs[w], audio_file_name))
  
  # glimpse(metadats_tmp)
  
  # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
  if(nrow(metadats_tmp) > 0){
    
    # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
    # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1,
      start = 0.1, 
      end = seewave::duration(tmp) - 0.1,
      group_ID = metadats_tmp[["Group"]],
      individual_ID = metadats_tmp[["Individual"]],
      call_ID = metadats_tmp[["Call"]]
    )
    
  } else {
    
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1, 
      start = 0.1, 
      end = seewave::duration(tmp) + 0.1,
      group_ID = NA,
      individual_ID = NA,
      call_ID = NA
    )
    
  }
  
  return(res)
  
}))

# See the selection table in warbleR format with all useful metadata for the synthetic experiment
glimpse(sel_tbl)

```

# Step 7: Create spectrogram image files of each audio file
```{r}

warbleR::spectrograms(sel_tbl, wl = 512, flim = c(0, 12), wn = "hanning", pal = reverse.gray.colors.2,ovlp = 90, inner.mar = c(5, 4, 4, 2), outer.mar = c(0, 0, 0, 0), picsize = 1, res = 100, cexlab = 1, propwidth = FALSE, xl = 1, osci = FALSE, gr = FALSE, sc = FALSE, line = FALSE, mar = 0.05, it = "jpeg", parallel = 1, path = audio_path, pb = TRUE, fast.spec = FALSE, by.song = NULL, sel.labels = NULL, title.labels = NULL, dest.path = images_path, box = TRUE, axis = TRUE)

# Rename the image files
imgs <- list.files(images_path)
imgs

new_nms <- gsub(".wav-1", "", imgs)
new_nms

file.rename(file.path(images_path, imgs), file.path(images_path, new_nms))

```

# Step 8. Perform spectrogrphic cross-correlation (SPCC) to measure acoustic simialrity of all calls in dataset (pairwise similarity matrix)

```{r}

glimpse(sel_tbl)

xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 10), wn = "hanning", cor.method = "pearson", parallel = 1, na.rm = FALSE, type = "spectrogram", path = audio_path)

str(xc_mat)
dim(xc_mat)

# xc_mat[1:5, 16:24]

# Need to troubleshoot this more...can't get negative values
xc_mat[xc_mat < 0]

# Get the percentage of values that are negative
neg_values <- length(xc_mat[xc_mat<0])/(dim(xc_mat)[1]*dim(xc_mat)[2])

# Stop the function if the percentage of negative values is > 0%
if(neg_values > 0){
  stop("Negative values are present in the spectrographic cross-correlation matrix")
}

# Update the dimension names of the matrix
dimnames(xc_mat) <- list(sel_tbl$sound.files, sel_tbl$sound.files)

```

TKTK consider creating heatmaps to visually represent the similarities and differences across categories at different levels. Add to the mehtods paper AND the paRsynth vignettes! Here the question would be: are we creating the expected patterns of acoustic variation. Complementary to acoustic space plots

Acoustic space plots.
```{r}

# View(xc_mat)

# Convert to a distance matrix and dist object for isoMDS
dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
# str(dist_mat)

iso <- invisible(MASS::isoMDS(dist_mat, k = 2, maxit = 1000, trace = FALSE))
str(iso)

mds_df <- data.frame(
  sound.files = dimnames(xc_mat)[[1]],
  X = as.vector(iso$points[, 1]), 
  Y = as.vector(iso$points[, 2])
  ) %>% 
  inner_join(
    sel_tbl %>% 
      dplyr::select(sound.files, group_ID, individual_ID),
    by = c("sound.files")
  ) %>% 
  dplyr::mutate(
    group_ID = as.character(group_ID),
    individual_ID = as.character(individual_ID),
    group_ID = as.factor(group_ID),
    individual_ID = as.factor(individual_ID)
  )
  
glimpse(mds_df)

# Colors by group
cols <- scales::alpha(c("navy", "orange"), 0.65)

# Shapes by individual within groups
shps <- c(21, 23, 24, 6)

# Convex hull polygons per group
hulls <- plyr::ddply(mds_df, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

mds_df %>%
  # glimpse()
  ggplot(aes(x = X, y = Y, color = group_ID, shape = individual_ID)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID, color = group_ID), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = group_ID, color = group_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = "none", shape = "none", fill = "none") +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3)
  )

```

