---
title: "Generate calls, spectrograms, acoustic space"
output: html_document
date: "2024-11-20"
---

Purpose: In this script, we will develop a traditional pipeline to create spectrograms and build spectrographic cross-correlation acoustic space for synthetic calls. We will generate synthetic vocal signals with strong group membership information encoding. We will generate a synthetic dataset of 2 groups, 4 individuals per group, and 3 calls per individual (group information can outweigh individual information by a factor of at least 10 or higher).

Next steps: Update this code to generate group distinctive and individually distinctive call datasets, including audio files, spectrograms, and acoustic space plots. Add the parameters we use to generate calls as columns in the metadata.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "warbleR")

# Install the packages in X if not already installed, TKTK change to remove require statement
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Install the paRsynth package from GitHub if you haven't installed it already
# devtools::install_github("gsvidaurre/paRsynth")

# Add paRsynth to the list of packages to load
X <- c(X, "paRsynth")

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/raneemsamman/Desktop" # Raneem's path
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
path <- "~/Desktop" # Grace's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where audio will be written out/read in
audio_dir <- "audio"

# Combine the base path, the analysis directory, and the audio directory into a single path
audio_path <- file.path(path, analysis_dir, audio_dir)

# Create the audio directory if it doesn't already exist on your computer
if(!dir.exists(audio_path)){ 
  dir.create(audio_path)
}

# Specify a folder inside the analysis directory where images will be written out/read in
images_dir <- "images"

# Combine the base path, the analysis directory, and the data directory into a single path
images_path <- file.path(path, analysis_dir, images_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(images_path)){ 
  dir.create(images_path)
}

```

Check out documentation for the paRsynth functions. These functions are written below in the order in which they should be used.
```{r eval = FALSE}

?paRsynth::generate_strings
?paRsynth::parsons_code
?paRsynth::frequency_anchors
?paRsynth::write_audio

```

# Step 1: Create character strings representing vocal signals with more group membership information than individual information
```{r}

# Set the seed for reproducibility
set.seed(44)

# Initialize the values of group_information and individual_information, which correspond to the length of the string that will be allocated to encoding group membership or individual identity information
# Group information can outweigh individual information by a factor of at least 3 or higher
factor_ratio <- 3
individual_information <- 2
group_information <- individual_information * factor_ratio

# Initialize the values of the number of groups, individuals, calls, and string length
n_groups <- 2
n_individuals <- 2
n_calls <- 2
string_length <- (group_information + individual_information) + 4

### Generate the string for each call
calls <- paRsynth::generate_strings(
  n_groups = n_groups, 
  n_individuals = n_individuals, 
  n_calls = n_calls, 
  string_length = string_length, 
  group_information = group_information, 
  individual_information = individual_information
)

glimpse(calls)

```

# Step 2: Convert the strings to Parsons code
```{r}

calls_parsons <- paRsynth::parsons_code(
  df = calls, 
  string_col = "Call", 
  mapping = list("A" = "up", "B" = "down", "C" = "constant")
)

glimpse(calls_parsons)

```

# Step 3: Convert the Parsons code to frequency values
```{r}

calls_parsons_frequencies <- frequency_anchors(
  df = calls_parsons, 
  parsons_col = "Parsons_Code", 
  group_id_col = "Group", 
  individual_id_col = "Individual", 
  call_id_col = "Call_ID", 
  call_string_col = "Call", 
  starting_frequency = 4000, 
  frequency_shift = 1000
)

glimpse(calls_parsons_frequencies)

```

# Step 4: For each call or string, use these frequency vectors to generate synthetic audio files with the soundgen package

TKTK see notes below, need to work on adding the soundgen arguments and parameters below.
```{r}

synthetic_call_metadata <- write_audio(
  df = calls_parsons_frequencies, 
  save_path = audio_path, 
  sampling_rate = 200000, 
  sylLen = 400, 
  prefix = "GroupMembership"
)

glimpse(synthetic_call_metadata)


# Testing soundgen arguments
pitches <- synthetic_call_metadata %>% 
    dplyr::select(names(synthetic_call_metadata)[grepl("Frequency", names(synthetic_call_metadata))]) %>% 
    slice(8) %>% 
    t(.) %>% 
    as.vector(.)

length(pitches)


# TKTK see below, this matrix is used to control amplitide across the harmonics
# rolloffExact = matrix(c(1, 0.2, 1, 0.02, .02,  # strength of H1-H5 at time 0
                        # 1, 0.2, 0.01, 0.1, 0.4), # strength of H1-H5 at time 1000
                      # ncol = 2)

# Use a vector to indicate that the source spectrum (glottal source) that produces harmonics does not change over time, or that the strength or amplitude of each harmonic does not change over time
# rolloffExact <- c(0.1, 0.5, 0.25, 1, 0.25, 0.08, 0.05, 0.02)

# Is it possible to control the number of harmonics with these objects? YES
rolloffExact <- c(0.1, 0.1)
# rolloffExact <- c(0.1)

# 32 frequency anchors and 4000ms (4s) produce calls that have thinner and clearer frequency contours
# 32 anchors and 1000ms produces calls that have thicker and blurrier contours
# TKTK focus on a good number of characters for 200ms and 400ms
# 18 and 22 characters is a bit blurry at 400 ms, 12 is a bit better
# 12 characters is also a bit blurry at 200 ms, 10 is a little better
# 30 anchors and 200 ms is very blurry and the contours are thicker
soundgen(
  sylLen = 200, # TKTK add specific guidelines for duration based on character string or freqency anchor length, see below
  # rolloff = -20, # do we want to keep this?
  # pitch = pitches[1:5], # fundamental frequency contour is much less thick with fewer anchors and duration of 400 ms
  pitch = pitches, # fundamental frequency contour is much less thick with the full number of anchors but longer duration (4000 ms)
  formants = NULL, 
  vocalTract = 5,
  # formantLocking = c(0, 1, 1, 1, 1, 0),  # except the beginning and end
  # shortestEpoch = 200,  # affects both subharmonics (if any) and formantLocking
  # noise = -20, # just to make formants visible in this example
  samplingRate = 44100, 
  pitchSamplingRate = 44100,
  pitchCeiling = 7000,
  # TKTK This works for smoothing!! And Loess smoothing works better than approx
  smoothing = list(interpol = "loess", loessSpan = 1, discontThres = 0, jumpThres = 0),
  # TKTK what works for controlling harmonics?
  # nonlinBalance = 1, # 0 and 2 make only slight differences here
  subRatio = 1, # TKTK this does make a difference and add subharmonics but it's only noticeable when this argument is set to 2, when enegry is more evenly allocated across the harmonics, and when the rolloff argument above is set to -20
  vibratoFreq = 1, # set vibrato to the lowest value
  # TKTK this argument works for allocating energy across the harmonics
  rolloffExact = rolloffExact,
  plot = TRUE, 
  windowLength = 30,
  step = 30*0.9,
  ylim = c(0, 20),
  contrast = 0.1
)

```


TKTK changes to write_audio: set formants to NA, nonlinBalance to 0 (default is 100), also allow changes to subratio or the number of subharmonics, also supDep (amplitude or salience across harmonics?), vibratoFreq should be none, also smoothing should be available!!

http://cogsci.se/soundgen/sound_generation.html#specifying-the-strength-of-each-harmonic: need to specify the salience of each harmonic when these are chosen

Do we need to pass timestamps to the function and also have default smoothing values??

We also need to change the thickness of each frequency contour but especially f0


TKTK in vignettes add code to check the sampling rate before running cross-correlation (otherwise will get negative values).


# Step 5: Save the metadata for the synthetic audio files to a CSV file
```{r}

# Add extra metadata for upcoming image files names and rearrange columns
synthetic_call_metadata %>%
  write.csv(., file = file.path(analysis_path, "synthetic_call_metadata.csv"), row.names = FALSE) 

```

# Step 6: Create a warbleR selection table
```{r}

# Create a vector of all of the audio files in the analysis path
wavs <- list.files(path = audio_path, pattern = ".wav$", full.names = FALSE)
length(wavs)
head(wavs)

# w <- 1 # testing

sel_tbl <- data.table::rbindlist(lapply(1:length(wavs), function(w){
  
  tmp <- tuneR::readWave(file.path(audio_path, wavs[w]))
  
  # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
  metadats_tmp <- synthetic_call_metadata %>%
    dplyr::filter(grepl(wavs[w], audio_file_name))
  
  # glimpse(metadats_tmp)
  
  # Create a row for the selection table in warbleR format if the audio file exists and metadata for that file also exists
  if(nrow(metadats_tmp) > 0){
    
    # Use 0.1s as a margin to indicate where the vocalization starts and ends in the audio file
    # soundgen::soundgen() adds 100ms of silence before and after the synthetic vocalization by default 
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1,
      start = 0.1, 
      end = seewave::duration(tmp) - 0.1,
      sampling_rate = tmp@samp.rate,
      group_ID = metadats_tmp[["Group"]],
      individual_ID = metadats_tmp[["Individual"]],
      call_ID = metadats_tmp[["Call"]]
    )
    
  } else {
    
    res <- data.frame(
      sound.files = wavs[w], 
      selec = 1, 
      start = 0.1, 
      end = seewave::duration(tmp) + 0.1,
      sampling_rate = NA,
      group_ID = NA,
      individual_ID = NA,
      call_ID = NA
    )
    
  }
  
  return(res)
  
}))

# See the selection table in warbleR format with all useful metadata for the synthetic experiment
glimpse(sel_tbl)

unique(sel_tbl$sampling_rate)

```

# Step 7: Create spectrogram image files of each audio file
```{r}

warbleR::spectrograms(sel_tbl, wl = 512, flim = c(0, 12), wn = "hanning", pal = reverse.gray.colors.2,ovlp = 90, inner.mar = c(5, 4, 4, 2), outer.mar = c(0, 0, 0, 0), picsize = 1, res = 100, cexlab = 1, propwidth = FALSE, xl = 1, osci = FALSE, gr = FALSE, sc = FALSE, line = FALSE, mar = 0.05, it = "jpeg", parallel = 1, path = audio_path, pb = TRUE, fast.spec = FALSE, by.song = NULL, sel.labels = NULL, title.labels = NULL, dest.path = images_path, box = TRUE, axis = TRUE)

# Rename the image files
imgs <- list.files(images_path)
imgs

new_nms <- gsub(".wav-1", "", imgs)
new_nms

invisible(file.rename(file.path(images_path, imgs), file.path(images_path, new_nms)))

```

# Step 8. Perform spectrogrphic cross-correlation (SPCC) to measure acoustic simialrity of all calls in dataset (pairwise similarity matrix)

```{r}

glimpse(sel_tbl)

xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 20), wn = "hanning", cor.method = "pearson", parallel = 1, na.rm = FALSE, type = "spectrogram", path = audio_path)

str(xc_mat)
dim(xc_mat)

# xc_mat[1:5, 16:24]

xc_mat[xc_mat < 0]

# Get the percentage of values that are negative
neg_values <- length(xc_mat[xc_mat<0])/(dim(xc_mat)[1]*dim(xc_mat)[2])

# Stop the function if the percentage of negative values is > 0%
if(neg_values > 0){
  stop("Negative values are present in the spectrographic cross-correlation matrix")
}

xc_mat[xc_mat < 0]

# Update the dimension names of the matrix
dimnames(xc_mat) <- list(sel_tbl$sound.files, sel_tbl$sound.files)

```

TKTK consider creating heatmaps to visually represent the similarities and differences across categories at different levels. Add to the mehtods paper AND the paRsynth vignettes! Here the question would be: are we creating the expected patterns of acoustic variation. Complementary to acoustic space plots

Acoustic space plots.
```{r}

# View(xc_mat)

# Convert to a distance matrix and dist object for isoMDS
dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
# str(dist_mat)

iso <- invisible(MASS::isoMDS(dist_mat, k = 2, maxit = 1000, trace = FALSE))
str(iso)

mds_df <- data.frame(
  sound.files = dimnames(xc_mat)[[1]],
  X = as.vector(iso$points[, 1]), 
  Y = as.vector(iso$points[, 2])
) %>% 
  inner_join(
    sel_tbl %>% 
      dplyr::select(sound.files, group_ID, individual_ID),
    by = c("sound.files")
  ) %>% 
  dplyr::mutate(
    group_ID = paste("group", group_ID, sep = "_"),
    individual_ID = paste("individual", individual_ID, sep = "_"),
    unique_individuals = paste(group_ID, individual_ID, sep = " - "),
    group_ID = factor(group_ID),
    individual_ID = factor(individual_ID),
    unique_individuals = factor(unique_individuals)
  )

glimpse(mds_df)
# View(mds_df)

levels(mds_df$group_ID)
levels(mds_df$individual_ID)
levels(mds_df$unique_individuals)

# Colors by group
cols <- scales::alpha(c("navy", "orange", "forestgreen", "firebrick", "grey"), 0.65)

# Shapes by individual within groups
shps <- rep(c(21, 23, 24, 6), length(levels(mds_df$group_ID)))

# Convex hull polygons per group or unique individual
# hulls <- plyr::ddply(mds_df, "unique_individuals", function(x){
#   x[chull(x$X, x$Y), ]
# })

hulls <- plyr::ddply(mds_df, "group_ID", function(x){
  x[chull(x$X, x$Y), ]
})

glimpse(hulls)

mds_df %>%
  ggplot(aes(x = X, y = Y, color = group_ID)) + 
  geom_polygon(data = hulls, aes(x = X, y = Y, fill = group_ID, color = group_ID), alpha = 0.2, size = 0.2, show.legend = FALSE) +
  geom_point(aes(fill = group_ID, color = group_ID, shape = individual_ID), size = 2, stroke = 0.5) +
  scale_shape_manual(values = shps) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  xlab("") + ylab("") + 
  guides(color = "none", shape = "none", fill = "none") +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 9),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.25),
    plot.margin = margin(0, 3, -3, -3)
  )

```

