---
title: "Information Encoding Experiments"
author: "Grace Smith-Vidaurre, Ari Cross"
output: html_document
date: "2024-07-08"
---

Purpose: The following code was designed to test the behavior of functions written to generate synthetic vocalizations that emphasize either individual identity or group membership information. These functions written by Ari generate individually distinctive or group-specific character strings that are converted to Parson's code and then audio files of frequency-modulated vocalizations using the `soundgen` package. The loops below iterate over varying ratios of how much of the initial character string is allocated to shared group membership versus unique individual identity. The output of each loop is the normalized mutual information (NMI) calculated between the original classes at both the individual and group levels compared to cluster labels obtained from k-means clustering on multidimensional scaling variables generated from a spectrographic cross-correlation (SPCC) matrix. 

The NMI calculations will allow us to address how much information about group membership versus individual identity is contained in patterns of acoustic variation across call datasets generated to emphasize either individual identity or group membership. For instance, when creating datasets of vocalizations that are more individually distinctive and less group-specific, the NMI for the individual-level should be high but low for the group-level, because patterns of acoustic variation should contain a lot of information about individual identity but less about individuals' group membership. Given that all calls contain individual identity and group membership information, we should also see some interesting patterns at intermediate ratios of the string allocated to individual identity versus group membership.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries and create a temporary working path.
```{r}

# Clean the global environment
rm(list = ls())

X <- c("dplyr", "stringdist", "tidyverse", "ggplot2", "apcluster", "soundgen", "parallel", "stringr", "data.table", "tuneR", "pbapply", "aricode", "Rmisc")

invisible(lapply(X, library, character.only = TRUE))

# This initial base path will need to be changed for other users
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's Mac mini base path
# path <- "/home/gsvidaurre/Desktop" # Grace's laptop base path
data_dir <- "synthetic_audio_tests"
tmp_path <- file.path(path, data_dir)
figure_path <- file.path(path, "GitHub_repos/iCER_ACRES_MSU_REU2024/figures")

if(!dir.exists(tmp_path)){ 
  dir.create(tmp_path)
}

# Set cores for parallel processing
cores <- parallel::detectCores() - 2

```

Load Ari's functions.
```{r}

# The string "GitHub_repos" may need need to be changed for other users
code_path <- file.path(path, "GitHub_repos", "iCER_ACRES_MSU_REU2024")

source(file.path(code_path, "functions.R"))

```

# Generate synthetic call datasets and run SPCC

Generate the individually distinctive or group distinctive character strings and audio files over varying proportions of il_middle to gl_middle. These ratios should be 0.01, 0.02, 0.04, 0.5, 5, 10, 25, and 50, and will correspond to gl_middle:il_middle values of 1:100, 2:100, 4:100, 50:100, 100:20, 100:10, 100:4, 100:2.

Iterate over each treatment a number of times so that we can calculate a 95% confidence interval around each NMI line below. Update the loop so that a selection table is made and SPCC is performed each time a new call dataset is generated. Then save the selection table and SPCC matrix but remove audio files before initiating the subsequent iteration. Audio files can be regenerated in another script in order to generate spectrogram image files. The duration of the audio files impacts the computational time (files over 400 ms take a long time to generate).
```{r}

# Set a seed for reproducibility
set.seed(888)

# Initialize the values of gl_middle and il_middle, which correspond to the length of the string that will be allocated to encoding group membership or individual identity information
gl_middles <- c(1, 2, 4, 50, rep(100, 4))
il_middles <- c(rep(100, 4), 20, 10, 4, 2)

# Iterate over each unique pair of gl_middle and il_middle values to create call datasets with varying amounts of group versus individual information (e.g. more convergence within groups versus more divergence within groups). Keep the number of groups, individuals, call per individual, and string length the same across iterations

n_groups <- 2
n_individuals <- 5 # Dropping sample sizes to 5 individuals and 5 calls per individual
n_calls <- 5
string_length <- 150
iteratns <- 3

# Testing the first iteration of each loop
# i <- 1
# n <- 1
# x <- 1

system.time(
  
  invisible(pblapply(1:length(gl_middles), function(i){
    
    cat(paste("gl_middles = ", gl_middles[i], "\n", sep = ""))
    
    nmi_res_tmp <- data.table::rbindlist(lapply(1:iteratns, function(n){
      
      ### Step 1: Generate the string for each call
      calls <- suppressMessages(gen_calls(n_groups = n_groups, n_individuals = n_individuals, n_calls = n_calls, string_length = string_length, gl_middle = gl_middles[i], il_middle = il_middles[i]))

      ### Step 2: Convert the strings to Parsons code
      calls_parsons <- add_parsons_code(calls, "Call", parsons_code_mapping)
      
      ### Step 3: Convert the Parsons code to frequency values
      
      calls_parsons_frequencies <- generate_frequency(calls_parsons, parsons_col = "Parsons_Code", group_id_col = "Group", individual_id_col = "Individual", call_id_col = "Call.No")
      
      ### Step 4: For each call or string, use these frequency vectors to generate synthetic audio files with Ari's functions and the soundgen package
      
      synthetic_call_metadata <- write_wave(calls_parsons_frequencies, save_path = tmp_path, sampling_rate = 150000, sylLen = 400, prefix = paste("Ratio", gl_middles[i]/il_middles[i], sep = "_"))
      
      ### Step 5: Generate a selection table for the warbleR package
      wavs <- list.files(path = tmp_path, pattern = paste("Ratio", gl_middles[i]/il_middles[i], sep = "_"))
      
      cat(paste("Number of audio files = ", length(wavs), "\n"))

      sel_tbl <- data.table::rbindlist(lapply(1:length(wavs), function(w){
        
        tmp <- tuneR::readWave(file.path(tmp_path, wavs[w]))

        # Return the metadata for the given call using the synthetic metadata generated during audio file generation above
        metadats_tmp <- synthetic_call_metadata %>%
          dplyr::filter(grepl(wavs[w], audio_file_name))
        
        if(nrow(metadats_tmp) > 0){
          
          res <- data.frame(
            sound.files = wavs[w], 
            selec = 1, 
            start = 0.1, 
            end = seewave::duration(tmp) + 0.1,
            group_ID = metadats_tmp[["Group"]],
            individual_ID = metadats_tmp[["Individual"]],
            call_ID = metadats_tmp[["Call"]],
            sampling_rate = tmp@samp.rate,
            gl_middle = gl_middles[i],
            il_middle = il_middles[i],
            proportion = gl_middles[i]/il_middles[i]
          )
          
        } else {
          
          res <- data.frame(
            sound.files = wavs[w], 
            selec = 1, 
            start = 0.1, 
            end = seewave::duration(tmp) + 0.1,
            group_ID = NA,
            individual_ID = NA,
            call_ID = NA,
            sampling_rate = tmp@samp.rate,
            gl_middle = gl_middles[i],
            il_middle = il_middles[i],
            proportion = gl_middles[i]/il_middles[i]
          )
          
        }
        
        return(res)
        
      }))
      
      ### Step 6: Perform SPCC using a default window length and a general bandpass filter
      xc_mat <- warbleR::cross_correlation(sel_tbl, wl = 512, ovlp = 90, bp = c(0, 10), wn = "hanning", cor.method = "pearson", parallel = cores, na.rm = FALSE, type = "spectrogram", path = tmp_path)
      
      # Get the percentage of values that are negative
      neg_values <- length(xc_mat[xc_mat<0])/(dim(xc_mat)[1]*dim(xc_mat)[2])
      
      # Stop the function if the percentage of negative values is > 0%
      if(neg_values > 0){
        stop("Negative values are present in the spectrographic cross-correlation matrix")
      }
      
      # Update the dimension names of the matrix
      dimnames(xc_mat) <- list(wavs, wavs)
      
      cat(paste("Dimensions of SPCC matrix = ", dim(xc_mat)[1], dim(xc_mat)[2], "\n"))
      
      cat(paste("NA's in SPCC matrix?", any(is.na(xc_mat)), "\n"))
      
      ### Step 7: Perform MDS
      
      # Convert the SPCC similarity matrix to a distance matrix and dist object for isoMDS
      dist_mat <- stats::as.dist(1 - xc_mat, diag = TRUE, upper = TRUE)
      
      # Reduce dimensionality of the SPCC matrix using multidimensional scaling (MDS)
      iso_res <- invisible(MASS::isoMDS(dist_mat, k = 2, maxit = 1000, trace = FALSE))
      
      # Make a data frame of the first two MDS dimensions and call metadata
      mds_df <- data.frame(sound.files = dimnames(iso_res$points)[[1]]) %>%
        dplyr::mutate(
          X = iso_res$points[, 1],
          Y = iso_res$points[, 2]
        ) %>%
        inner_join(
          sel_tbl %>%
            dplyr::select(sound.files, group_ID, individual_ID, call_ID),
          by = c("sound.files")
        )
      
      cat(paste("Dimensions of MDS results = ", dim(mds_df)[1], dim(mds_df)[2], "\n"))
      
      cat(paste("NA's in MDS X dimension?", any(is.na(mds_df$X)), "\n"))
      
      cat(paste("NA's in MDS Y dimension?", any(is.na(mds_df$Y)), "\n"))
      
      ### Step 8: Remove .wav files to free up storage space
      rem_files <- file.path(tmp_path, wavs)
      invisible(file.remove(rem_files))
      
      ### Step 9: Perform clustering and Normalized Mutual Information (NMI) calculation
      # In order to compute NMI at two social levels (individual and group), we need to run clustering at these two levels
      
      ### Group-level clustering and NMI calculation
      
      # Set the number of clusters to the number of unique groups
      num_clusters <- length(unique(mds_df$group_ID))
      
      # Perform k-means clustering with this number of clusters
      # Ensure that the kmeans algorithm uses only the MDS variables, so that it uses information from the patterns of acoustic variation only in order to detect clusters
      kmeans_grp <- kmeans(mds_df[, grep("X|Y", names(mds_df))], centers = num_clusters)
      
      cat(paste("NA's in group clustering?", any(is.na(kmeans_grp$cluster)), "\n"))
      
      # Compute NMI at the group-level
      orig_classes <- mds_df$group_ID
      nmi_grp <- NMI(orig_classes, kmeans_grp$cluster)
      
      ### Individual-level clustering and NMI calculation
      
      # Set the number of clusters to the number of unique individuals across groups
      num_clusters <- mds_df %>% 
        distinct(group_ID, individual_ID) %>% 
        nrow()
      
      # Perform k-means clustering with this number of clusters
      # Ensure that the kmeans algorithm uses only the MDS variables, so that it uses information from the patterns of acoustic variation only in order to detect clusters
      kmeans_ind <- kmeans(mds_df[, grep("X|Y", names(mds_df))], centers = num_clusters)
      
      cat(paste("NA's in individual clustering?", any(is.na(kmeans_ind$cluster)), "\n"))
      
      # Compute NMI at the individual-level, which means that the original classes are the group plus individual identity
      orig_classes <- paste(mds_df$group_ID, mds_df$individual_ID, sep = "-")
      nmi_ind <- NMI(orig_classes, kmeans_ind$cluster)
      
      ### Step 10: return NMI results
      return(
        data.frame(
          exptl_ratio = gl_middles[i]/il_middles[i],
          iteration = n,
          NMI_group = nmi_grp,
          NMI_individual = nmi_ind
        )
      )
      
    }))
    
    ### Step 11. Write out the NMI results for the given treatment across iterations
    nmi_res_tmp %>% 
      write.csv(file.path(tmp_path, paste("nmi_results_", gl_middles[i]/il_middles[i], ".csv", sep = "")), row.names = FALSE)
    
  }))

)

# On the Mac Mini this process took about 23 minutes
# user   system  elapsed 
# 1579.362  563.165 1430.844 

```

How often do the NMI calculations go below 0 or above 1?
```{r}

nmi_files <- list.files(path = tmp_path, pattern = "nmi_")
nmi_files

nmi_res <- data.table::rbindlist(pblapply(1:length(nmi_files), function(n){
  
  return(read.csv(file.path(tmp_path, nmi_files[n])))
  
}))

glimpse(nmi_res)

# Two group-level calculations go below 1
nmi_res %>% 
  dplyr::filter(
    NMI_group < 0
  )

# No other values go below 0 or over 1
nmi_res %>% 
  dplyr::filter(
    NMI_group > 1
  )

nmi_res %>% 
  dplyr::filter(
    NMI_individual < 0
  )


nmi_res %>% 
  dplyr::filter(
    NMI_individual > 1
  )

```


# Plot NMI results

Generate plots of NMI values at the individual and group-level across the experimental call datasets. I added 95% CIs, but these don't make sense because they vary to go below 0 and above 1. I decided to use the interquartile range (the difference between the upper and lower quartiles) instead.
```{r}

nmi_files <- list.files(path = tmp_path, pattern = "nmi_")
nmi_files

nmi_res <- data.table::rbindlist(pblapply(1:length(nmi_files), function(n){
  
  return(read.csv(file.path(tmp_path, nmi_files[n])))
  
}))

glimpse(nmi_res)

# Calculate summary statistics (mean and interquartile range) across iterations
nmi_sum <- nmi_res %>%
  # Pivot longer to add a column by social level
  pivot_longer(
    cols = c("NMI_group", "NMI_individual"),
    names_to = "type",
    values_to = "NMI"
  ) %>%
  dplyr::mutate(
    social_level = type,
    social_level = gsub("NMI_", "", social_level)
  ) %>%
  dplyr::select(-c("type")) %>%
  dplyr::mutate(
    social_level = gsub("g", "G", social_level),
    social_level = gsub("ind", "Ind", social_level)
  ) %>% 
  # Group NMI results by ratio and social_level in order to calculate means and quartiles
  group_by(exptl_ratio, social_level) %>%
  dplyr::reframe(
    mean_nmi = round(mean(NMI), 3),
    Q1 = quantile(NMI, 0.25), # first quartile
    Q3 = quantile(NMI, 0.75) # third quartile
    # ci_lower = round(Rmisc::CI(NMI, ci = 0.95)[["lower"]], 3),
    # ci_upper = round(Rmisc::CI(NMI, ci = 0.95)[["upper"]], 3)
  )

glimpse(nmi_sum)

```

Create plots that represent call datasets at each social level (e.g. more group membership or individual identity information). Use a log-scale axis to spread out the x-axis more evenly.

Plotting aesthetics shared across plots.
```{r}

# Encode the NMI calculations at the two social levels with different linetypes
ltys <- c("dashed", "dotted")

```

More group membership information.
```{r}

# # Create custom underlined text labels for the original ratios for the group-specific call dataset
# parseLabel <- sprintf("underline(%s)",
#                       gsub(" ", "~", nmi_sum %>%
#                              dplyr::filter(
#                                exptl_ratio > 1
#                              ) %>%
#                              dplyr::filter(
#                                social_level == "Group"
#                              ) %>%
#                              dplyr::mutate(
#                                label = paste("Ratio: ", exptl_ratio, sep = "")
#                              ) %>%
#                              pull(label), fixed = TRUE))
# 
# length(parseLabel)

# Plot the data
nmi_sum %>%
  dplyr::filter(
    exptl_ratio > 1
  ) %>%
  ggplot(aes(x = log(exptl_ratio), y = mean_nmi)) +
  geom_line(aes(group = social_level, linetype = social_level), color = "black", linewidth = 1) +
  geom_errorbar(aes(ymin = Q1, ymax = Q3), linetype = "solid", color = "black", width = 0) +
  geom_point(color = "black", size = 3) +
  # geom_text(
  #   data =
  #     nmi_sum %>%
  #     dplyr::filter(
  #       exptl_ratio > 1
  #     ) %>%
  #     dplyr::filter(
  #       social_level == "Group"
  #     ) %>% 
  #     dplyr::mutate(
  #       label = parseLabel
  #     ),
  #   aes(x = log(exptl_ratio), y = 1.07, label = parseLabel), hjust = 0.5, parse = TRUE, size = 3.5) +
  scale_linetype_manual(values = ltys) +
  xlab("Log ratio of group to individual information") +
  ylab("Normalized Mutual Information") +
  guides(linetype = guide_legend(title = "Social level", override.aes = list(linewidth = 1))) +
  ylim(c(0, 1)) +
  theme_bw() +
  theme(
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    legend.title = element_text(size = 24),
    legend.text = element_text(size = 22)
  )

ggsave(file.path(figure_path, "NMI_Results_Group-SpecificDataset.png"), units = "in", width = 8.2, height = 6, dpi = 300)

```

More individual identity information.
```{r}

# # Create custom underlined text labels for the original ratios for the group-specific call dataset
# parseLabel <- sprintf("underline(%s)",
#                       gsub(" ", "~", nmi_sum %>%
#                              dplyr::filter(
#                                exptl_ratio < 1
#                              ) %>%
#                              dplyr::filter(
#                                social_level == "Individual"
#                              ) %>% 
#                              dplyr::mutate(
#                                label = paste("Ratio: ", exptl_ratio, sep = "")
#                              ) %>% 
#                              pull(label), fixed = TRUE))
# 
# length(parseLabel)

# Plot the data
nmi_sum %>%
  dplyr::filter(
    exptl_ratio < 1
  ) %>%
  ggplot(aes(x = log(exptl_ratio), y = mean_nmi)) +
  geom_line(aes(group = social_level, linetype = social_level), linewidth = 1) +
  geom_errorbar(aes(ymin = Q1, ymax = Q3), linetype = "solid", color = "black", width = 0) +
  geom_point(color = "black", size = 3) +
  # geom_text(
  #   data =
  #     nmi_sum %>%
  #     dplyr::filter(
  #       exptl_ratio < 1
  #     ) %>%
  #     dplyr::filter(
  #       social_level == "Individual"
  #     ) %>% 
  #     dplyr::mutate(
  #       label = parseLabel
  #     ),
  #   aes(x = log(exptl_ratio), y = 1.05, label = parseLabel), hjust = 0.45, parse = TRUE, size = 3) +
  scale_linetype_manual(values = ltys) +
  xlab("Log ratio of group to individual information") +
  ylab("Normalized Mutual Information") +
  guides(linetype = guide_legend(title = "Social level", override.aes = list(linewidth = 1))) +
  ylim(c(0, 1)) +
  theme_bw() +
  theme(
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title = element_text(size = 24),
    axis.text = element_text(size = 20),
    legend.title = element_text(size = 24),
    legend.text = element_text(size = 22)
  )

ggsave(file.path(figure_path, "NMI_Results_IndividuallyDistinctiveDataset.png"), units = "in", width = 8.2, height = 6, dpi = 300)

```
