---
title: "ConceptualFigure_FrequencyAnchors"
author: Grace Smith-Vidaurre, Brittany Coppinger
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Purpose: This script uses the synthetic call metadata to create slowed down audio files as well as a conceptual graphic of frequency anchors for the paRsynth pipeline. Slowed down audio files and the conceptual figure will be used for presentations. The conceptual figure may be used for the manuscript.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, messsage = FALSE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "tidyverse", "data.table", "gganimate")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

```

```{r load packages, eval = FALSE}

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE, verbose = FALSE))

```

```{r load packages in background, include = FALSE}

# The only solution right now to avoid having a whole bunch of verbose output printed from the chunk above
# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE, verbose = FALSE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "C:/Users/britt/Desktop" # Britt's path

# Initialize a path for the local GitHub repo for this manuscript, for saving final figures here
# git_path <- "C:/Users/britt/Documents/GitHub" # Britt's path
git_path <- "/Users/gracesmith-vidaurre/Desktop/GitHub_repos"

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where audio will be written out/read in
audio_dir <- "audio"

# Combine the base path, the analysis directory, and the audio directory into a single path
audio_path <- file.path(path, analysis_dir, audio_dir)

# Create the audio directory if it doesn't already exist on your computer
if(!dir.exists(audio_path)){ 
  dir.create(audio_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

```

Read in the synthetic call metadata.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))
glimpse(synthetic_call_metadata)

```

# Synthetic calls at quarter speed

Produce calls that are slowed down so that frequency modulation patterns are easier to hear by the human ear. Choose the same calls use for the group membership dataset generated for a main figure (see script `Figures_Spectrograms.Rmd`).
```{r}

wav_nms <- c(
  "GroupMembership_Group2_Indiv4_Call1",
  "GroupMembership_Group2_Indiv4_Call2",
  "GroupMembership_Group2_Indiv6_Call1",
  "GroupMembership_Group2_Indiv6_Call2",
  "GroupMembership_Group3_Indiv1_Call3",
  "GroupMembership_Group3_Indiv1_Call4",
  "GroupMembership_Group3_Indiv4_Call1",
  "GroupMembership_Group3_Indiv4_Call4"
)

```

```{r}

speed <- 0.25 # quarter time, 1/4 full speed

# Add the file extension to the audio file names
wav_nms_ext <- paste(wav_nms, ".wav", sep = "")
wav_nms_ext

# First find these .wav files and write them out with shorter names to the figures path, since these will be used as media. Then upload these files to Google Drive
# w <- 1
invisible(pblapply(1:length(wav_nms), function(w){
  
  tmp_wav <- readWave(file.path(audio_path, wav_nms_ext[w]))
  
  tmp_wav@samp.rate <- tmp_wav@samp.rate * speed
  
  writeWave(tmp_wav, file.path(figure_path, paste(paste(wav_nms[w], "quarterSpeed", sep = "_"), ".wav", sep = "")))
  
}))

```

## Conceptual figure of frequency anchors

Choose a single call for talk slides: get the character string and also the vector of frequency anchors.
```{r}

# Choose the first call in this dataset (Group 1, Individual 1, Call 1)
filt_data <- synthetic_call_metadata %>% 
  slice(1)

glimpse(filt_data)

# Call string
filt_data$Call

# [1] "CABCAABACCBCCBAA"

# Frequency anchors are in columns, pull these out as a vector
freq_cols <- filt_data %>%
  # Select only the columns that start with the pattern "Frequency"
  select(names(.)[grep("^Frequency", names(.))])

glimpse(freq_cols)

# We need to transpose this data frame so that all of the frequency values are in rows not columns, and then we need to convert the resulting matrix to a vector
frequency_anchors <- as.vector(t(freq_cols))

# Looks good
frequency_anchors
length(frequency_anchors)

```

Make a conceptual graphic showing how the frequency values produced from the paRsynth pipeline pipeline serve as frequency modulation "anchors" for soundgen to generate synthetic audio files. This be a line graph of the frequency anchors above.
```{r}

# Create a data frame of the frequency anchors plus timestamps
freq_anchors <- data.frame(
  freq_anchors = frequency_anchors,
  # The timestamps should be evenly spaced across the duration of the call, which is the soundgen default
  # We generated calls in the first script that had 200 ms duration
  time = round(seq(0, 0.2, 0.2/(length(frequency_anchors) - 1)), 3)
)

# X-axis is time, y-axis is frequency
glimpse(freq_anchors)

# Make a graphic of the frequency anchors plus a line through them
Freq_anch_plot <-  ggplot(freq_anchors, aes(x = time, y = freq_anchors/1000)) +
  geom_line(color = scales::alpha("#A8CDECFF"), linetype = "dashed", linewidth = 2) +
  # Turn on the line below for the animation of the graph, turn off for the static version
  geom_point(aes(group = seq_along(time)), size = 8, color = scales::alpha("#F6955EFF")) +
  # Turn on the line below for the static graph image, turn off for animated version
  # geom_point(size = 5, color = scales::alpha("#F6955EFF")) +
  xlab("Time (s)") +
  ylab("Frequency (kHz)") +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    # axis.title = element_text(size = 16),
    axis.text = element_text(size = 16),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  ) +
  # The line below animates the plot, turn off for static image (make sure to remove the + from the line above too!)
  gganimate::transition_reveal(time)

# We will use this image file and it may need to be resized
# use the ggsave line to save the static plot, as the anim_save line to save the animated plot
# this sizing is for use in a powerpoint presentation
# ggsave(file.path(figure_path, "Concept_FreqAnch.png"), units = "in", width = 5, height = 4.6, dpi = 600)
# this take several minutes to process and save on Britt's laptop, just FYI!
gganimate::animate(Freq_anch_plot, units = "in", height = 3.5, width = 12.25, res = 300)
gganimate::anim_save(file.path(figure_path, "Concept_FreqAnch_GIF.gif"))
```