---
title: "Information Encoding Experiments - Effect Size Calculations"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

TKTK calculating effect size and plotting accuracy and density plots. 

Purpose: The following code was designed to visualize the accuracy of SPCC and Edit distance calculations across the various experimental treatments. 
  First, the code creates a figure (TKTK figure XX in manuscript) that visualizes accuracy scores. This figure uses output from the script TKTK "Synthetic_Experiments"to create a data frame which is used to create plots of average accuracy for SPCC and Edit methods by Group Info Proportion and Social Environment Treatments. Plots are separate for information level (group or individual).
  Second, this code calculates Cliff's Delta Effect Size for Group vs Individual Information level accuracy measures across all Social Environment X Group Information Proportion X Method conditions. Before calculating these effect sizes, we check the distribution of our accuracy measures. They are not normally distributed, so we opt to calculate Cliff's Delta as the effect size. This code saves the data table with all the Cliff's Delta values, 95% Confidence Intervals and effect size magnitudes. Magnitude is assessed through the effsize package, which uses thresholds provided in Romano, 2006. (|d|<0.147 "negligible", |d|<0.33 "small", |d|<0.474 "medium", otherwise "large"). These values are included in the TKTK table in the manuscript. Finally, we create density plots to viszualize effect size measures to create main and supplemental figures for the manuscropt. 

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# tktk update list
# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "pbapply", "stringdist", "tidyverse",  "data.table", "ggpubr", "effsize", "paletteer")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### Manually update in every new coding session ##################################

# Initialize a base path (we may need a separate base path per user)
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
path <- "C:/Users/britt/Desktop/paRsynth_methods_synthetic_dataset" #Brittany's path

# Initialize a path for the local GitHub repo for this manuscript, for saving final figures here
git_path <- "C:/Users/britt/Documents/GitHub/paRsynth-methods-paper/figures" # Britt's path
# git_path <- file.path(path, "GitHub_repos/paRsynth-methods-paper/figures") # Grace's path
###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_simulation_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){ 
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){ 
  dir.create(figure_path)
}

```

# Part 1: Plotting accuracy scores by XXX

## Read in accuracy calculations from XXX output
```{r}

files <- list.files(path = data_path, pattern = "^Accuracy_")
files

res <- data.table::rbindlist(pblapply(1:length(files), function(n){
  
  return(read.csv(file.path(data_path, files[n])))
  
}), fill = TRUE)

glimpse(res)

# View(res)

# Check that there are no accuracy values above 1, looks good
sapply(res %>%
         dplyr::select(names(.)[grep("accuracy", names(.))]),
       function(X){
         any(X > 1)
       }
)

# Check that there are no accuracy values below 0, looks good
sapply(res %>%
         dplyr::select(names(.)[grep("accuracy", names(.))]),
       function(X){
         any(X < 0)
       }
)

```

## Modify datframe "res" to allow for plotting of accuracy results and 95% confidence intervals, save this dataframe as "res_summ_acc"
```{r}

# Average Accuracy Measures by Encoding treatment and social condition

# Check that the number of rows matches the number of treatments and iterations
# 4 social and 4 information treatments by 10 iterations should be 160 rows, looks good
glimpse(res)

# Summarize the results from the synthetic experiments to calculate the mean and 95% CI per treatment combination (social condition and information encoding condition)

res_summ_acc <- res %>%
  # Make the data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>%
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    tmp = accuracy_type,
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    tmp = gsub(pattern = "_mean", replace = "", tmp)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = tmp, into = c(NA, "accuracy_method", "accuracy_level"), sep = "_") %>%
  # View()
  # Group by the columns that have information about each experimental treatment
  # Operations like this are helpful for avoiding nested loops. This grouping should yield 16 groups across the two experimental treatments (4 x 4), plus the two methods and social levels for accuracy calculations
  dplyr::group_by(n_groups, group_information_proportion, accuracy_method, accuracy_level) %>%
  # Once a data frame is grouped, you can calculate summary statistics by each group
  dplyr::summarise(
    mean_accuracy = mean(accuracy_measurements),
    # Calculate the 95% CI measurements and extract the upper 95% CI value
    upper_95_CI = Rmisc::CI(accuracy_measurements, ci = 0.95)[["upper"]],
    lower_95_CI = Rmisc::CI(accuracy_measurements, ci = 0.95)[["lower"]]
  ) %>%
  # Make sure to ungroup before plotting, and the columns used for grouping will be retained
  ungroup() %>%
  # Reorganize scoial_envt_treatment, so that legend scale goes in order from Sparse to Dense
  # mutate() creates new columns and can be used to modify/overwrite exist columns, like below when reorganizing factor levels
  dplyr::mutate(
    n_groups = factor(n_groups),
    # Convert the x-axis column to factor to control axis ticks
    group_information_proportion = factor(round(group_information_proportion, 2))
  )

# There should be 4 social conditions * 4 information encoding conditions * 2 accuracy methods * 2 social levels in rows, or 64 rows, looks good
glimpse(res_summ_acc)

# The levels for the social condition treatment column looks good
levels(res_summ_acc$n_groups)

# Looks good
unique(res_summ_acc$accuracy_method)
unique(res_summ_acc$accuracy_level)

```

## Plot accuracy scores
```{r}
# Make color list that contains 1 ,2 4, and 5th color hex codes from paletteer_packages:Arches
# paletteer_d("nationalparkcolors::Arches")
#A8CDECFF #F6955EFF #682C37FF #9B6981FF #7887A4FF #A89F8EFF
# Use #A8CDECFF #F6955EFF #9B6981FF #7887A4FF

cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 0.2)
shps <- c(21, 24) # Encode accuracy method by shape. See the points function for options

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
class_labs <- c("Classes: 2", "Classes: 4", "Classes: 6", "Classes: 8")
names(class_labs) <- c("2", "4", "6", "8")

# Renaming the Accuracy Information Level labels
level_labs <- c("Group-level accuracy", "Individual-level accuracy")
names(level_labs) <- c("group", "individual")

# Renaming the Accuracy Method labels
method_labs <- c("edit distance", "SPCC")
names(method_labs) <- c("edit", "SPCC")

# Aaking this in case we want to make the facet background a very very light grey
ngrey <- scales::alpha("grey", 0.2)

# Make the faceted plot without ggarrange(), no need to make separate plots unless you need more flexibility
res_summ_acc %>%
  ggplot(aes(x = group_information_proportion, y = mean_accuracy, color = accuracy_level, fill = accuracy_level, shape = accuracy_level)) +
  # linewidth controls the width of the errorbar lines, stroke controls the width of the symbol border
  geom_pointrange(aes(ymin = lower_95_CI, ymax = upper_95_CI), linewidth = 0.5, stroke = 0.5, size = 0.75) +
  facet_grid(
    accuracy_method ~ n_groups,
    labeller = labeller(accuracy_method = method_labs, n_groups = class_labs)
  ) +
  scale_y_continuous(limits = c(0, 1.05)) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fillcols) +
  scale_shape_manual(values = shps) +
  # Change the legend titles, make sure to do this for all legend aesthetic layers. You can also override aesthetics set in the main plot
  guides(color = guide_legend(title = "Social level", override.aes = list(size = 0.8)), fill = guide_legend(title = "Social level"),
         shape = guide_legend(title = "Social level")) +
  labs(y = "Average accuracy", x = "Proportion of group information") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.margin = margin(t = 0, r = 0, b = -0.25, l = 0, unit = "line"),
    strip.text.x = element_text (size = 11, face = "plain"),
    strip.text.y = element_text (size = 11, face = "plain"),
    strip.background = element_rect(color = "black", fill = ngrey)
  )

# save as tiff file
ggsave(filename = file.path(git_path, "AverageAccuracy_PointRange.tiff"), width = 7.25, height = 6.25, units = "in", dpi = 300)

# This is a good reference to walk through customizing facet aes https://www.datanovia.com/en/blog/how-to-change-ggplot-facet-labels/
```


# TKTK calculate then plot effect size

## First, check the normality the accuracy measures (summed by level) before running effect size analyses. For each measure, create density and QQ plots to visualize the distribution of the data, then perform a Shapiro Wilks test of normality. 
```{r}

# Start with data frame "res"
glimpse(res)

# To check the distribution of our accuracy measures, we need to set up new data the has separate columns for group and individual accuracy measures and saves the information about method (SPCC or edit distance) in another column
# To do this, we will create a table called "res_summ_eff"
res_summ_eff <- res %>%
    #Make data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy", take the column names and move them to a column called "accuracy_type" and the values to a column called "accuracy_measurements"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>% 
  # Create new columns that extract information in "accuracy_type" about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    accuracy_type = gsub(pattern = "_mean", replace = "", accuracy_type)
  ) %>%
  # Then use "separate" to extract the information that we want. The "NA" in "into" allows us to drop information that we don't want to retain
  tidyr::separate(col = accuracy_type, into = c(NA, "accuracy_method", "accuracy_level")) %>% 
  # Now, recover "level" as separate columns with pivot wider. 
  pivot_wider(
    names_from = accuracy_level, 
    values_from = accuracy_measurements,
    names_glue = "accuracy_{accuracy_level}_measurements"
  ) 

# end with the new data table, "res_summ_eff"
glimpse(res_summ_eff)

# Now check distribution  of two accuracy measures (Group and Individual) using 3 methods: density plot, QQ plot, and Shaprio Wilks Normality Test

# First, check the distribution of accuracy_group_measurements
# Create a density plot for all values in "accuracy_group_measurements". Normally distributed data would follow a bell-shaped curve here. Our density plot does not appear to be normally distributed.
print(ggpubr::ggdensity(res_summ_eff$accuracy_group_measurements, 
                  main = "Density plot of SPCC Group Accuracy", 
                  xlab = "Accuracy"))
# Create a qq plot. Normally distributed data would follow the trend line on the qq plot, but our data deviates from this line.
print(ggpubr::ggqqplot(res_summ_eff$accuracy_group_measurements))
# perform a Shapiro Wilk's test for normality
print(shapiro.test(res_summ_eff$accuracy_group_measurements))
# Density plot is left skewed and QQ plot is not aligned
# 	Shapiro-Wilk normality test
# data:  res_summ_eff$accuracy_group_measurements
# W = 0.92249, p-value = 8.049e-12
# P value of <0.05 implies the data are significantly different from normal). NOT NORMALLY DISTRIBUTED

# Now repeat the steps above, but for "accuracy_individual_measurements"
print(ggpubr::ggdensity(res_summ_eff$accuracy_individual_measurements, 
                  main = "Density plot of SPCC Group Accuracy", 
                  xlab = "Accuracy"))
print(ggpubr::ggqqplot(res_summ_eff$accuracy_individual_measurements))
# Density plot is left skewed and QQ plot is not aligned
# 	Shapiro-Wilk normality test
# data:  res_summ_eff$accuracy_individual_measurements
# W = 0.94642, p-value = 2.201e-09
# P value of <0.05 implies the data are significantly different from normal). NOT NORMALLY DISTRIBUTED

#Because the accuracy measures are not normally distributed, we will use Cliff's delta to calculate effect size. Cliff's D can be used to estimate the effect size for an experiment comparing two samples with ordinal data. See this page for an R tutorial: https://openpublishing.library.umass.edu/pare/article/id/1977/
```

## Second, calculate effect sizes for Group vs Individual Accuracy for all Social x Info Proportion combinations between Methods
```{r}

# Start with data frame "res_sum_eff" created above
glimpse(res_summ_eff)

# Calculate effect sizes of the difference between levels per treatment combination, and save these results to a table called "eff_res_level"
eff_res_level <- res_summ_eff %>% 
  # Group by the columns that have information about each experimental treatment
  # Operations like this are helpful for avoiding nested loops. This grouping should yield 32 groups
  dplyr::group_by(n_groups, group_information_proportion, accuracy_method) %>% 
  # Once the data frame is grouped, we can calculate effect size comparisons 
  # Because we call Group measurements before Individual measurements in this function, it means Group is the comparison group. Therefore, a negative eff_delta value means the distribution of Group measurements is smaller than Individual measurements. A positive value means it is bigger. Below, we save all the delta values, 95% confidence intervals, and the magnitudes of each effect size comparison. 
  dplyr::reframe(
    eff_delta = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["estimate"]],
    eff_CI_upper = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["conf.int"]][["upper"]],
    eff_CI_lower = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["conf.int"]][["lower"]],
    eff_magnitude = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["magnitude"]]
  ) 

# This code prints the following warning message, which we investigate below:

# Warning message:
# There were 60 warnings in `dplyr::reframe()`.
# The first warning was:
# ℹ In argument: `eff_delta = ...[[]]`.
# ℹ In group 8: `n_groups = 2`, `group_information_proportion = 1`,
#   `accuracy_method = "edit"`.
# Caused by warning in `cliff.delta.default()`:
# ! The samples are fully disjoint, using approximate Confidence Interval estimation
# ℹ Run dplyr::last_dplyr_warnings() to see the 59 remaining
#   warnings. 
# This code throws several warnings:
# Running dplyr::last_dplyr_warnings() shows that this warning pops up for many other effect size calculations too, like group 17: `n_groups = 6`, `group_information_proportion = 0`,
  # `accuracy_method = "SPCC"`.
# See below for our investigation of these warnings

glimpse(eff_res_level)

# Print the results
eff_res_level %>%
  # The period indicates the current object
  print(n = nrow(.))

# Save the results as a .csv file as well
eff_res_level %>%
  write.csv(., file = file.path(data_path, "effect_sizes_byLevel.csv"), row.names = FALSE)

```

## Third, TKTK make a plot to highlight how effect sizes were calculated. Density plots of the accuracy distributions to highlight how effect sizes were calculated.

Make one main figure that has class sizes of 2 and 8 only. Make 2 supplementary figures of all classes but edit distance and SPCC only.

Main figure.
```{r}

eff_res <- read.csv(file.path(data_path, "effect_sizes_byLevel.csv"))
glimpse(eff_res)

cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 1)
shps <- c(21, 24) # Encode accuracy level. See the points function for options

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
class_labs <- c("Classes: 2", "Classes: 8")
names(class_labs) <- c("2", "8")

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
method_labs <- c("Edit", "SPCC")
names(method_labs) <- c("edit", "SPCC")

prop_labs <- c("Proportion of\n group information: 0", "0.33", "0.67", "1")
names(prop_labs) <- unique(res$group_information_proportion)

# Aaking this in case we want to make the facet background a very very light grey
ngrey <- scales::alpha("grey", 0.1)

glimpse(res)

# Make the faceted plot without ggarrange(), no need to make separate plots unless you need more flexibility
res_density_values <- res %>%
  # Make the data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>%
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    tmp = accuracy_type,
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    tmp = gsub(pattern = "_mean", replace = "", tmp)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = tmp, into = c(NA, "accuracy_method", "accuracy_level"), sep = "_") %>% 
  # Change social level labels to be capitalized
  dplyr::mutate(
    accuracy_level = gsub("group", "Group", accuracy_level),
    accuracy_level = gsub("individual", "Individual", accuracy_level)
  )

glimpse(res_density_values)

# Generate means for vertical dashed lines
means <- res_density_values %>%
  dplyr::filter(n_groups %in% c(2, 8)) %>%
  group_by(accuracy_level, accuracy_method, n_groups, group_information_proportion) %>%
  dplyr::summarize(
    mean_val = mean(accuracy_measurements)
  ) %>%
  dplyr::select(
    accuracy_level, accuracy_method, n_groups, group_information_proportion, mean_val
  ) %>%
  ungroup()

glimpse(means)

# Make labels of the effect size value and the 95% CI
glimpse(eff_res)

eff_res_label <- eff_res %>% 
  dplyr::filter(n_groups %in% c(2, 8)) %>%
  group_by(n_groups, accuracy_method, group_information_proportion) %>% 
  dplyr::mutate(
    eff_label = paste(c(sprintf("%.02f", round(eff_delta, 2)), " (", paste(c(sprintf("%.02f", round(eff_CI_lower, 2)), sprintf("%.02f", round(eff_CI_upper, 2))), collapse = ", "), ")"), collapse = "")
  ) %>% 
  # Add a label to create bolded text for large effect sizes (>= 0.474)
  dplyr::mutate(
    eff_magnitude = ifelse(abs(eff_delta) >= 0.474, "large", "not large"),
    eff_fontface = ifelse(abs(eff_delta) >= 0.474, "bold", "plain")
  ) %>% 
  ungroup()

glimpse(eff_res_label)

# Use the means to generate coordinates for where bars to indicate effect size calculations should start and end
bar_coords <- means %>%
  pivot_wider(
    values_from = "mean_val",
    names_from = "accuracy_level"
  ) %>% 
  # Add information for coloring these bars by which information had greater accuracy
  dplyr::mutate(
    stronger_encoding = ifelse(Group > Individual, "Group", "Individual")
  ) %>% 
  # Join with the effect size results to get information about which of these bars or segments correspond to large effect sizes
  inner_join(
    eff_res_label %>% 
      dplyr::select(accuracy_method, group_information_proportion, n_groups, eff_magnitude),
    by = c("accuracy_method", "group_information_proportion", "n_groups")
  )

glimpse(bar_coords)

res_density_values %>%
  dplyr::filter(n_groups %in% c(2, 8)) %>%
  ggplot() +
  # Density curves for group level (blue)
  geom_density(data = res_density_values %>%
                 dplyr::filter(n_groups %in% c(2, 8)) %>%
                 dplyr::filter(accuracy_level == "Group"), color = scales::alpha(fillcols[1], 0), fill = scales::alpha(fillcols[1], 0.65), aes(x = accuracy_measurements)) +
  # Add a mean line using geom_segment to control height: mean line for group level
  geom_segment(data = means %>%
                 dplyr::filter(accuracy_level == "Group"), aes(x = mean_val, xend = mean_val, y = 0, yend = 40), linewidth = 0.75, color = fillcols[1], linetype = "dashed") +
  # Density curves for individual level (orange)
  geom_density(data = res_density_values %>%
                 dplyr::filter(n_groups %in% c(2, 8)) %>%
                 dplyr::filter(accuracy_level == "Individual"), color = scales::alpha(fillcols[2], 0), fill = scales::alpha(fillcols[2], 0.65), aes(x = accuracy_measurements)) +
  # Add a mean line using geom_segment to control height: mean line for individual level
  geom_segment(data = means %>%
                 dplyr::filter(accuracy_level == "Individual"), aes(x = mean_val, xend = mean_val, y = 0, yend = 40), linewidth = 0.75, color = fillcols[2], linetype = "dashed") +
  # Add horizontal bars or segments between the means of each density curve that represent each effect size calculation. These bars are colored by the social level with higher accuracy, and the transparency folows the strength of the effect size (large effect sizes are more opaque)
  geom_segment(data = bar_coords, aes(x = Group, xend = Individual, y = 40, yend = 40, color = stronger_encoding, alpha = eff_magnitude), linewidth = 2) +
  facet_grid(
    n_groups ~ accuracy_method ~ group_information_proportion,
    scales = "fixed",
    labeller = labeller(accuracy_method = method_labs, n_groups = class_labs, group_information_proportion = prop_labs)
  ) +
  # Add the effect size values plus the 95% CIs. Add bolded text for large effect sizes
  geom_text(data = eff_res_label, aes(label = eff_label, y = 50, x = 0.65, fontface = eff_fontface), size = 3) +
  scale_y_continuous(limits = c(0, 55)) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fillcols) +
  scale_shape_manual(values = shps) +
  scale_alpha_manual(values = c(1, 0.5)) +
  # Change the legend titles, make sure to do this for all legend aesthetic layers. You can also override aesthetics set in the main plot
  guides(color = guide_legend(title = "Social level", override.aes = list(size = 0.8)), fill = guide_legend(title = "Social level"), alpha = "none") +
  labs(y = "Density of accuracy values at either social social", x = "Accuracy measurements") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    legend.position = "top",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.margin = margin(t = 0, r = 0, b = -0.25, l = 0, unit = "line"),
    strip.text.x = element_text (size = 10, face = "plain"),
    strip.text.y = element_text (size = 10, face = "plain"),
    strip.background = element_rect(color = "black", fill = ngrey)
  )

# save as tiff file
ggsave(filename = file.path(git_path, "AccuracyDensityPlots_EffectSizes.tiff"), width = 7.25, height = 6.25, units = "in", dpi = 300)

```

Supplementary figures.
```{r}

cols <- c("#A8CDECFF", "#F6955EFF", "#9B6981FF", "#7887A4FF")
fillcols <- scales::alpha(cols, alpha = 0.2)
shps <- c(21, 24) # Encode accuracy level. See the points function for options

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
class_labs <- c("Classes: 2", "4", "6", "8")
names(class_labs) <- c("2", "4", "6", "8")

# Need to make named character vectors to relabel facet text
# Renaming the Accuracy Method labels
method_labs <- c("Edit", "SPCC")
names(method_labs) <- c("edit", "SPCC")

prop_labs <- c("Proportion of group information: 0", "0.33", "0.67", "1")
names(prop_labs) <- unique(res$group_information_proportion)

# Aaking this in case we want to make the facet background a very very light grey
ngrey <- scales::alpha("grey", 0.2)

glimpse(res)

# Make the faceted plot without ggarrange(), no need to make separate plots unless you need more flexibility
res_density_values <- res %>%
  # Make the data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>%
  # Create new columns that extract information in accuracy_type about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    tmp = accuracy_type,
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    tmp = gsub(pattern = "_mean", replace = "", tmp)
  ) %>%
  # Then use separate to extract the information that we want. The NA in into allows us to drop information that we don't want to retain
  tidyr::separate(col = tmp, into = c(NA, "accuracy_method", "accuracy_level"), sep = "_")

glimpse(res_density_values)

# Generate means
means <- res_density_values %>%
  group_by(accuracy_level, accuracy_method, n_groups, group_information_proportion) %>%
  dplyr::summarize(
    mean_val = mean(accuracy_measurements)
  ) %>%
  dplyr::select(
    accuracy_level, accuracy_method, n_groups, group_information_proportion, mean_val
  )

res_density_values %>%
  ggplot(aes(x = accuracy_measurements)) +
  geom_density(data = res_density_values %>%
                 dplyr::filter(accuracy_level == "group"), color = cols[1], fill = fillcols[1]) +
  geom_vline(data = means %>%
               dplyr::filter(accuracy_level == "group"), aes(xintercept = mean_val), color = cols[1], linetype = "dashed") +
  geom_density(data = res_density_values %>%
                 dplyr::filter(accuracy_level == "individual"), color = cols[2], fill = fillcols[2]) +
  geom_vline(data = means %>%
               dplyr::filter(accuracy_level == "individual"), aes(xintercept = mean_val), color = cols[2], linetype = "dashed") +
  facet_grid(
    accuracy_method ~ n_groups ~ group_information_proportion,
    scales = "free",
    labeller = labeller(accuracy_method = method_labs, n_groups = class_labs, group_information_proportion = prop_labs)
  ) +
  scale_color_manual(values = cols) +
  scale_fill_manual(values = fillcols) +
  scale_shape_manual(values = shps) +
  # Change the legend titles, make sure to do this for all legend aesthetic layers. You can also override aesthetics set in the main plot
  guides(color = guide_legend(title = "Method", override.aes = list(size = 0.8)), fill = guide_legend(title = "Method"),
         shape = guide_legend(title = "Accuracy level", order = 1, override.aes = list(size = 0.8))) +
  labs(y = "Density", x = "Accuracy measurements") +
  theme_bw() +
  # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11),
    legend.position = "top",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.margin = margin(t = 0, r = 0, b = -0.25, l = 0, unit = "line"),
    strip.text.x = element_text (size = 10, face = "plain"),
    strip.text.y = element_text (size = 10, face = "plain"),
    strip.background = element_rect(color = "black", fill = ngrey)
  )

# save as tiff file
ggsave(filename = file.path(git_path, "DensityPlot_EffectSizeAide.tiff"), width = 7.25, height = 5.25, units = "in", dpi = 300)

```
