---
title: "ConceptualFigure_FrequencyAnchors"
author: Grace Smith-Vidaurre, Brittany Coppinger
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Purpose: This script uses the synthetic call metadata to create a conceptual graphic of frequency anchors for the paRsynth pipeline. This figure is used for talks and potentially for the manuscript.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, messsage = FALSE)

```

Load packages and set paths.
```{r}

# Clean the global environment
rm(list = ls())

# Specify the required packages
X <- c("devtools", "dplyr", "tidyverse", "data.table", "gganimate", "tuneR", "warbleR")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

```

```{r load packages, eval = FALSE}

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE, verbose = FALSE))

```

```{r load packages in background, include = FALSE}

# The only solution right now to avoid having a whole bunch of verbose output printed from the chunk above
# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE, verbose = FALSE))

```

Initialize working directories for data on your local machine.
```{r}

# Initialize a base path (this will need to be different per user)
# path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "C:/Users/britt/Desktop" # Britt's path
path <- "/Users/summe/OneDrive/Desktop" #Summer's path

# Initialize a path for the local GitHub repo for this manuscript, for saving final figures here
# git_path <- "C:/Users/britt/Documents/GitHub" # Britt's path
# git_path <- "/Users/gracesmith-vidaurre/Desktop/GitHub_repos"
git_path <- "/Users/summe/OneDrive/Desktop/github_repo/paRsynth-methods-paper/figures" #Summer's path

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_methods_synthetic_dataset"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Specify a folder inside the analysis directory where audio will be written out/read in
audio_dir <- "audio"

# Combine the base path, the analysis directory, and the audio directory into a single path
audio_path <- file.path(path, analysis_dir, audio_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the github directory where data will be written out/read in
figure_dir <- "Fig_1"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(git_path, figure_dir)
```

Read in the synthetic call metadata.
```{r}

synthetic_call_metadata <- read.csv(file.path(analysis_path, "synthetic_call_metadata.csv"))
glimpse(synthetic_call_metadata)

```

Choose a single call for talk slides: get the character string and also the vector of frequency anchors.
```{r}

# Choose the first call in this dataset (Group 1, Individual 1, Call 1)
filt_data <- synthetic_call_metadata %>% 
  slice(1)

glimpse(filt_data)

# Call string
filt_data$Call

# [1] "CABCAABACCBCCBAA"

# Frequency anchors are in columns, pull these out as a vector
freq_cols <- filt_data %>%
  # Select only the columns that start with the pattern "Frequency"
  select(names(.)[grep("^Frequency", names(.))])

glimpse(freq_cols)

# We need to transpose this data frame so that all of the frequency values are in rows not columns, and then we need to convert the resulting matrix to a vector
frequency_anchors <- as.vector(t(freq_cols))

# Looks good
frequency_anchors
length(frequency_anchors)

```

Make a conceptual graphic showing how the frequency values produced from the paRsynth pipeline pipeline serve as frequency modulation "anchors" for soundgen to generate synthetic audio files. This be a line graph of the frequency anchors above.
```{r}

# Create a data frame of the frequency anchors plus timestamps
freq_anchors <- data.frame(
  freq_anchors = frequency_anchors,
  # The timestamps should be evenly spaced across the duration of the call, which is the soundgen default
  # We generated calls in the first script that had 200 ms duration
  time = round(seq(0.1, 0.3, 0.2/(length(frequency_anchors) - 1)), 3)
)

# X-axis is time, y-axis is frequency
glimpse(freq_anchors)

# Make a graphic of the frequency anchors plus a line through them
Freq_anch_plot <-  ggplot(freq_anchors, aes(x = time, y = freq_anchors/1000)) +
  # geom_line(color = scales::alpha("#A8CDECFF"), linetype = "dotted", linewidth = 2) +
  geom_line(color = "grey24", linetype = "dotted", linewidth = 1) +
  geom_point(size = 5, shape = 21, color = "black", fill = "grey60", stroke = 1.2) +
  #geom_point(size = 3, shape = 19, color = "grey56") +
  xlab("Time (s)") +
  ylab("Frequency (kHz)") +
  scale_y_continuous(limits = c(0, 6.2)) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    # axis.title = element_text(size = 16),
    axis.text = element_text(size = 12),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  ) # 

# We will use this image file and it may need to be resized
# use the ggsave line to save the static plot, as the anim_save line to save the animated plot

# This sizing is being used by Summer for creation of manuscript figure
ggsave(file.path(figure_path, "Concept_FreqAnch.tiff"), units = "in", width = 6.5, height = 3, dpi = 600)



```

Finally, make a spectrogram of the audio file that corresponds with the call used for this figure
```{r}

# Set color palette for spectrograms
gray_colors <- reverse.gray.colors.2(12)

# Read in the audio file, return a wave object
tmp_wav <- tuneR::readWave(file.path(audio_path, "GroupMembership_Group1_Indiv1_Call1.wav"))
# str(tmp_wav)

# Use ggspectro to generate a spectrogram
gg <- ggspectro(wave = tmp_wav, f = tmp_wav@samp.rate, ovlp = 90) +
  
  # Plot amplitude values or cells in the spectrogram. Interpolation needs to be TRUE and sit outside of the aes() call to smoothen the otherwise very pixelated appearance of the raster
  geom_raster(aes(fill = amplitude), hjust = 0, vjust = 0, interpolate = TRUE) +
  
  # Control the x-axis aesthetics
  scale_x_continuous(limits = c(0.08, 0.33), breaks = seq(0.1, 0.3, 0.05), labels = seq(0.1, 0.3, 0.05), expand = c(0, 0)) +
  
  # Control the y-axis aesthetics
  scale_y_continuous(limits = c(0, 9), breaks = seq(0, 8, 2), labels = seq(0, 8, 2), expand = c(0, 0)) +
  
  # We want spectrograms to be in grayscale
  # Change the values of limits to change how colors are assigned across amplitude bins
  scale_fill_gradientn(colours = gray_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-35, 10)) +
  # Use the theme function above to modify the overall plot aesthetics
  theme(
    # Use element_blank() to remove grid lines
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "transparent"),
    panel.border = element_rect(linetype = "solid", fill = NA, color = "grey"),
    axis.line = element_line(linewidth = 0.15),
    legend.position = "none",
    plot.background = element_rect(fill = "white"),
    # Control the white space around the figure in the resulting image file
    plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "lines"), # top, right, bottom, left
    # Turn off the axis titles, which should remove titles for all 3 axes, including amplitude and the amplitude scale bar
    axis.title = element_blank(),
    # Control the size of the x and y-axis text 
    axis.text = element_text(size = 12, color = "black", vjust = 0),
    # Control the size of the axis tick lines
    axis.ticks = element_line(color = "black", linewidth = 0.15)
  )

# Once the plot is generated in the graphics device, you can save as an an image file on your computer using ggsave()
# Substitute the ".wav" extension with the image file extension we will use, with gsub()
# gsub(pattern = ".wav$", replace = ".jpeg", lexicon_wavs[w]) # uncomment to test inside of the function
# The width and the height should be specified once you figure out a good size for spectrograms in the final composite figure
ggsave(filename = file.path(figure_path, "GroupMembership_Group1_Indiv1_Call1.tiff"), units = "in", width = 6.38, height = 3, dpi = 600)
```

