---
title: "Information Encoding Experiments - Effect Size Calculations"
author: "Grace Smith-Vidaurre, Brittany Coppinger, others"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Purpose: The following code was designed to calculate Cliff's Delta Effect Size for Group vs Individual Information level accuracy measures across all Social Environment X Group Information Proportion X Method conditions. Before calculating these effect sizes, we check the distribution of our accuracy measures. They are not normally distributed, so we opt to calculate Cliff's Delta as the effect size.

Effect Sizes are calculated in Steps 3. This code saves the data table with all the Cliff's Delta values, 95% Confidence Intervals and effect size magnitudes. Magnitude is assessed through the effsize package, which uses thresholds provided in Romano, 2006. (|d|<0.147 "negligible", |d|<0.33 "small", |d|<0.474 "medium", otherwise "large")

These tables will be included in the manuscript and will be called in future figure scripts to plot average effect size values for each type of comparison. 

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE)

```

Load packages and set cores.
```{r}

# Clean the global environment
rm(list = ls())

# tktk update list
# Initialize packages for data processing and analysis
X <- c("devtools", "dplyr", "pbapply", "stringdist", "tidyverse",  "data.table", "ggpubr", "effsize")

# Install packages if they're not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

# Load all of the packages specified above
invisible(lapply(X, library, character.only = TRUE))

# Set cores for parallel processing
cores <- parallel::detectCores() - 4

```

Initialize working directories for data and figures.
```{r}

###################### Manually update in every new coding session ##################################

# Initialize a base path (we may need a separate base path per user)
path <- "/Users/gracesmith-vidaurre/Desktop" # Grace's path
# path <- "/home/gsvidaurre/Desktop" # Grace's path
# path <- "~/Desktop" # Grace's path
# path <- "C:/Users/britt/Desktop" #Brittany's path

###################################################################################

```

```{r}

# Initialize the directory for analysis on your local computer
analysis_dir <- "paRsynth_synthetic_experiments"

# Combine the base path and the data directory into a single path
analysis_path <- file.path(path, analysis_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(analysis_path)){ 
  dir.create(analysis_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
data_dir <- "data"

# Combine the base path, the analysis directory, and the data directory into a single path
data_path <- file.path(path, analysis_dir, data_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(data_path)){ 
  dir.create(data_path)
}

# Specify a folder inside the analysis directory where data will be written out/read in
figure_dir <- "figures"

# Combine the base path, the analysis directory, and the data directory into a single path
figure_path <- file.path(path, analysis_dir, figure_dir)

# Create the data directory if it doesn't already exist on your computer
if(!dir.exists(figure_path)){ 
  dir.create(figure_path)
}

```

Step 1: Load the data files from the Accuracy Calculations results. These files are the results from the "Experiments_InformationEncoding_Accuracy" script. These need to be manually downloaded from google drive and stored in the data folder first 
```{r}

# Read in outputs from the TKTK code that generated accuracy scores
files <- list.files(path = data_path, pattern = "^Accuracy_")

# Combine these files into one datatable called "res" 
res <- data.table::rbindlist(pblapply(1:length(files), function(n){
  
  return(read.csv(file.path(data_path, files[n])))
  
}), fill = TRUE)

# View the datatable "res"
glimpse(res)

```

Step 2: Checking the normality of the accuracy measures (summed by level) before we run effect size analyses. For each measure, we create density and QQ plots to visualize the distribution of the data. Then we perform a Shapiro Wilks test of normality. 
```{r}

# Start with data frame "res"
glimpse(res)

# To check the distribution of our accuracy measures, we need to set up new data the has separate columns for group and individual accuracy measures and saves the information about method (SPCC or edit distance) in another column
# To do tihs, we will create a table called "res_summ"
res_summ <- res %>%
    #Make data frame longer so that each row is a separate accuracy calculation
  pivot_longer(
    # Select all of the columns that start with the pattern "accuracy", take the column names and move them to a column called "accuracy_type" and the values to a column called "accuracy_measurements"
    cols = names(.)[grep("^accuracy", names(.))],
    names_to = "accuracy_type",
    values_to = "accuracy_measurements"
  ) %>% 
  # Create new columns that extract information in "accuracy_type" about the method used to calculate accuracy and the social level at which accuracy was calculated
  dplyr::mutate(
    # Replace the pattern "_mean" with nothing so that all values in this column have 3 units separated by an underscore
    accuracy_type = gsub(pattern = "_mean", replace = "", accuracy_type)
  ) %>%
  # Then use "separate" to extract the information that we want. The "NA" in "into" allows us to drop information that we don't want to retain
  tidyr::separate(col = accuracy_type, into = c(NA, "accuracy_method", "accuracy_level")) %>% 
  # Now, recover "level" as separate columns with pivot wider. 
  pivot_wider(
    names_from = accuracy_level, 
    values_from = accuracy_measurements,
    names_glue = "accuracy_{accuracy_level}_measurements"
  ) 

# end with the new data table, "res_summ"
glimpse(res_summ)

```

```{r}

# Now check distribution  of two accuracy measures (Group and Individual) using 3 methods: density plot, QQ plot, and Shaprio Wilks Normality Test

# First, check the distribution of accuracy_group_measurements
# Create a density plot for all values in "accuracy_group_measurements". Normally distributed data would follow a bell-shaped curve here. Our density plot does not appear to be normally distributed.
print(ggpubr::ggdensity(res_summ$accuracy_group_measurements, 
                  main = "Density plot of SPCC Group Accuracy", 
                  xlab = "Accuracy"))
# Create a qq plot. Normally distributed data would follow the trend line on the qq plot, but our data deviates from this line.
print(ggpubr::ggqqplot(res_summ$accuracy_group_measurements))
# perform a Shapiro Wilk's test for normality
print(shapiro.test(res_summ$accuracy_group_measurements))
# Density plot is left skewed and QQ plot is not aligned
# 	Shapiro-Wilk normality test
# data:  res_summ$accuracy_group_measurements
# W = 0.92249, p-value = 8.049e-12
# P value of <0.05 implies the data are significantly different from normal). NOT NORMALLY DISTRIBUTED

# Now repeat the steps above, but for "accuracy_individual_measurements"
print(ggpubr::ggdensity(res_summ$accuracy_individual_measurements, 
                  main = "Density plot of SPCC Group Accuracy", 
                  xlab = "Accuracy"))
print(ggpubr::ggqqplot(res_summ$accuracy_individual_measurements))
# Density plot is left skewed and QQ plot is not aligned
# 	Shapiro-Wilk normality test
# data:  res_summ$accuracy_individual_measurements
# W = 0.94642, p-value = 2.201e-09
# P value of <0.05 implies the data are significantly different from normal). NOT NORMALLY DISTRIBUTED

```

Because the accuracy measures are not normally distributed, we will use Cliff's delta to calculate effect size. Cliff's D can be used to estimate the effect size for an experiment comparing two samples with ordinal data. See this page for an R tutorial: https://openpublishing.library.umass.edu/pare/article/id/1977/

Step 3: Calculating Effect Sizes for Group vs Individual Accuracy for all Social x Info Proportion combinations between Methods
```{r}

# Start with data frame "res_sum" created above
glimpse(res_summ)

# Calculate effect sizes of the difference between levels per treatment combination, and save these results to a table called "eff_res_level"
eff_res_level <- res_summ %>% 
  # Group by the columns that have information about each experimental treatment
  # Operations like this are helpful for avoiding nested loops. This grouping should yield 32 groups
  dplyr::group_by(n_groups, group_information_proportion, accuracy_method) %>% 
  # Once the data frame is grouped, we can calculate effect size comparisons 
  # Because we call Group measurements before Individual measurements in this function, it means Group is the comparison group. Therefore, a negative eff_delta value means the distribution of Group measurements is smaller than Individual measurements. A positive value means it is bigger. Below, we save all the delta values, 95% confidence intervals, and the magnitudes of each effect size comparison. 
  dplyr::reframe(
    eff_delta = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["estimate"]],
    eff_CI_upper = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["conf.int"]][["upper"]],
    eff_CI_lower = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["conf.int"]][["lower"]],
    eff_magnitude = effsize::cliff.delta(accuracy_group_measurements, accuracy_individual_measurements, conf.level = .95)[["magnitude"]]
  ) 

# This code prints the following warning message, which we investigate below:

# Warning message:
# There were 60 warnings in `dplyr::reframe()`.
# The first warning was:
# ℹ In argument: `eff_delta = ...[[]]`.
# ℹ In group 8: `n_groups = 2`, `group_information_proportion = 1`,
#   `accuracy_method = "edit"`.
# Caused by warning in `cliff.delta.default()`:
# ! The samples are fully disjoint, using approximate Confidence Interval estimation
# ℹ Run dplyr::last_dplyr_warnings() to see the 59 remaining
#   warnings. 
# This code throws several warnings:
# Running dplyr::last_dplyr_warnings() shows that this warning pops up for many other effect size calculations too, like group 17: `n_groups = 6`, `group_information_proportion = 0`,
  # `accuracy_method = "SPCC"`.
# See below for our investigation of these warnings

glimpse(eff_res_level)

# Print the results
eff_res_level %>%
  # The period indicates the current object
  print(n = nrow(.))

# Save the results as a .csv file as well
eff_res_level %>%
  write.csv(., file = file.path(data_path, "effect_sizes_byLevel.csv"), row.names = FALSE)
.
```

Step 4: Investigating warnings and creating supplemental figures

The warnings above mean that the distributions for the comparison throwing the warning are completely different from each other. To double check this is true, below we create density plots for each n_group and group info proportion combination for SPCC Accuracy measures and for Edit Distance Accuracy measure. This will be a Supplemental Figure in the Manuscript. 

```{r}
# take the datatable "res_summ" and alter it so that "n_groups" is a factor
res_summ <- res_summ %>% 
  dplyr::mutate(
    n_groups = factor(n_groups),
    # Convert the x-axis column to factor to control axis ticks
    group_information_proportion = factor(round(group_information_proportion, 2))
  ) 

# confirm those changes were made by glimpsing the new "res_summ"
glimpse(res_summ)

# Rename Facet variables for labeling purposes
res_summ_rename <- res_summ %>% 
  dplyr::rename(
    Clusters = n_groups,
    Group_Information = group_information_proportion)

# confirm those changes were made by glimpsing the new "res_summ_rename"
glimpse(res_summ_rename)

# Create density plots for visualization of the warning above for SPCC method
res_summ_rename %>% 
  # filter "res_summ_rename" so that we are only using SPCC values
  dplyr::filter(accuracy_method == "SPCC") %>% 
  # use ggplot to create density plots
  ggplot() +
  # create a density plot for the Group measurements
  geom_density(aes(x = accuracy_group_measurements), fill = alpha("#F6955EFF", 0.65)) +
  # create another density plot onto of the first that is for Individual Measurments
  geom_density(aes(x = accuracy_individual_measurements), fill = alpha("#A8CDECFF", 0.65)) +
  # Create a grid off all the density plots
  facet_grid(
    Clusters ~ Group_Information,
    scales = "free",
    # label facets with variable name and value
    labeller = label_both) +
  labs(y = "Density", x = "Accuracy Score") +
  theme_bw() +
    # Remove gridlines using theme() and change the background color of the strip labels
  # Place legend on the top
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size=14),
    axis.title = element_text(size=16,face="bold"),
    # Change facet elements
    strip.text.x = element_text (size = 14),
    strip.text.y = element_text (size = 14),
    strip.background = element_rect(color = "black", fill = "white")
  )

# Print above plot as tiff
ggsave(filename = "Supplimental_Density_SPCC", path = figure_path, width = 10, height = 10, device = "tiff", dpi = 700)

# Make same plot but for edit distance
res_summ_rename %>% 
  dplyr::filter(accuracy_method == "edit") %>% 
  ggplot() +
  geom_density(aes(x = accuracy_group_measurements), fill = alpha("#F6955EFF", 0.65)) +
  geom_density(aes(x = accuracy_individual_measurements), fill = alpha("#A8CDECFF", 0.65)) +
  facet_grid(
    Clusters ~ Group_Information,
    scales = "free",
    labeller = label_both) +
  labs(y = "Density", x = "Accuracy Score") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.text = element_text(size=14),
    axis.title = element_text(size=16,face="bold"),
    strip.text.x = element_text (size = 14),
    strip.text.y = element_text (size = 14),
    strip.background = element_rect(color = "black", fill = "white")
  )

# Print above plot as tiff
ggsave(filename = "Supplimental_Density_edit", path = figure_path, width = 10, height = 10, device = "tiff", dpi = 700)
```

